### 2016-01-20 paperMSR.tex
Adding the abstract

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}
\usepackage{url}
\usepackage{epsfig}
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{float}           % H para posicionar figuras
\usepackage{booktabs}
\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{MSR '16}{May 14-15, 2016, Austin, Texas, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{MSR}{'16 Austin, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{{\ttlit Bug Seeding}, On the importance of Previous Commit}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodriguez\\
       \affaddr{University King Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonzalez-Barahon\\
      \affaddr{University King Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{University King Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{29 January 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug some , these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit. However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}

\textbf{In this paper, in order to ascertain the validity of such a claim, we have conducted an observational study that involved bug notifications from a very active project such as OpenStack, in which their source code is continuously evolving. Our results are promising in indicating that exists bug fixed which were not introduced in the previous commit.}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>  
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
%\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Bug-introduction, SZZ algoritm, Fix-inducing}

\section{Introduction}
\label{sec:introduction}
In order to investigate if this assumption is valid, we formulate following research questions:
\begin{itemize}
    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not? 
    \item RQ2:  How often is the bug caused in the previous commit? 
\end{itemize}

%The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}. In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports. This problem is solved in Subsection~\ref{}, answering in this way RQ1. After having discriminated bug reports from those that are not, to answer the RQ2 we have calculated how many times the cause of the bug could be attributed to the previous commit (see Subsection~\ref{subsec:second}). Results are then shown in Section~\ref{}. Finally, we present a discussion, including the threats to validity, in Section~\ref{}.

\section{The Case of Study}
\label{sec:caseStudy}
\subsection{Fist Stage: The Filtering}
\label{sec:firstStage}
%OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system. The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.

We use the tool to analyze 500 randomly tickets from the four principal repositories in OpenStack. This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository. They are generally tracked in Launchpad \texttt{Nova},\texttt{Cinder},\texttt{Horizon} and \texttt{Neutron}\footnote{\url{https://bugs.launchpad.net/NameOfRepository}}

The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit. Also, the code changes if neither the descriptions and the comments clarified the underlying ticket. Each ticket was then categorized into one of three following groups.
\begin{enumerate}
  \item The ticket describes a bug report.
  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
  \item The ticket presents a vague description and cannot be classified without doubts.
\end{enumerate}

Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.

\subsubsection{The Tool}
\label{sec:tool}
%A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not. The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.

\subsection{Second Stage: Responsability of Previous Commit}
\label{sec:secondStage}
In the second stage, we only focused on the analysis of \textit{Error} group, because this group contained the tickets that were bug reports. Discarding the \textit{Undecided} group in favour of the \textit{Error} group reduces the accuracy of the experiment due to the fact that some errors are being lost in \textit{Undecided} group. However the \textit{Undecided} group being only 16\% of the bugs under consideration makes us think that this fact does not 
affect the validity of the final results.

We focused on analyzing characteristics of the commit such as the type of code, the number of previous commits involved, and the number of folders modified by the fixing commit to classify the bug report into one of three groups according to the responsibility of the previous commit:

\begin{enumerate}
  \item It is responsible, 
  \item It is not responsible,
  \item Undecided.
\end{enumerate}
 We use therefore the \texttt{diff} command to display line\-by\-line difference between two files. \texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system. \texttt{diff} examines both files and returns the differences found between them, showing the line number.% the necessary modifications which should be done in order to the files match. the differences found between them,showing the line number. %FIXME: de aqui en adelante no entiendo la frase. need to be made for first file and second file to match, that is, returns the differences found between them.

At this stage, we got a list with all the previous commits, which could be where the bug was introduced. We have to identify those previous commits responsible for inserting the line with the bug. When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, after the analysis the responsible can be only one of them or maybe two, in fact sometimes all of them were responsible. Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.

\section{Results}
\label{sec:results}

\subsection{Fist Stage}
\label{sec:resultsFS}
%We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers, 
\begin{table*}
\centering
%\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table*}

\begin{table*}
\begin{center} {\footnotesize
\caption{ Concordance between each developer in each repository}
\label{tab:2}
\begin{tabular}{llllll}
\toprule[0.3mm]%{\smallskip}
  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table*}

\subsection{Second Stage}
\label{sec:resultsSS}

%\begin{table}[htb]
%\begin{center} {\footnotesize
%\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
%\label{secondStage}
%\begin{tabular}{lcc}
%\toprule[0.3mm]
%  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
%  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
%\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
%\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
%\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
%\bottomrule[0.3mm]
%\end{tabular} }
%\end{center}
%\end{table}

\section{Discussion}
\label{sec:discussion}
%This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.

\subsection{Threats to validity}
\label{sec:threats}
The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.

In addition our model has threats, external and internal, that make our model not 100\% valid. The internal threats are following:

\begin{itemize}
    \item We have not taken into account errors that have been classified into \textit{Undecided}.
    \item There could be some lax criteria involving the subjective opinion of the reviewers.
    \item We are not experts in analyzing and classifying tickets, and our inexperience may have influenced the results of the analysis.
    \item We are only using part of the information that the ticket provides, like comments and text. There could be a recognized pattern, unknown at first sight, that involves other parts of the information, or the whole information.
\end{itemize}

The external threats, related to the researchers that have conducted the classification, are following:

\begin{itemize}
    \item The word \textit{bug} is continuously mentioned in the description and commit of a ticket even when we found it is not an error. This could lead to the incorrect classification during the reviewing process.
    \item Some tickets are not explicitly described, which could increase the percentage of \textit{Undecided}. This is especially true if the reviewers are not from OpenStack.
\end{itemize}

Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
\begin{enumerate}
\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
\item Does the Bug report only the same ticket classified as Bug report for all the developers?
\end{enumerate}

\section{Conclusions and Future Work}
\label{sec:conclusions}

%In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases. Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug. Thus, the articles based on SZZ algorithm may be based on a wrong assumption. However, a larger number of tickets has to be studied to ascertain that our findings can be generalized. Our idea is contribute with this study in the knowledge about the responsibility practiced by the previous commit in a bug, helping to the software engineering community in the code review process. FIXME: aclarar esta frase que no me queda clara: Our idea is propose a reinterpretation in the responsibility practiced by the previous commit in a bug.

%In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized. In this way, with a larger population we may be able to find certain patterns that we are now omitting. Furthermore, we extend this study to other projects to ascertain that what we have found occurs regardless of the project analyzed, because the OpenStack may be a special project, where the code is evolving continuously. In fact, we can access a huge database of other projects such as Eclipse or Mozilla that will allow us analyze this assumption, and where we will use statistical analysis to compare the results obtained in the different projects.

%In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage. The future work with the tool will focus on improving and automating the second stage.

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}

### 2016-01-20 paperMSR.tex
Modifying the abstract

@@
 \begin{abstract}
-\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug some , these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit.
+\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit.
 However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}

### 2016-01-20 paperMSR.tex
Modifying the abstract

@@
 \textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit.
-However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}
+However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects which present this characteristic.}
 

### 2016-01-21 paperMSR.tex
Modified title, abstract, keywords.

--- 2016-01-20 paperMSR.tex
@@
 
-\title{{\ttlit Bug Seeding}, On the importance of Previous Commit}
+\title{Who introduced the bug? The importance of the previous commit}
 %\subtitle{[Extended Abstract]
@@
 \begin{abstract}
-\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug some , these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit.
-However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}
+To fix a bug in a certain software product, some parts of its source code are modified.
+At first glance, it could seem reasonable that the fixed bug was introduced by the previous modification of those same parts of the source code (the previous commit).
+In fact, many studies on bug seeding start with this assumption.
+However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug was introduced by other actions, such as an older modification, or a change in called APIs.
 
-\textbf{In this paper, in order to ascertain the validity of such a claim, we have conducted an observational study that involved bug notifications from a very active project such as OpenStack, in which their source code is continuously evolving.
-Our results are promising in indicating that exists bug fixed which were not introduced in the previous commit.}
+This paper tries to shed some light on this area, by analyzing the relationship of bug fixes with their previous commits.
+To this end, we conducted an observational study on bug reports, their fixes, and their correspoonding previous commits for OpenStack.
+Our results show that the mentioned asumption does not hold for a large fraction of the analyzed bugs, which were not introduced by their previous commit.
 \end{abstract}
@@
 
-\keywords{Bug-introduction, SZZ algoritm, Fix-inducing}
+\keywords{Bug introduction, bug seeding, SZZ algoritm, previous commit}
 

### 2016-01-25 paperMSR.tex
adding text

--- 2016-01-20 paperMSR.tex
@@
 \label{sec:introduction}
+How to plan to apply the knowledge in a way that can benefit software engineers.
+What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
+
 In order to investigate if this assumption is valid, we formulate following research questions:
@@
 
-%The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}.
+The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}.
 In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports.
@@
 \label{sec:firstStage}
-%OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
+OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
 The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.
@@
 \label{sec:tool}
-%A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
+A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
 The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.
@@
 Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.
+\subsubsection{Discarting False Positives}
+\label{sec:discarting}
+We have to discart these previous commits that change the format, that add blank spaces and that change comments.
+¿What happen with the lines which are copied from others previous commits?
 
@@
 \label{sec:resultsFS}
-%We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
+We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
 The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
@@
 
-%\begin{table}[htb]
-%\begin{center} {\footnotesize
-%\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-%\label{secondStage}
-%\begin{tabular}{lcc}
-%\toprule[0.3mm]
-%  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
-%  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-%\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
-%\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
-%\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
-%\bottomrule[0.3mm]
-%\end{tabular} }
-%\end{center}
-%\end{table}
+\begin{table}[htb]
+\begin{center} {\footnotesize
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{secondStage}
+\begin{tabular}{lcc}
+\toprule[0.3mm]
+  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
+  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
+\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
+\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
+\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table}
+
+After discarding the noise caused by the false positives the results are:
+\begin{table}[htb]
+\begin{center} {\footnotesize
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{secondStage}
+\begin{tabular}{lcc}
+\toprule[0.3mm]
+  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
+  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
+\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
+\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
+\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table}
 
@@
 \label{sec:discussion}
-%This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.
+This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.
+
+Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
+\begin{enumerate}
+\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
+\item Does the Bug report only the same ticket classified as Bug report for all the developers?
+\end{enumerate}
+
+How to proceed if looking for the responsability of a bug when only added lines are inserted?
+And we are talking about a bug report not a new feature, these kinds of cases use to be when a developer forgot check some case inside a function.
+[reference]
+\begin{enumerate}
+\item Is responsible the function where these lines are content?
+\item Is responsible the last commit that modify something in the function?
+\end{enumerate}
 
@@
 
-Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
-\begin{enumerate}
-\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
-\item Does the Bug report only the same ticket classified as Bug report for all the developers?
-\end{enumerate}
-
 \section{Conclusions and Future Work}
@@
 
-%In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases.
+In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases.
 Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug.
@@
 
-%In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized.
+In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized.
 In this way, with a larger population we may be able to find certain patterns that we are now omitting.
@@
 
-%In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage.
+In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage.
 The future work with the tool will focus on improving and automating the second stage.

### 2016-01-25 paperMSR.tex

@@
 \begin{abstract}
-\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit.
-However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects which present this characteristic.}
+To fix a bug in a certain software product, some parts of its source code are modified.
+At first glance, it could seem reasonable that the fixed bug was introduced by the previous modification of those same parts of the source code (the previous commit).
+In fact, many studies on bug seeding start with this assumption.
+However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug was introduced by other actions, such as an older modification, or a change in called APIs.
 
-\textbf{In this paper, in order to ascertain the validity of such a claim, we have conducted an observational study that involved bug notifications from a very active project such as OpenStack, in which their source code is continuously evolving.
-Our results are promising in indicating that exists bug fixed which were not introduced in the previous commit.}
+This paper tries to shed some light on this area, by analyzing the relationship of bug fixes with their previous commits.
+To this end, we conducted an observational study on bug reports, their fixes, and their correspoonding previous commits for OpenStack.
+Our results show that the mentioned asumption does not hold for a large fraction of the analyzed bugs, which were not introduced by their previous commit.
 \end{abstract}
@@
 \label{sec:resultsFS}
+
 We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
 The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
+
 \begin{table*}
@@
 \label{sec:discussion}
+
 This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.

### 2016-01-25 paperMSR.tex
added text and images

@@
 \label{sec:caseStudy}
+
+OpenStack was particularly of interest because of its continuously evolving due to its very active community.
+Although its short life, only five years, more than 5 thousand of resarchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project \footnote{\url{http://activity.openstack.org/dash/browser/}}.
+Futhermore, all history is saved and available in a version control system, being able to access to its issue tracking system \footnote{\url{https://launchpad.net/openstack}} and the source code review \footnote{\url{https://review.openstack.org/}}
+
+OpenStack is composed by 10 projects, but we only focused in the four more actives in the 2015, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack}
+\begin{table}[htb]
+\centering
+%\begin{center} {\footnotesize
+\caption{ Commits per Project in OpenStack}
+\label{tab:OpenStack}
+\begin{tabular}{lll}
+\toprule[0.3mm]%{\smallskip}
+  & All History \kern 1pc & Last Year (2015) \\\hline
+Nova    \kern 1pc & (184) 55\% & (115) 34\%  \\
+Fuel    \kern 1pc & (188) 76\% & (54) 22 \%  \\
+Netron  \kern 1pc & (188) 56\% & (116) 35\% \\
+Openstack-manuals \kern 1pc & (184) 55\% & (115) 34\%  \\
+Horizon \kern 1pc & (188) 76\% & (54) 22 \%  \\
+Cinder  \kern 1pc & (188) 56\% & (116) 35\% \\
+Keystone\kern 1pc & (184) 55\% & (115) 34\%  \\
+Heat    \kern 1pc & (188) 76\% & (54) 22 \%  \\
+Glance  \kern 1pc & (188) 56\% & (116) 35\% \\
+Tempest \kern 1pc & (188) 56\% & (116) 35\% \\
+\bottomrule[0.3mm]
+\end{tabular} %}
+%\end{center}
+\end{table}
+
+In this four projects we analized the relationship of bug fixes with their previous commits.
+In order to that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
+
 \subsection{Fist Stage: The Filtering}
 \label{sec:firstStage}
-OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
-The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.
+At this stage and with a tool's support developed to classify bug reports from other issues we distinguished the real bug reports in which afterwards analyzed the relation of the bug fixes with their previous commit.
 
-We use the tool to analyze 500 randomly tickets from the four principal repositories in OpenStack.
+We use the tool to analyze 459 randomly tickets from the four principal repositories in OpenStack.
 This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
@@
 
-The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit.
+The parameters analyzed for each ticket, to distinguish bug reports from others, were the title and the description of the issue report and the description of the fix commit.
 Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
@@
 
-Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.
+Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{Not Bug Report} and Group 3 as \textit{Undecided}.
+
+Furthermore, due to tool allows carry out a double bind analysis, three researchers, included me, used the tool to classify the 459 tickets.
+In 417 of the ticktes we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
+
+The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, and the number of tickets classifyed identically by two different researchers.
+
+\begin{table*}
+\centering
+%\begin{center} {\footnotesize
+\caption{ Classification statistics of each researcher}
+\label{tab:1}
+\begin{tabular}{lllll}
+\toprule[0.3mm]%{\smallskip}
+  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
+Researcher 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
+Researcher 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
+Researcher 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
+Total Concordance\kern 1pc & 209 & 74 & 6 & 292 \\
+\bottomrule[0.3mm]
+\end{tabular} %}
+%\end{center}
+\end{table*}
+
+With the methodology at this stage, the researchers obtained a concordance of 70\% in their classification, being able to distinguish 209 bug reports from 292 issues report using the tool.
 
@@
 \label{sec:tool}
-A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
-The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.
+The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not.
+The tool extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
+
+The image \ref{fig:1} shows a screenshot of anlayze tab, the principal feature of the tool where each research can comment and classify the tickets.
+
+\begin{figure*}
+\centering
+\includegraphics[height=15cm]{index.png}
+\caption{Screenshot of Analyze Tab}
+\label{fig:1}       % Give a unique label
+\end{figure*}
 
@@
 \label{sec:secondStage}
-In the second stage, we only focused on the analysis of \textit{Error} group, because this group contained the tickets that were bug reports.
-Discarding the \textit{Undecided} group in favour of the \textit{Error} group reduces the accuracy of the experiment due to the fact that some errors are being lost in \textit{Undecided} group.
-However the \textit{Undecided} group being only 16\% of the bugs under consideration makes us think that this fact does not
-affect the validity of the final results.
+In the second stage, we only focused on the analysis of \textit{Bug Report} group, because this group contained the tickets that we are sure were bug reports.
+Discarding the \textit{Undecided} group in favour of the \textit{Bug Report} group reduces the accuracy of the experiment due to the fact that some errors are being lost in \textit{Undecided} group.
+However the \textit{Undecided} group being only 6\% of the bugs under consideration makes us think that this fact does not affect the validity of the final results.
 
-We focused on analyzing characteristics of the commit such as the type of code, the number of previous commits involved, and the number of folders modified by the fixing commit to classify the bug report into one of three groups according to the responsibility of the previous commit:
+We focused on analyzing the previous commits involved in a bug fix, understanding previous commit as the last commit that touched the line that has been fixed in the bug fix commit.
+The image \ref{fig:2} shows a real example in which the commit 31f208423 injected the lines 715, 716 and 717 in the file.
+But in the line 716, this commit inserted a bug.
+According to the description of the commmit that fixed the bug, image \ref{fig:3}, the value in the variable of the line 716 had to be boolean, obtaining that the previous commit is responsible to cause the bug.
+\begin{figure*}
+\centering
+\includegraphics[height=2in, width=7in]{previouscommit.png}
+\caption{Example of previous commit. The 31f208423 is the previous commit in the line involved in the bug-fix}
+\label{fig:2}       % Give a unique label
+\end{figure*}
 
+\begin{figure}[htb]
+\centering
+\includegraphics[height=2.3cm]{gerritPrevCommit.png}
+\caption{Description of the bug-fix commit}
+\label{fig:3}       % Give a unique label
+\end{figure}
+
+We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups:
 \begin{enumerate}
@@
 \end{enumerate}
- We use therefore the \texttt{diff} command to display line\-by\-line difference between two files.
+
+For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and to be sure that the lines was inserted/modified in the previous commit, we have to analyze these lines in the commit parent of the previous commit.
+This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.
+
+The analisys was done manually, and we used \textit{git blame} to see all the previos commit in each line of a involved file.
+In \ref{fig:4}, we can show the steps following to discover the responsible of the bug.
+\begin{enumerate}
+  \item git checkout \textit{commmit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
+  \item git checkout \textit{parent of commmit that fix the bug}, git blame \textit{file involved}.
+In this step we can see all the previous commits involved in the different lines touched in the fix bug.
+  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can esure that the previous commit inserted these lines.
+\end{enumerate}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[height=2in, width=7in]{gitBlame.png}
+\caption{Process to discover the commit that caused the bug }
+\label{fig:4}       % Give a unique label
+\end{figure*}
+
+To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit.
 \texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system.
@@
 Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.
+
+After anlayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits were responsibles to cause the bug.
 \subsubsection{Discarting False Positives}
 \label{sec:discarting}
-We have to discart these previous commits that change the format, that add blank spaces and that change comments.
-¿What happen with the lines which are copied from others previous commits?
+We have to discart these previous commits that change the format, that add blank spaces, that change comments and that copied lines from the previous commit but.
+
+\begin{table}[htb]
+\begin{center} {\footnotesize
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{secondStage}
+\begin{tabular}{lcc}
+\toprule[0.3mm]
+  & \multicolumn{1}{c}{After } & \multicolumn{1}{c}{Before} \\
+  & \multicolumn{1}{c}{False Negative} & \multicolumn{1}{c}{False Negative} \\\hline
+\raisebox{1ex}{Responsible} & 152 & 152 \\[0ex]
+\raisebox{1ex}{Not responsible} & 154 & 114 \\[0ex]
+\raisebox{1ex}{Undecided} & 42 & 42 \\[0ex]
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table}
 
@@
 We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
-The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
-
-\begin{table*}
-\centering
-%\begin{center} {\footnotesize
-\caption{ Classification statistics of each developer}
-\label{tab:1}
-\begin{tabular}{lllll}
-\toprule[0.3mm]%{\smallskip}
-  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
-Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
-Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
-Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
-\bottomrule[0.3mm]
-\end{tabular} %}
-%\end{center}
-\end{table*}
-
-\begin{table*}
-\begin{center} {\footnotesize
-\caption{ Concordance between each developer in each repository}
-\label{tab:2}
-\begin{tabular}{llllll}
-\toprule[0.3mm]%{\smallskip}
-  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
-D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
-D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
-D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
-\bottomrule[0.3mm]
-\end{tabular} }
-\end{center}
-\end{table*}
+The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,
 
@@
 
-\begin{table}[htb]
-\begin{center} {\footnotesize
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{secondStage}
-\begin{tabular}{lcc}
-\toprule[0.3mm]
-  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
-  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
-\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
-\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
-\bottomrule[0.3mm]
-\end{tabular} }
-\end{center}
-\end{table}
-
-After discarding the noise caused by the false positives the results are:
+58 tickets with more than one previous commit and 
 \begin{table}[htb]
@@
 
-Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
+Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
 \begin{enumerate}
 \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
-\item Does the Bug report only the same ticket classified as Bug report for all the developers?
+\item Does the Bug report only the same ticket classified as Bug report for all the researchers?
 \end{enumerate}
@@
 How to proceed if looking for the responsability of a bug when only added lines are inserted?
-And we are talking about a bug report not a new feature, these kinds of cases use to be when a developer forgot check some case inside a function.
+And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
 [reference]

### 2016-01-26 paperMSR.tex
SOme changes

@@
 \label{sec:introduction}
-How to plan to apply the knowledge in a way that can benefit software engineers.
-What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
+%How to plan to apply the knowledge in a way that can benefit software engineers.
+%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
 
-In order to investigate if this assumption is valid, we formulate following research questions:
+%Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community.
+Software source code is affected by many changes, many of them due to failure of the software because of emergent bugs.
+Concepts such as bug seeding help us to find how and where a bug was inserted in the source code, and which is the responsible line for a bug~\cite{zimmermann2005mining}.
+
+%The current body of knowledge presents a wide collection of tools~\cite{kim2006automatic,fejzer2015supporting} that analyzes the code, and suggest where a potential bug can be found.
+Other publications describe how to find an error in the source code~\cite{yin2011fixes,zimmermann2006mining}.
+
+%These articles are based on an implicit assumption: that the line that contains the error was caused by the immediately previous commit as in~\cite{kim2008classifying}, where the authors introduce a new technique to classify changes into two main categories, buggy or clean.
+In fact they assume the last commit contains the line with the bug.
+Other authors~\cite{sliwerski2005changes} do not even mention who is the responsible, because they (implicitly) assume the fixed bugs were introduced in the previous commits.
+
+We refer to such \textit{previous commit} that the commit immediately before the bug fix.
+
+%While performing research on the topic, we did not find any empirical evidence that supported this assumption, so we decided to investigate its validity in the case of a large project, such as the OpenStack free/open source cloud computing infrastructure software.
+
+%In order to investigate if this assumption is valid, we formulate following research questions:
+In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
 \begin{itemize}
@@
 
-The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}.
-In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports.
-This problem is solved in Subsection~\ref{}, answering in this way RQ1.
-After having discriminated bug reports from those that are not, to answer the RQ2 we have calculated how many times the cause of the bug could be attributed to the previous commit (see Subsection~\ref{subsec:second}).
-Results are then shown in Section~\ref{}.
-Finally, we present a discussion, including the threats to validity, in Section~\ref{}.
+The remainder of this paper is structured as follows.
+First, we present the motivations that support our study,  explaining the current problem in section~\ref{sec:assumption}.
+Then, Section~\ref{sec:caseStudy} describes our empirical study in an open source project such as OpenStack, followed by the results in Section~\ref{sec:results}.
+Section~\ref{sec:discussion} discusses potential applications and improvements of our approach.
+Section~\ref{sec:threats} reports threats to validity.
+Finally, Section~\ref{sec:related} presenst the actual body of knowdeadge about who caused the bug and Section~\ref{sec:conclusions} concludes the article.
+
+\section{The Current Assumption}
+\label{sec:assumption}
+
+- Problem of missclassification\\
+- Problem of little empirical evidence about the hypotesis.\\
 
@@
 
+Each ticket has an id unique in Launchpad, which will be referred as \textit{n\_ticket}.
+Given its id, all information about the bug is publicly available in the issues tracking system\footnote{\url{https://bugs.launchpad.net/cinder/+bug/n_ticket}}.
+OpenStack uses Gerrit as code review system to see the evolution of each bug report\footnote{\url{https://review.openstack.org/ }}.
+Specifically we found the code review for each \textit{'n\_ticket'}\footnote{\url{https://review.openstack.org/#/c/n_review}}, where \textit{'n\_review'} is the review unique id for each \textit{'n\_ticket'}.
+In the code review all the information about the patchset that fixed the bug is shown.
+
 The parameters analyzed for each ticket, to distinguish bug reports from others, were the title and the description of the issue report and the description of the fix commit.
@@
 
+The researchers found main differences to extract data or to classify. In case of disagreement about the ticket classification among researchers, four criteria were used:
+\begin{itemize}
+    \item When there are only test files in the ticket, we classified it as note being a bug report.
+Test files in a ticket will not be analyzed, they are indispensables and used as testing method to determine whether the code is fit for use.
+Sometimes the developers inserted the bug only in the test files, in these cases the ticket was not considered as bug report because the software works as expected only failed the test.
+    \item When the title described a new feature, our criteria indicated that it was not a bug report.
+New features are not considered bug reports, because there is no failure.
+The optimization, deletion of a dead code or the implementation of new characteristics are included in this criteria.
+    \item When the title described the program as not working as expected, our criteria indicated that it was a bug report.
+Sometimes the bug is not in a main function which prevents \texttt{Cinder} from working, because a developer has considered it an important bug, although not relatively important.
+But it is not working as he/she expected.
+    \item When the title described that updates were required, our criteria indicated that it was a bug report.
+We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
+\end{itemize}
+
+Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue.
+In this case, the ticket was classified into the \textit{Undecided} group.
+
 Furthermore, due to tool allows carry out a double bind analysis, three researchers, included me, used the tool to classify the 459 tickets.
@@
 
-\begin{table*}
-\centering
-%\begin{center} {\footnotesize
-\caption{ Classification statistics of each researcher}
-\label{tab:1}
-\begin{tabular}{lllll}
+\begin{table*}[htb]
+\begin{center} {\footnotesize
+\caption{ Concordance between each developer in each repository}
+\label{tab:3}
+\begin{tabular}{llllll}
 \toprule[0.3mm]%{\smallskip}
-  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
-Researcher 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
-Researcher 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
-Researcher 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
-Total Concordance\kern 1pc & 209 & 74 & 6 & 292 \\
+  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
+D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
+D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
+D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
 \bottomrule[0.3mm]
-\end{tabular} %}
-%\end{center}
+\end{tabular} }
+\end{center}
 \end{table*}
+
+The table ~\ref{tab:3} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
+The concordance between the developers could be higer if they were expert in the project.
 
@@
 
-\subsubsection{The Tool}
+\subsubsection{BugTracking: The tool used}
 \label{sec:tool}
 The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not.
-The tool extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
+The tool is available at\footnote{\url{bugtracking.libresoft.es}} and extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
+The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
+\begin{enumerate}
+  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze.
+Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
+  \item Tab Analyze: Is the Tab showed in \ref{fig:1} where the user select/insert an identifyer of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
+  \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
+  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
+\end{enumerate}
 
@@
 
-We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups:
+At this stage, we got a list with all the previous commits, which could be where the bug was introduced.
+We  identifyed a total of 348 previous commits which can be responsible for inserting the line with the bug.
+When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
+After the analysis the responsible can be only one of them, more than one or none.
+
+We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups, according to the responsability of the previous commit in the bug fix:
 \begin{enumerate}
-  \item It is responsible,
-  \item It is not responsible,
-  \item Undecided.
+  \item It is responsible, when we are sure that the commit inserted the line with the bug.
+  \item It is not responsible, when we are sure that the commit dind't insert the line with the bug.
+  \item Undecided, when we cannot be sure if the commit is responsible due to our few knowleadge about the project or when the bug fix only added lines, complicating the analysis.
 \end{enumerate}
@@
 
-To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit.
+%To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit.
 \texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system.
@@
 
-At this stage, we got a list with all the previous commits, which could be where the bug was introduced.
-We have to identify those previous commits responsible for inserting the line with the bug.
-When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, after the analysis the responsible can be only one of them or maybe two, in fact sometimes all of them were responsible.
-Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.
+After analayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits inserted the bug.
+This expecific project, which is continuosly evolving, presents some cases in which the bug was introduced by other actions.
+A clear example is the changes in called APIs, after the addition of a new feauture the called API fails, due to it requires an extra argument, but in the API there is not any bug.
 
-After anlayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits were responsibles to cause the bug.
+Other example is shows in the commit log of a bug fix \ref{fig:5}, the name of a variable changed in the new version causing a failure.
+This change due to the new requirements in the version doesn't implicate that the previous commit was who inserted the bug, because until the new version the system doesn't fail.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[height=2.3cm]{UpdateFixBug.png}
+\caption{Description of the bug-fix commit}
+\label{fig:5}       % Give a unique label
+\end{figure}
+
 \subsubsection{Discarting False Positives}
 \label{sec:discarting}
-We have to discart these previous commits that change the format, that add blank spaces, that change comments and that copied lines from the previous commit but.
+The classification of the previous commits according to its responsability has some noise that we had to delete.
+These previous commits that changed the format, added blank lines, changed comments or copied lines from the previous commit were discarted due to they were not responsibles for cause the bug.
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Fist Stage}
+\label{sec:resultsFS}
+We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
+The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,
+
+\begin{table*}
+\centering
+%\begin{center} {\footnotesize
+\caption{ Classification statistics of each researcher}
+\label{tab:1}
+\begin{tabular}{lllll}
+\toprule[0.3mm]%{\smallskip}
+  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
+Researcher 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
+Researcher 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
+Researcher 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
+Total Concordance\kern 1pc & 209 & 74 & 6 & 292 \\
+\bottomrule[0.3mm]
+\end{tabular} %}
+%\end{center}
+\end{table*}
+
+\subsection{Second Stage}
+\label{sec:resultsSS}
 
@@
 \toprule[0.3mm]
-  & \multicolumn{1}{c}{After } & \multicolumn{1}{c}{Before} \\
+  & \multicolumn{1}{c}{After} & \multicolumn{1}{c}{Before} \\
   & \multicolumn{1}{c}{False Negative} & \multicolumn{1}{c}{False Negative} \\\hline
@@
 
-\section{Results}
-\label{sec:results}
-
-\subsection{Fist Stage}
-\label{sec:resultsFS}
-
-We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
-The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,
-
-\subsection{Second Stage}
-\label{sec:resultsSS}
-
-58 tickets with more than one previous commit and 
+58 tickets with more than one previous commit and 131 with only one previous commit
 \begin{table}[htb]
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
-\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
-\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
+\raisebox{1ex}{Responsible} & 65\% & 86\% \\[0ex]
+\raisebox{1ex}{Not responsible} & 30\% & 82\%\\[0ex]
+\raisebox{1ex}{Undecided} & 36\% & 11\%\\[0ex]
 \bottomrule[0.3mm]
@@
 
-\subsection{Threats to validity}
+\section{Threats to validity}
 \label{sec:threats}
@@
 
-\section{Conclusions and Future Work}
+\section{Related Work}
+\label{sec:related}
+First SZZ\\
+Second Improvement of SZZ\\
+Then SZZ revisited\\
+Then Buginnings\\
+Finally our idea.
+
+\section{Conclusions}
 \label{sec:conclusions}
-
-In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases.
-Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug.
-Thus, the articles based on SZZ algorithm may be based on a wrong assumption.
-However, a larger number of tickets has to be studied to ascertain that our findings can be generalized.
-Our idea is contribute with this study in the knowledge about the responsibility practiced by the previous commit in a bug, helping to the software engineering community in the code review process.
-FIXME: aclarar esta frase que no me queda clara: Our idea is propose a reinterpretation in the responsibility practiced by the previous commit in a bug.
-
-In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized.
-In this way, with a larger population we may be able to find certain patterns that we are now omitting.
-Furthermore, we extend this study to other projects to ascertain that what we have found occurs regardless of the project analyzed, because the OpenStack may be a special project, where the code is evolving continuously.
-In fact, we can access a huge database of other projects such as Eclipse or Mozilla that will allow us analyze this assumption, and where we will use statistical analysis to compare the results obtained in the different projects.
-
-In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage.
-The future work with the tool will focus on improving and automating the second stage.
 
@@
 \section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+We thank the two phd students, Dorealda Dalipaj and Nelson Sekitoleko, that participated differentiating Bug report from the others.
+Also, we thank Bitergia \footnote{\url{http://bitergia.com/}} to explain its available database of OpenStack.
+Finally,thanks the Spanish Goverment because all authors are funded in part by it, through project TIN2014-59400-R.
 
+\nocite{*}
 %

### 2016-01-27 paperMSR.tex
Added Results and Methodology

@@
 \label{sec:introduction}
+- Codigo que era correcto deja de serlo
+- En el momento en el que se introdujo fue un error
+- ¿Código erroneo o hubo otro cambio?
+- Díficil conocer el codigo en todo el contexto 
 %How to plan to apply the knowledge in a way that can benefit software engineers.
@@
 \begin{itemize}
-    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-    \item RQ2:  How often is the bug caused in the previous commit?
+    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
+     \item RQ1:  How I can know that a change was done to fix a bug in the source code? How I can identify them?
+    %\item RQ2:  How often is the bug caused in the previous commit?
+     \item RQ2:  In which cases the previous commit/s are responsible to cause the bug?
 \end{itemize}
 
+\begin{figure*}
+\centering
+\includegraphics[height=2in, width=7in]{responsible.png}
+\caption{Example of previous commit. The 31f208423 is the previous commit in the line involved in the bug-fix}
+\label{fig:2}       % Give a unique label
+\end{figure*}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[height=2.4cm]{gerritPrevCommit.png}
+\caption{Description of the bug-fix commit when the previous commit caused the bug}
+\label{fig:3}       % Give a unique label
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[height=2.4cm]{UpdateFixBug.png}
+\caption{Description of the bug-fix commit when the previous commit dind't cause the bug}
+\label{fig:5}       % Give a unique label
+\end{figure}
+
 The remainder of this paper is structured as follows.
-First, we present the motivations that support our study,  explaining the current problem in section~\ref{sec:assumption}.
-Then, Section~\ref{sec:caseStudy} describes our empirical study in an open source project such as OpenStack, followed by the results in Section~\ref{sec:results}.
+First, we present the motivations that support our study,  explaining the current body of knowleadge in section~\ref{sec:related}.
+Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applaying our approach to OpenStack in Section~\ref{sec:results}.
 Section~\ref{sec:discussion} discusses potential applications and improvements of our approach.
 Section~\ref{sec:threats} reports threats to validity.
-Finally, Section~\ref{sec:related} presenst the actual body of knowdeadge about who caused the bug and Section~\ref{sec:conclusions} concludes the article.
+Finally, Section~\ref{sec:conclusions} concludes the article.
 
-\section{The Current Assumption}
-\label{sec:assumption}
+\section{Related Work}
+\label{sec:related}
+First SZZ\\
+Second Improvement of SZZ\\
+Then SZZ revisited\\
+Then Buginnings\\
+Finally our idea.
 
-- Problem of missclassification\\
-- Problem of little empirical evidence about the hypotesis.\\
+\section{Methodology}
+\label{sec:methodology}
+%We present our approach to identify how and where a bug was inserted into the source code, causing a later fix. 
+We extract all the data necesary to analyze when the bug was inserted from the issue tracking system and the code review system used by the project we are analyzing.
+OpenStack uses Launchpad\footnote{\url{https://launchpad.net/openstack}} and Gerrit\footnote{\url{https://review.openstack.org/}}.
 
-\section{The Case of Study}
-\label{sec:caseStudy}
+The Launchapd of each project works with issues reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
+But, in our study we are only interested in those tickets that describe a bug report and, in addition, have been closed with a merged in the code source to fix the bug.
+In this bug reports we can find a comment with the link of Gerrit where the bug was fixed.
+Is in Gerrit where we can see all the patchsets proposed and the comments done by the reviewers.
 
+\subsection{Fist Stage: The Filtering}
+\label{sec:firstStage}
+In our approach, first of all we must identifying which of those issues extracted from Launchapd are bug reports.
+But, this is not a trivial task and we performed this identification using a web tool\footnote{\url{bugtracking.libresoft.es}} development to provide the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
+The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
+
+During the identification of the issues we have to take into account the next parameters for each ticket, the title and the description of the issue report and the description of the fix commit.
+Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
+Each ticket was then categorized into one of three following groups.
+\begin{enumerate}
+  \item The ticket describes a bug report.
+  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
+  \item The ticket presents a vague description and cannot be classified without doubts.
+\end{enumerate}
+
+Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{Not Bug Report} and Group 3 as \textit{Undecided}.
+
+As result of analyze the tickets, main differences extracting data and to classifying tickets were found. So, we agree to follow the next four criteria: 
+\begin{itemize}
+    \item When there are only test files in the ticket, we classified it as note being a bug report.
+Test files in a ticket will not be analyzed, they are indispensables and used as testing method to determine whether the code is fit for use.
+Sometimes the developers inserted the bug only in the test files, in these cases the ticket was not considered as bug report because the software works as expected only failed the test.
+    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, our criteria indicated that it was not a bug report because there is no failure. 
+    \item When the title described the program as not working as expected, our criteria indicated that it was a bug report. 
+    \item When the title described that updates were required, our criteria indicated that it was a bug report.
+We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
+\end{itemize}
+
+Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue.
+In this case, the ticket was classified into the \textit{Undecided} group.
+\subsection{Second Stage: Responsability of Previous Commit}
+\label{sec:secondStage}
+The next part is focusing on analyzing the previous commit in the \textit{Bug Report} group.
+For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and be sure that the lines was inserted/modified in the previous commit.
+This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.
+
+The analisys was done manually, and we used \textit{git blame} to see all the previos commit in each line of a involved file.
+Also, we used \textit{diff} to see all the differences between two files, in our case, the file is going to be the same but in different moment inside the control version system used.
+
+Te procedure following in each file involved in a fix bug is show in the figure \ref{fig:4}, and describes below;
+\begin{enumerate}
+  \item git checkout \textit{commmit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
+  \item git checkout \textit{parent of commmit that fix the bug}, git blame \textit{file involved}.
+In this step we can see all the previous commits involved in the different lines touched in the fix bug.
+  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can esure that the previous commit inserted these lines.
+\end{enumerate}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[height=2in, width=7in]{noResponsible.png}
+\caption{Process to discover the commit that caused the bug }
+\label{fig:4}       % Give a unique label
+\end{figure*}
+
+Finally we need to discard some noise presents in our final resulst according to the responsability of the previous commit inserting the bug in the code source.
+Due to they were not responsibles for cause the bug, we delete those previous commit which presents the following criteria;
+\begin{itemize}
+    \item Blank lines
+    \item Format changes
+    \item Copied lines
+    \item Changes in the comment.
+    \item Updatings in the version of a file. 
+\end{itemize}
+%- Que utilizo 
+%- Donde se encuentra
+%- Como los analizo (Tool)
+%- Que tengo en cuenta en el análisis de los tickets....
+%- Como resultado de analizar los tickets encuentro ...
+%- Despues me interesa los commits anteriores
+%- Que realizo un análisis manual
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+We validate our methodology anlayzing 459 tickets in OpenStack.
 OpenStack was particularly of interest because of its continuously evolving due to its very active community.
@@
   & All History \kern 1pc & Last Year (2015) \\\hline
-Nova    \kern 1pc & (184) 55\% & (115) 34\%  \\
-Fuel    \kern 1pc & (188) 76\% & (54) 22 \%  \\
-Netron  \kern 1pc & (188) 56\% & (116) 35\% \\
-Openstack-manuals \kern 1pc & (184) 55\% & (115) 34\%  \\
-Horizon \kern 1pc & (188) 76\% & (54) 22 \%  \\
-Cinder  \kern 1pc & (188) 56\% & (116) 35\% \\
-Keystone\kern 1pc & (184) 55\% & (115) 34\%  \\
-Heat    \kern 1pc & (188) 76\% & (54) 22 \%  \\
-Glance  \kern 1pc & (188) 56\% & (116) 35\% \\
-Tempest \kern 1pc & (188) 56\% & (116) 35\% \\
+Nova    \kern 1pc & - & - \\
+Fuel    \kern 1pc & - & -  \\
+Netron  \kern 1pc & - & - \\
+Openstack-manuals \kern 1pc & - & -  \\
+Horizon \kern 1pc & - & -  \\
+Cinder  \kern 1pc & - & - \\
+Keystone\kern 1pc & - & -  \\
+Heat    \kern 1pc & - & -  \\
+Glance  \kern 1pc & - & - \\
+Tempest \kern 1pc & - & - \\
 \bottomrule[0.3mm]
@@
 In this four projects we analized the relationship of bug fixes with their previous commits.
-In order to that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
+In order to identify the moment in which the bug was injected into the source code.
+The first stage we did automatically using the tool and a double bind between three researchers, three PhD student  included me.
+The second stage was done manually and only me was involved analizing this relationship.
+%that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
 
-\subsection{Fist Stage: The Filtering}
-\label{sec:firstStage}
-At this stage and with a tool's support developed to classify bug reports from other issues we distinguished the real bug reports in which afterwards analyzed the relation of the bug fixes with their previous commit.
+\section{Results}
+\label{sec:results}
 
-We use the tool to analyze 459 randomly tickets from the four principal repositories in OpenStack.
+We extracted a total of 459 different tickets from the Launchpad of the four principal projects in OpenStack, 125 tickets from Nova, 125 tickets from cinder, 125 tickets from Horizon and 84 tickets from Neutron.
+These tickets first, were analized to identify those ones which were real bug reports.
+And secondly, each file was analyzed to obtain which previous commit inserted the bug causing the failure of the system and reporting the bug report.
+
+\subsection{Fist Stage}
+\label{sec:resultsFS}
+
+We classify a total of 459 tickets using the tool.
+In 417 of the ticktes, we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
+
+The table \ref{tab:2} shows the percentage of each researcher after analyzing the tickets, and the number of tickets classifyed identically by two different researchers.
+Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly differents with a higher number of tickets classifyed as Bug Report.
+
+Finally, the researchers identifyed in the same way 292 tickets, that is, their results matched in a 70\% of the cases.
+Obtaining 209 tickets classifyed as Bug report, 74 tickets classifyed as Not Bug Report and 9 tickets classifyed as Undecided.
+
+\begin{table}
+\centering
+%\begin{center} {\footnotesize
+\caption{ Classification statistics of each researcher}
+\label{tab:2}
+\begin{tabular}{lllll}
+\toprule[0.3mm]%{\smallskip}
+  & Bug Report\kern 1pc & Not Bug Report & Undecided & Total \\\hline
+R1  & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
+R2  & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
+R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
+Finally & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
+\bottomrule[0.3mm]
+\end{tabular} %}
+%\end{center}
+\end{table}
+
+Also we had measured the concordance in the classification of each developer according to the project analized.
+The table \ref{tab:3} shows that the concordante got between all the three research was very similar, around a 70\%.
+Furthermore, the concordance form each researcher with the rest alwas was up to 60\%.
+
+\begin{table}[htb]
+\begin{center} {\footnotesize
+\caption{ Concordance between each developer in each repository}
+\label{tab:3}
+\begin{tabular}{llllll}
+\toprule[0.3mm]%{\smallskip}
+  & Nova & Cinder & Horizon & Neutron & Total\\\hline
+R1 and R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
+R1 and R3   &  -        & (46) 73\%  & (48) 76\% & (26)62\% & 71 \% \\
+R2 and R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table}
+
+%The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, and the number of
+%\subsection{Fist Stage: The Filtering}
+%\label{sec:firstStage}
+%At this stage and with a tool's support developed to classify bug reports from other issues we distinguished the real bug reports in which afterwards analyzed the relation of the bug fixes with their previous commit.
+
+%We use the tool to analyze 459 randomly tickets from the four principal repositories in OpenStack.
 This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
@@
 
-Each ticket has an id unique in Launchpad, which will be referred as \textit{n\_ticket}.
+%Each ticket has an id unique in Launchpad, which will be referred as \textit{n\_ticket}.
 Given its id, all information about the bug is publicly available in the issues tracking system\footnote{\url{https://bugs.launchpad.net/cinder/+bug/n_ticket}}.
@@
 
-The parameters analyzed for each ticket, to distinguish bug reports from others, were the title and the description of the issue report and the description of the fix commit.
-Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
-Each ticket was then categorized into one of three following groups.
-\begin{enumerate}
-  \item The ticket describes a bug report.
-  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
-  \item The ticket presents a vague description and cannot be classified without doubts.
-\end{enumerate}
-
-Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{Not Bug Report} and Group 3 as \textit{Undecided}.
-
-The researchers found main differences to extract data or to classify. In case of disagreement about the ticket classification among researchers, four criteria were used:
-\begin{itemize}
-    \item When there are only test files in the ticket, we classified it as note being a bug report.
-Test files in a ticket will not be analyzed, they are indispensables and used as testing method to determine whether the code is fit for use.
-Sometimes the developers inserted the bug only in the test files, in these cases the ticket was not considered as bug report because the software works as expected only failed the test.
-    \item When the title described a new feature, our criteria indicated that it was not a bug report.
-New features are not considered bug reports, because there is no failure.
-The optimization, deletion of a dead code or the implementation of new characteristics are included in this criteria.
-    \item When the title described the program as not working as expected, our criteria indicated that it was a bug report.
-Sometimes the bug is not in a main function which prevents \texttt{Cinder} from working, because a developer has considered it an important bug, although not relatively important.
-But it is not working as he/she expected.
-    \item When the title described that updates were required, our criteria indicated that it was a bug report.
-We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
-\end{itemize}
-
-Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue.
-In this case, the ticket was classified into the \textit{Undecided} group.
-
-Furthermore, due to tool allows carry out a double bind analysis, three researchers, included me, used the tool to classify the 459 tickets.
+%Furthermore, due to tool allows carry out a double bind analysis, three researchers, included me, used the tool to classify the 459 tickets.
 In 417 of the ticktes we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
 
-The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, and the number of tickets classifyed identically by two different researchers.
-
-\begin{table*}[htb]
-\begin{center} {\footnotesize
-\caption{ Concordance between each developer in each repository}
-\label{tab:3}
-\begin{tabular}{llllll}
-\toprule[0.3mm]%{\smallskip}
-  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
-D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
-D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
-D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
-\bottomrule[0.3mm]
-\end{tabular} }
-\end{center}
-\end{table*}
-
-The table ~\ref{tab:3} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
+%The table ~\ref{tab:3} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
 The concordance between the developers could be higer if they were expert in the project.
 
-With the methodology at this stage, the researchers obtained a concordance of 70\% in their classification, being able to distinguish 209 bug reports from 292 issues report using the tool.
+%With the methodology at this stage, the researchers obtained a concordance of 70\% in their classification, being able to distinguish 209 bug reports from 292 issues report using the tool.
 
-\subsubsection{BugTracking: The tool used}
-\label{sec:tool}
-The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not.
+%\subsubsection{BugTracking: The tool used}
+%\label{sec:tool}
+%The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not.
 The tool is available at\footnote{\url{bugtracking.libresoft.es}} and extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
-The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
-\begin{enumerate}
-  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze.
-Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
-  \item Tab Analyze: Is the Tab showed in \ref{fig:1} where the user select/insert an identifyer of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
-  \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
-  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
-\end{enumerate}
+%The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
 
-The image \ref{fig:1} shows a screenshot of anlayze tab, the principal feature of the tool where each research can comment and classify the tickets.
+%\begin{figure*}
+%\centering
+%\includegraphics[height=15cm]{index.png}
+%\caption{Screenshot of Analyze Tab}
+%\label{fig:1}       % Give a unique label
+%\end{figure*}
 
-\begin{figure*}
-\centering
-\includegraphics[height=15cm]{index.png}
-\caption{Screenshot of Analyze Tab}
-\label{fig:1}       % Give a unique label
-\end{figure*}
-
-\subsection{Second Stage: Responsability of Previous Commit}
-\label{sec:secondStage}
-In the second stage, we only focused on the analysis of \textit{Bug Report} group, because this group contained the tickets that we are sure were bug reports.
+%\subsection{Second Stage: Responsability of Previous Commit}
+%\label{sec:secondStage}
+%In the second stage, we only focused on the analysis of \textit{Bug Report} group, because this group contained the tickets that we are sure were bug reports.
 Discarding the \textit{Undecided} group in favour of the \textit{Bug Report} group reduces the accuracy of the experiment due to the fact that some errors are being lost in \textit{Undecided} group.
@@
 
-We focused on analyzing the previous commits involved in a bug fix, understanding previous commit as the last commit that touched the line that has been fixed in the bug fix commit.
+%We focused on analyzing the previous commits involved in a bug fix, understanding previous commit as the last commit that touched the line that has been fixed in the bug fix commit.
 The image \ref{fig:2} shows a real example in which the commit 31f208423 injected the lines 715, 716 and 717 in the file.
@@
 According to the description of the commmit that fixed the bug, image \ref{fig:3}, the value in the variable of the line 716 had to be boolean, obtaining that the previous commit is responsible to cause the bug.
-\begin{figure*}
-\centering
-\includegraphics[height=2in, width=7in]{previouscommit.png}
-\caption{Example of previous commit. The 31f208423 is the previous commit in the line involved in the bug-fix}
-\label{fig:2}       % Give a unique label
-\end{figure*}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[height=2.3cm]{gerritPrevCommit.png}
-\caption{Description of the bug-fix commit}
-\label{fig:3}       % Give a unique label
-\end{figure}
-
-At this stage, we got a list with all the previous commits, which could be where the bug was introduced.
+%At this stage, we got a list with all the previous commits, which could be where the bug was introduced.
 We  identifyed a total of 348 previous commits which can be responsible for inserting the line with the bug.
@@
 
-We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups, according to the responsability of the previous commit in the bug fix:
-\begin{enumerate}
-  \item It is responsible, when we are sure that the commit inserted the line with the bug.
-  \item It is not responsible, when we are sure that the commit dind't insert the line with the bug.
-  \item Undecided, when we cannot be sure if the commit is responsible due to our few knowleadge about the project or when the bug fix only added lines, complicating the analysis.
-\end{enumerate}
-
-For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and to be sure that the lines was inserted/modified in the previous commit, we have to analyze these lines in the commit parent of the previous commit.
-This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.
-
-The analisys was done manually, and we used \textit{git blame} to see all the previos commit in each line of a involved file.
-In \ref{fig:4}, we can show the steps following to discover the responsible of the bug.
-\begin{enumerate}
-  \item git checkout \textit{commmit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
-  \item git checkout \textit{parent of commmit that fix the bug}, git blame \textit{file involved}.
-In this step we can see all the previous commits involved in the different lines touched in the fix bug.
-  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can esure that the previous commit inserted these lines.
-\end{enumerate}
-
-\begin{figure*}[htb]
-\centering
-\includegraphics[height=2in, width=7in]{gitBlame.png}
-\caption{Process to discover the commit that caused the bug }
-\label{fig:4}       % Give a unique label
-\end{figure*}
+%We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups, according to the responsability of the previous commit in the bug fix:
+%\begin{enumerate}
+%  \item It is responsible, when we are sure that the commit inserted the line with the bug.
+%  \item It is not responsible, when we are sure that the commit dind't insert the line with the bug.
+%  \item Undecided, when we cannot be sure if the commit is responsible due to our few knowleadge about the project or when the bug fix only added lines, complicating the analysis.
+%\end{enumerate}
 
@@
 
-After analayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits inserted the bug.
+%After analayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits inserted the bug.
 This expecific project, which is continuosly evolving, presents some cases in which the bug was introduced by other actions.
@@
 
-Other example is shows in the commit log of a bug fix \ref{fig:5}, the name of a variable changed in the new version causing a failure.
+%Other example is shows in the commit log of a bug fix \ref{fig:5}, the name of a variable changed in the new version causing a failure.
 This change due to the new requirements in the version doesn't implicate that the previous commit was who inserted the bug, because until the new version the system doesn't fail.
 
-\begin{figure}[htb]
-\centering
-\includegraphics[height=2.3cm]{UpdateFixBug.png}
-\caption{Description of the bug-fix commit}
-\label{fig:5}       % Give a unique label
-\end{figure}
+%\section{Results}
+%\label{sec:results}
 
-\subsubsection{Discarting False Positives}
-\label{sec:discarting}
-The classification of the previous commits according to its responsability has some noise that we had to delete.
-These previous commits that changed the format, added blank lines, changed comments or copied lines from the previous commit were discarted due to they were not responsibles for cause the bug.
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Fist Stage}
-\label{sec:resultsFS}
-We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
+%\subsection{Fist Stage}
+%\label{sec:resultsFS}
+%We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
 The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,
-
-\begin{table*}
-\centering
-%\begin{center} {\footnotesize
-\caption{ Classification statistics of each researcher}
-\label{tab:1}
-\begin{tabular}{lllll}
-\toprule[0.3mm]%{\smallskip}
-  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
-Researcher 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
-Researcher 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
-Researcher 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
-Total Concordance\kern 1pc & 209 & 74 & 6 & 292 \\
-\bottomrule[0.3mm]
-\end{tabular} %}
-%\end{center}
-\end{table*}
 
@@
 
+At this stage, we analyzed the 209 we got a list with all the previous commits and we were be able to classifyed the previous commit/s as Responsible, Not Responsible or Undecided, taken into account that the bug could be inserted in different lines of different commits, but not everyone had to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
+In fact, the responsible can be only one of them, more than one or maybe none.
+
+We identifyed a total of 348 previous commits which can be responsible for inserting the line containing the bug.
+After analizing the Bug Reports and their previous commits and discarded 40 of them because were noise, Table \ref{tab:responsability}, we got that 152 previous commit were responsibles to cause the bug whereas 114 previous commit had not any responsability in the failure of the system, and only in 42 previous commits we were unable to identify the cause of the bug.
+
 \begin{table}[htb]
 \begin{center} {\footnotesize
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{secondStage}
+\caption{ Responsability of each previous commit before and after deleting the noise in the results}
+\label{tab:responsability}
 \begin{tabular}{lcc}
 \toprule[0.3mm]
-  & \multicolumn{1}{c}{After} & \multicolumn{1}{c}{Before} \\
-  & \multicolumn{1}{c}{False Negative} & \multicolumn{1}{c}{False Negative} \\\hline
+  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
+  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
 \raisebox{1ex}{Responsible} & 152 & 152 \\[0ex]
@@
 
-58 tickets with more than one previous commit and 131 with only one previous commit
+Futhermore, focusing on how many previous commits presented each Bug Report, we obtained that 131 had one previous commit implicated, whereas 58 had more than one previous commit implicated in their file/s.
+According to Table \ref{tab:secondStage}, from the 131, we obtained that 65 of them inserted the bug, but 30 of them were not responsibles in the failure of the system.
+And from the 58 which had more than one previous commits, we obtained in total 189 previous commit, where 86 of them were respnsibles and 82 were not responsibles.
+%Probably, the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
+After the analysis the responsible can be only one of them, more than one or maybe none.
+
 \begin{table}[htb]
@@
 \caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{secondStage}
+\label{tab:secondStage}
 \begin{tabular}{lcc}
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Responsible} & 65\% & 86\% \\[0ex]
-\raisebox{1ex}{Not responsible} & 30\% & 82\%\\[0ex]
-\raisebox{1ex}{Undecided} & 36\% & 11\%\\[0ex]
+\raisebox{1ex}{Responsible}     & 65 & 86 \\[0ex]
+\raisebox{1ex}{Not responsible} & 30 & 82 \\[0ex]
+\raisebox{1ex}{Undecided}       & 36 & 11 \\[0ex]
 \bottomrule[0.3mm]
@@
 
+Also, we looked the distribution of the previous commit in each Bug Report, Table \ref{tab:secondStage2}, we observed that the most commun distribuion in the relationship between previous commit and bug report is one previous commit per Bug Report, following by the second commun distribution, two previous commit per Bug Report.
+\begin{table*}[htb]
+\begin{center} {\footnotesize
+\caption{ Distribution of number of previous commit per Bug Report in each project}
+\label{tab:secondStage2}
+\begin{tabular}{lccccc}
+\toprule[0.3mm]
+  & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
+  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
+\raisebox{1ex}{Neutron} & 11 & 3 & 2 & 2 & 0 \\[0ex]
+\raisebox{1ex}{Horizon} & 39 & 8 & 3 & 2 & 4 \\[0ex]
+\raisebox{1ex}{Nova} & 44 & 5 & 2 & 4 & 4 \\[0ex]
+\raisebox{1ex}{Cinder} & 37 & 9 & 6 & 2 & 2\\[0ex]
+\raisebox{1ex}{Total} & 131 & 25 & 13 & 10 & 10\\[0ex]
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table*}
+
+Finally we wanted to know the responsability preactised by each previous commit in the failure of a system, in other words, we were interested in analize from those cases where exists more than one previous commit, how many of them inserted the bug in the code source, Table \ref{tab:secondStage3}.
+We obtained that in 8 Bug Reports all the previous commits were responsibles, in 30 Bug reports at least one of their previous commit caused the bug and in 11 bug report none of their previous commits inserted the bug.
+\begin{table*}[htb]
+\begin{center} {\footnotesize
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{tab:secondStage3}
+\begin{tabular}{lccccc}
+\toprule[0.3mm]
+   & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous} & \multicolumn{1}{c}{Total}\\
+  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
+\raisebox{1ex}{All Responsible}          & 4 & 3 & 0 & 1 & 8\\[0ex]
+\raisebox{1ex}{At least one responsible} & 9 & 7 & 5 & 9 & 30\\[0ex]
+\raisebox{1ex}{None Responsible}         & 4 & 2 & 4 & 1 & 11\\[0ex]
+\raisebox{1ex}{Undecided}                & 1 & 0 & 1 & 0 & 2\\[0ex]
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table*}
+
 \section{Discussion}
@@
 
-This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.
-
+- Como se responden las RQ1 y RQ2
+- No todos los casos son tan claros como los mostrados en los ejemplos ....
+- Casuistica del common juidment
+- Hemos sido conservadores
+-Hemos utilizado la herramienta porque es un proceso complicado
 Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
@@
 
-\section{Related Work}
-\label{sec:related}
-First SZZ\\
-Second Improvement of SZZ\\
-Then SZZ revisited\\
-Then Buginnings\\
-Finally our idea.
-
 \section{Conclusions}

### 2016-01-27 paperMSR.tex
Deleted some comments
added a little of the Introduction

@@
 \label{sec:introduction}
-- Codigo que era correcto deja de serlo
-- En el momento en el que se introdujo fue un error
-- ¿Código erroneo o hubo otro cambio?
-- Díficil conocer el codigo en todo el contexto 
+
+When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line/s that contains the bug in the source code.
+It seems reasonable to assign the responsability to insert the bug to the previous moodification of this/those lines, \textit{The previous commit}.
+But in fact, find when and where a bug was injected into the souce code is not a trivial task.
+
+In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or even we can find this assumption in tools that prevent dor future bugs; \textit{" We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
+We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating when the line containing the bug was inserted into the code.
+
+We based on some reasons to suppose that the previous commit doesn't insert the bug.
+Our main reason is that in a project wich is evolving continuously and where many different developers are working on, the code that before was correct, now can be buggy.
+Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
+As a result, the software fails at this line.
+But in fact, the previous commit which wrote the called API is not responsible, due to the line did't contain any bug at the moment in which was written.
+
+%- Codigo que era correcto deja de serlo
+%- En el momento en el que se introdujo fue un error
+%- ¿Código erroneo o hubo otro cambio?
+%- Díficil conocer el codigo en todo el contexto
+
+With our appproach we can identify which are the changes that introduced a bug, and this coul be useful to improve the accuracy of those tools developed to prevent bugs.
+Also, the software developers stand to benefit from identifying where the bug was inserted, improve their methodology.
 %How to plan to apply the knowledge in a way that can benefit software engineers.
@@
 
-%Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community.
-Software source code is affected by many changes, many of them due to failure of the software because of emergent bugs.
-Concepts such as bug seeding help us to find how and where a bug was inserted in the source code, and which is the responsible line for a bug~\cite{zimmermann2005mining}.
-
-%The current body of knowledge presents a wide collection of tools~\cite{kim2006automatic,fejzer2015supporting} that analyzes the code, and suggest where a potential bug can be found.
-Other publications describe how to find an error in the source code~\cite{yin2011fixes,zimmermann2006mining}.
-
-%These articles are based on an implicit assumption: that the line that contains the error was caused by the immediately previous commit as in~\cite{kim2008classifying}, where the authors introduce a new technique to classify changes into two main categories, buggy or clean.
-In fact they assume the last commit contains the line with the bug.
-Other authors~\cite{sliwerski2005changes} do not even mention who is the responsible, because they (implicitly) assume the fixed bugs were introduced in the previous commits.
-
-We refer to such \textit{previous commit} that the commit immediately before the bug fix.
-
-%While performing research on the topic, we did not find any empirical evidence that supported this assumption, so we decided to investigate its validity in the case of a large project, such as the OpenStack free/open source cloud computing infrastructure software.
-
-%In order to investigate if this assumption is valid, we formulate following research questions:
 In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
@@
 \end{itemize}
-%- Que utilizo 
-%- Donde se encuentra
-%- Como los analizo (Tool)
-%- Que tengo en cuenta en el análisis de los tickets....
-%- Como resultado de analizar los tickets encuentro ...
-%- Despues me interesa los commits anteriores
-%- Que realizo un análisis manual
 
@@
 \end{table}
-
-%The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, and the number of
-%\subsection{Fist Stage: The Filtering}
-%\label{sec:firstStage}
-%At this stage and with a tool's support developed to classify bug reports from other issues we distinguished the real bug reports in which afterwards analyzed the relation of the bug fixes with their previous commit.
-
-%We use the tool to analyze 459 randomly tickets from the four principal repositories in OpenStack.
-This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
-They are generally tracked in Launchpad \texttt{Nova},\texttt{Cinder},\texttt{Horizon} and \texttt{Neutron}\footnote{\url{https://bugs.launchpad.net/NameOfRepository}}
-
-%Each ticket has an id unique in Launchpad, which will be referred as \textit{n\_ticket}.
-Given its id, all information about the bug is publicly available in the issues tracking system\footnote{\url{https://bugs.launchpad.net/cinder/+bug/n_ticket}}.
-OpenStack uses Gerrit as code review system to see the evolution of each bug report\footnote{\url{https://review.openstack.org/ }}.
-Specifically we found the code review for each \textit{'n\_ticket'}\footnote{\url{https://review.openstack.org/#/c/n_review}}, where \textit{'n\_review'} is the review unique id for each \textit{'n\_ticket'}.
-In the code review all the information about the patchset that fixed the bug is shown.
-
-%Furthermore, due to tool allows carry out a double bind analysis, three researchers, included me, used the tool to classify the 459 tickets.
-In 417 of the ticktes we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
-
-%The table ~\ref{tab:3} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
-The concordance between the developers could be higer if they were expert in the project.
-
-%With the methodology at this stage, the researchers obtained a concordance of 70\% in their classification, being able to distinguish 209 bug reports from 292 issues report using the tool.
-
-%\subsubsection{BugTracking: The tool used}
-%\label{sec:tool}
-%The tool was designed to solve the problem of missclassified, providing the researcher with all the relevant information needed to decide if an issue belongs to a bug report or not.
-The tool is available at\footnote{\url{bugtracking.libresoft.es}} and extracts automatically tickets from the project's repository, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
-%The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
-
-%\begin{figure*}
-%\centering
-%\includegraphics[height=15cm]{index.png}
-%\caption{Screenshot of Analyze Tab}
-%\label{fig:1}       % Give a unique label
-%\end{figure*}
-
-%\subsection{Second Stage: Responsability of Previous Commit}
-%\label{sec:secondStage}
-%In the second stage, we only focused on the analysis of \textit{Bug Report} group, because this group contained the tickets that we are sure were bug reports.
-Discarding the \textit{Undecided} group in favour of the \textit{Bug Report} group reduces the accuracy of the experiment due to the fact that some errors are being lost in \textit{Undecided} group.
-However the \textit{Undecided} group being only 6\% of the bugs under consideration makes us think that this fact does not affect the validity of the final results.
-
-%We focused on analyzing the previous commits involved in a bug fix, understanding previous commit as the last commit that touched the line that has been fixed in the bug fix commit.
-The image \ref{fig:2} shows a real example in which the commit 31f208423 injected the lines 715, 716 and 717 in the file.
-But in the line 716, this commit inserted a bug.
-According to the description of the commmit that fixed the bug, image \ref{fig:3}, the value in the variable of the line 716 had to be boolean, obtaining that the previous commit is responsible to cause the bug.
-
-%At this stage, we got a list with all the previous commits, which could be where the bug was introduced.
-We  identifyed a total of 348 previous commits which can be responsible for inserting the line with the bug.
-When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
-After the analysis the responsible can be only one of them, more than one or none.
-
-%We analyzed a total of 209 tickets in which there were 348 previous commit, which we had to classify into one of the following groups, according to the responsability of the previous commit in the bug fix:
-%\begin{enumerate}
-%  \item It is responsible, when we are sure that the commit inserted the line with the bug.
-%  \item It is not responsible, when we are sure that the commit dind't insert the line with the bug.
-%  \item Undecided, when we cannot be sure if the commit is responsible due to our few knowleadge about the project or when the bug fix only added lines, complicating the analysis.
-%\end{enumerate}
-
-%To analyze the lines of the files involved, we used therefore the \texttt{diff} command to display line-by-line difference between the file before and after the bug fix commit.
-\texttt{diff} is well-known algorithm, extensively explained in the research literature~\cite{ukkonen1985algorithms,myers1986ano}, which is included in any source code management system.
-\texttt{diff} examines both files and returns the differences found between them, showing the line number.% the necessary modifications which should be done in order to the files match.
-the differences found between them,showing the line number.
-%FIXME: de aqui en adelante no entiendo la frase.
-need to be made for first file and second file to match, that is, returns the differences found between them.
-
-%After analayzed all the previous commit involved in the 209 Bug reports, we have discovered that not all the previous commits inserted the bug.
-This expecific project, which is continuosly evolving, presents some cases in which the bug was introduced by other actions.
-A clear example is the changes in called APIs, after the addition of a new feauture the called API fails, due to it requires an extra argument, but in the API there is not any bug.
-
-%Other example is shows in the commit log of a bug fix \ref{fig:5}, the name of a variable changed in the new version causing a failure.
-This change due to the new requirements in the version doesn't implicate that the previous commit was who inserted the bug, because until the new version the system doesn't fail.
-
-%\section{Results}
-%\label{sec:results}
-
-%\subsection{Fist Stage}
-%\label{sec:resultsFS}
-%We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
-The table \ref{tab:1} show the percentage of each researcher after analyzing the tickets, 417 tickets were analyzed by two different researchers,
 

### 2016-01-27 paperMSR.tex
Added the rest of the introduction

@@
 When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line/s that contains the bug in the source code.
-It seems reasonable to assign the responsability to insert the bug to the previous moodification of this/those lines, \textit{The previous commit}.
+It seems reasonable to assign the responsability to insert the bug to the previous modification of this/those lines, \textit{The previous commit}.
 But in fact, find when and where a bug was injected into the souce code is not a trivial task.
 
-In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or even we can find this assumption in tools that prevent dor future bugs; \textit{" We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
-We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating when the line containing the bug was inserted into the code.
+In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or even we can find this assumption in tools that prevent for future bugs; \textit{" We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
+We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.
 
-We based on some reasons to suppose that the previous commit doesn't insert the bug.
-Our main reason is that in a project wich is evolving continuously and where many different developers are working on, the code that before was correct, now can be buggy.
+The image \ref{fig:1} shows a clear example of we understand as responsible to cause the bug.
+In the image we can see three different versions of the same file in the history of the control version used in the project.
+The left code \textit{(1)} was written to fix the bug inserted in the middle code \textit{(2)} and with the \textit{31f08423} as the id of change,the previous commit.
+The code in the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug.
+In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was.
+And, according to the description of the commit log that fix the bug  \ref{fig:2}, this previous commit is responsible due to used the variable as string when had to be used as in the rest of the code, like as boolean.
+
+Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug.
+The bug fix commit log, \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware.
+This change done because of the new requirements in the version doesn't implicate that the previous commit was who inserted the bug.
+
+We based on some reasons to suppose that the previous commit didn't insert the bug.
+But, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy.
 Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
@@
 
-%- Codigo que era correcto deja de serlo
-%- En el momento en el que se introdujo fue un error
-%- ¿Código erroneo o hubo otro cambio?
-%- Díficil conocer el codigo en todo el contexto
-
-With our appproach we can identify which are the changes that introduced a bug, and this coul be useful to improve the accuracy of those tools developed to prevent bugs.
-Also, the software developers stand to benefit from identifying where the bug was inserted, improve their methodology.
-%How to plan to apply the knowledge in a way that can benefit software engineers.
-%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
+Unfortunately, not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}.
+So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modifyed or, another change in the software, related to the update of the software and its evolution, caused the bug.
 
@@
 \includegraphics[height=2in, width=7in]{responsible.png}
-\caption{Example of previous commit. The 31f208423 is the previous commit in the line involved in the bug-fix}
-\label{fig:2}       % Give a unique label
+\caption{Example of when the previous commit,31f208423, inserted the bug}
+\label{fig:1}       % Give a unique label
 \end{figure*}
@@
 \caption{Description of the bug-fix commit when the previous commit caused the bug}
+\label{fig:2}       % Give a unique label
+\end{figure}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[height=2in, width=7in]{noResponsible.png}
+\caption{Example of when the previous commit,0dc91bed, did not inserted the bug}
 \label{fig:3}       % Give a unique label
-\end{figure}
+\end{figure*}
 
@@
 \caption{Description of the bug-fix commit when the previous commit dind't cause the bug}
-\label{fig:5}       % Give a unique label
+\label{fig:4}       % Give a unique label
 \end{figure}
@@
 
-Te procedure following in each file involved in a fix bug is show in the figure \ref{fig:4}, and describes below;
+Te procedure following in each file involved in a fix bug is describing below;
 \begin{enumerate}
@@
 \end{enumerate}
-
-\begin{figure*}[htb]
-\centering
-\includegraphics[height=2in, width=7in]{noResponsible.png}
-\caption{Process to discover the commit that caused the bug }
-\label{fig:4}       % Give a unique label
-\end{figure*}
 
@@
   & Nova & Cinder & Horizon & Neutron & Total\\\hline
-R1 and R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
-R1 and R3   &  -        & (46) 73\%  & (48) 76\% & (26)62\% & 71 \% \\
-R2 and R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
+R1\&R2   & (44)70\% & (40)77\%  & (37)60\% & -        & 68\% \\
+R1\&R3   &  -        & (46)73\%  & (48)76\% & (26)62\% & 71 \% \\
+R2\&R3   & (41)66\% & (10)100\% & -         & -        &  71\% \\
 \bottomrule[0.3mm]
@@
 \label{sec:conclusions}
+The empirical experiment carried out in OpenStack, supported that the current premisse assumed does not hold for a large fraction of the analyzed bugs, because around the half of the previous commits were not responsibles inserting the bug.
+With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
+Also, the software developers stand to benefit from identifying where the bug was inserted, improve their methodology.
+%How to plan to apply the knowledge in a way that can benefit software engineers.
+%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
 

### 2016-01-27 paperMSR.tex
Added threats to validity

@@
 %\begin{center} {\footnotesize
-\caption{ Classification statistics of each researcher}
+\caption{ Statistics of each researcher in the classification}
 \label{tab:2}
@@
 \toprule[0.3mm]%{\smallskip}
-  & Bug Report\kern 1pc & Not Bug Report & Undecided & Total \\\hline
-R1  & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
-R2  & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
-R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
-Finally & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
+  & Bug Report & Not Bug Report & Undecided & Total \\\hline
+R1  & (184)55\% & (115)34\% & (35)11\% & 334 \\
+R2  & (188)76\% & (54)22 \% & (7)3\% & 249 \\
+R3 & (188)56\% & (116)35\% & (30)9\% & 334 \\
+Finally & (209)72\% & (74)25\% & (9)3\% & 292 \\
 \bottomrule[0.3mm]
@@
 \label{sec:discussion}
-
+\fbox{\begin{minipage}{25em}
+\textbf{RQ1:} asdasdasdasdasdasdsaddasdadasdasd
+\end{minipage}}
+\fbox{\begin{minipage}{25em}
+\textbf{RQ2:} asdasdasdasdasdasdsaddasdadasdasd
+\end{minipage}}
 - Como se responden las RQ1 y RQ2
@@
 \label{sec:threats}
-The limited sample size of tickets used in this research is the major threat to its validity.
+%The limited sample size of tickets used in this research is the major threat to its validity.
 %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency.
 This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
+The size of the tickets extracted form the Launcpad is medium, but doing the analisys manually we are sure that the results present in this paper are valid, being sure that the previous commits classifyed as not responsible, they are.
 
-In addition our model has threats, external and internal, that make our model not 100\% valid. The internal threats are following:
+Although, we understand that the model presented has some threats, external and internal, that make our model not 100\% valid.
+The internal threats related to the researchers that have conducted the study are following:
 
 \begin{itemize}
-    \item We have not taken into account errors that have been classified into \textit{Undecided}.
-    \item There could be some lax criteria involving the subjective opinion of the reviewers.
-    \item We are not experts in analyzing and classifying tickets, and our inexperience may have influenced the results of the analysis.
+    \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we are lost some real bug reports belonging this group .
+    \item There could be some lax criteria involving the subjective opinion of the researchers.
+    \item The researchers are not experts in OpenStack, and our inexperience may have influenced the results of the analysis.
     \item We are only using part of the information that the ticket provides, like comments and text.
-There could be a recognized pattern, unknown at first sight, that involves other parts of the information, or the whole information.
+There could be a recognized pattern in teh data, unknown at first sight, that involves other parts of the information.
+    \item Although we use a random script to extract the tickets reported in during the last year, 2015, from the launchpad, in this year could be some bias unidentified.
+    \item In case of the researchers didn't find the information to know if the previous commit inserted the bug or in contrast, it was caused by the evolution of the software.
+They keep the traditionalist thought, classify these previous commits are responsibles.
 \end{itemize}
 
-The external threats, related to the researchers that have conducted the classification, are following:
+The external threats, related to the case of the project, are following:
 
@@
     \item Some tickets are not explicitly described, which could increase the percentage of \textit{Undecided}. This is especially true if the reviewers are not from OpenStack.
+    \item OpenStack is a special project put down a constant evolution due to their active community of developers.
+Maybe, in other projects with less commits per year the statistics about the responsability of previous commit change.
 \end{itemize}
@@
 \label{sec:conclusions}
-The empirical experiment carried out in OpenStack, supported that the current premisse assumed does not hold for a large fraction of the analyzed bugs, because around the half of the previous commits were not responsibles inserting the bug.
+The empirical experiment carried out in OpenStack, supported that the current premisse assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not responsibles inserting the bug.
 With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.

### 2016-01-27 paperMSR.tex
Added some related work

@@
 When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line/s that contains the bug in the source code.
-It seems reasonable to assign the responsability to insert the bug to the previous modification of this/those lines, \textit{The previous commit}.
-But in fact, find when and where a bug was injected into the souce code is not a trivial task.
+It seems reasonable to assign the previous modification of this/those lines, \textit{The previous commit}, as the cause of the bug.
+But in fact, find when and where a bug was injected into the souce code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.
 
@@
 \label{sec:related}
-First SZZ\\
-Second Improvement of SZZ\\
+First SZZ, the first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}.
+Currently, is a well-known algorithm called SZZ, which is based on text diferencing to discover modified, added and delete lines between the bug-fix and its previous version.
+SZZ uses CVS annotate command to identify the last commit that touched these lines.
+
+Second, a improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion.
+Also, they deleting some false positives as blank spaces, changes in the format or changes in the comments.
 Then SZZ revisited\\
-Then Buginnings\\
+
+Then Buginnings \cite{sinha2010buginnings} is not a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences.
+Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.
+
+These two approach have the similar ideas: (1) find the differences between the bug-fix version of and the previous version of the file to recognize those changes done by bug-fix commit.
+(2) look back in the code revision history until identify which version touched the lines affected in the bug-fix for the last time.
+
 Finally our idea.

### 2016-01-27 paperMSR.tex
Added data from OpenStack

@@
 \label{sec:related}
-First SZZ, the first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}.
+The first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}.
 Currently, is a well-known algorithm called SZZ, which is based on text diferencing to discover modified, added and delete lines between the bug-fix and its previous version.
@@
 
-Second, a improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion.
+An improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion.
 Also, they deleting some false positives as blank spaces, changes in the format or changes in the comments.
-Then SZZ revisited\\
 
-Then Buginnings \cite{sinha2010buginnings} is not a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences.
+Other methodology to identify the origins of a bug is describes in \cite{sinha2010buginnings}, this work doesn't present a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences.
 Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.
@@
 
+Exists several articles based on SZZ such as \cite{williams2008szz} revisied SZZ algorithm, tracking bug-inducing changes and identify change types of them.
+Also, in \cite{yangbug} the authors applyed this algorithm to find out what kind of bug-inducing changes are likely to become in a great threat after being marked as bug-fix changes.In addition, new techniques in bug prediction are based in this algotimh such as \cite{kim2008classifying} which was the first work classifying file changes as buggy or clean using change information features and source code terms.
+
+In addition some tools are based on SZZ too such as \cite{} 
 Finally our idea.
@@
 
-OpenStack is composed by 10 projects, but we only focused in the four more actives in the 2015, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack}
+OpenStack is composed by 9 projects, but we only focused in the four of them, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack} these projects are really actives during all their history and in the last year.
 \begin{table}[htb]
@@
   & All History \kern 1pc & Last Year (2015) \\\hline
-Nova    \kern 1pc & - & - \\
-Fuel    \kern 1pc & - & -  \\
-Netron  \kern 1pc & - & - \\
-Openstack-manuals \kern 1pc & - & -  \\
-Horizon \kern 1pc & - & -  \\
-Cinder  \kern 1pc & - & - \\
-Keystone\kern 1pc & - & -  \\
-Heat    \kern 1pc & - & -  \\
-Glance  \kern 1pc & - & - \\
-Tempest \kern 1pc & - & - \\
+Nova    \kern 1pc & 14,558 & 3,283 \\
+Fuel    \kern 1pc & 9,139 & 5,123 \\
+Netron  \kern 1pc & 8,452 & 3,855 \\
+Horizon \kern 1pc & 4,871 & 1,994 \\
+Cinder  \kern 1pc & 4,556 & 1,832 \\
+Keystone\kern 1pc & 4,874 & 1,795  \\
+Heat    \kern 1pc & 6,395 & 2,372  \\
+Glance  \kern 1pc & 2,651 & 723 \\
+Tempest \kern 1pc & 4,141 & 1,312 \\
 \bottomrule[0.3mm]

### 2016-01-27 paperMSR.tex
Added data from OpenStack

@@
 
-In addition some tools are based on SZZ too such as \cite{} 
+%In addition some tools are based on SZZ too such as \cite{} 
 Finally our idea.
@@
 
-\section{Conclusions}
+\section{Conclusions and Future Work}
 \label{sec:conclusions}
@@
 %What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
+
+A final field in our future work concerns the full automatization on the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
+Another interesting investigation could leadge the same empirical study in a project with a community less active, to can prove if our idea is fullfil in other projects.
 

### 2016-01-28 paperMSR.tex
RQ1 and RQ2

@@
 
-When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line/s that contains the bug in the source code.
-It seems reasonable to assign the previous modification of this/those lines, \textit{The previous commit}, as the cause of the bug.
+When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line that contains the bug in the source code.
+It seems reasonable to assign the previous modification of this line as the cause of the bug, this previous modification is \textit{The previous commit}.
 But in fact, find when and where a bug was injected into the souce code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.
 
-In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or even we can find this assumption in tools that prevent for future bugs; \textit{" We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
+In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
 We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.
@@
     %\item RQ2:  How often is the bug caused in the previous commit?
-     \item RQ2:  In which cases the previous commit/s are responsible to cause the bug?
+     \item RQ2:  In which cases the previous commit/s inserted the line with the bug into the source code?
 \end{itemize}
@@
 \fbox{\begin{minipage}{25em}
-\textbf{RQ1:} asdasdasdasdasdasdsaddasdadasdasd
+\textbf{RQ1: Using all the information available in the bug tracking system and code review system related a fix-bug, we have obtained that this fix-bug were real Bug Reports in a 72\% of the tickets analyzed}
 \end{minipage}}
 \fbox{\begin{minipage}{25em}
-\textbf{RQ2:} asdasdasdasdasdasdsaddasdadasdasd
+\textbf{RQ2: We have comfirmed that 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them didn't injected any bug in the code source } 
 \end{minipage}}
-- Como se responden las RQ1 y RQ2
+\\
 - No todos los casos son tan claros como los mostrados en los ejemplos ....

### 2016-01-28 paperMSR.tex
Some changes in the text

@@
 
-In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
-We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.
+In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.
+Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
+Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understandig the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.
 
@@
 In the image we can see three different versions of the same file in the history of the control version used in the project.
-The left code \textit{(1)} was written to fix the bug inserted in the middle code \textit{(2)} and with the \textit{31f08423} as the id of change,the previous commit.
-The code in the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug.
+The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit.
+The code on the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug.
 In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was.
-And, according to the description of the commit log that fix the bug  \ref{fig:2}, this previous commit is responsible due to used the variable as string when had to be used as in the rest of the code, like as boolean.
+And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as boolean keeping the concordance with the rest of the code.
 
 Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug.
-The bug fix commit log, \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware.
-This change done because of the new requirements in the version doesn't implicate that the previous commit was who inserted the bug.
+In this example, the bug fix commit log \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware.
+This change was done because of the new requirements in the version, and this doesn't implicate that the previous commit inserted the bug, because when the line involved in the fix-bug was inserted by first time, it doesn't contain any bug.
 
-We based on some reasons to suppose that the previous commit didn't insert the bug.
-But, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy.
+We based on some reasons such as the explained before to suppose that the previous commit didn't insert the bug.
+Thus, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy.
 Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
@@
 Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applaying our approach to OpenStack in Section~\ref{sec:results}.
-Section~\ref{sec:discussion} discusses potential applications and improvements of our approach.
+Section~\ref{sec:discussion} answers the research question suggested in ~\ref{sec:introduction}discusses potential applications and improvements of our approach.
 Section~\ref{sec:threats} reports threats to validity.
@@
 In this case, the ticket was classified into the \textit{Undecided} group.
-\subsection{Second Stage: Responsability of Previous Commit}
+\subsection{Second Stage: Who caused the Bug?}
 \label{sec:secondStage}

### 2016-01-28 paperMSR.tex
Updating

@@
 In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.
+Also in \cite{pan2009toward}'s work describing the bug fix patterns we can find this assumption; \textit{"The version before the bug fix revision is the bug version"}.
 Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
@@
 
-The image \ref{fig:1} shows a clear example of we understand as responsible to cause the bug.
+The image \ref{fig:1} shows a clear example of we understand as cause of the bug.
 In the image we can see three different versions of the same file in the history of the control version used in the project.

### 2016-01-29 paperMSR.tex
Some minor changes to the abstract and fixes to the semantics

@@
 \alignauthor
-Gema Rodriguez\\
-       \affaddr{University King Juan Carlos}\\
+Gema Rodr\'iguez\\
+       \affaddr{Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
@@
 \alignauthor
-Jesus M. Gonzalez-Barahon\\
-      \affaddr{University King Juan Carlos}\\
+Jesus M. Gonz\'alez-Barahona\\
+      \affaddr{Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
@@
 \alignauthor Gregorio Robles\\
-       \affaddr{University King Juan Carlos}\\
+       \affaddr{Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
        \affaddr{Madrid, Spain}\\
-       \email{grex@gsyc.es}
+       \email{grex@gsyc.urjc.es}
 \and  % use '\and' if you need 'another row' of author names
@@
 \begin{abstract}
-To fix a bug in a certain software product, some parts of its source code are modified.
-At first glance, it could seem reasonable that the fixed bug was introduced by the previous modification of those same parts of the source code (the previous commit).
+It is common practice that developers mark in the versioning system when they are fixing a software bug.
+At first glance, it could seem reasonable to assume that the fixed bug had been introduced in the previous modification of those same parts of the source code (i.e., in the previous commit).
 In fact, many studies on bug seeding start with this assumption.
-However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug was introduced by other actions, such as an older modification, or a change in called APIs.
+However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug may have been introduced by other actions, such as an older modification, or a change in the API that is being called.
 
-This paper tries to shed some light on this area, by analyzing the relationship of bug fixes with their previous commits.
-To this end, we conducted an observational study on bug reports, their fixes, and their correspoonding previous commits for OpenStack.
-Our results show that the mentioned asumption does not hold for a large fraction of the analyzed bugs, which were not introduced by their previous commit.
+This paper tries to shed some light on this topic, by analyzing the relationship of bug fixes with their previous commits.
+To this end, we conducted an observational study on bug reports, their fixes, and their corresponding previous commits for the OpenStack project.
+Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed.
+FIXME: maybe something more here
 \end{abstract}
@@
 
-\keywords{Bug introduction, bug seeding, SZZ algoritm, previous commit}
+\keywords{Bug introduction, bug seeding, SZZ algorithm, previous commit}
 
@@
 
-When a failure is found in the behavoir of a software, the developers try to fix it locating and modifiying the line that contains the bug in the source code.
+When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the line that contains the bug in the source code.
 It seems reasonable to assign the previous modification of this line as the cause of the bug, this previous modification is \textit{The previous commit}.
-But in fact, find when and where a bug was injected into the souce code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.
+But in fact, find when and where a bug was injected into the source code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.
 
@@
 Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
-Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understandig the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.
+Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understanding the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.
 
@@
 The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit.
-The code on the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug.
+The code on the right \textit{(3)} is to ensure that in previous versions of the file did not exist the bug.
 In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was.
-And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as boolean keeping the concordance with the rest of the code.
+And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as Boolean keeping the concordance with the rest of the code.
 
 Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug.
-In this example, the bug fix commit log \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware.
+In this example, the bug fix commit log \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the software.
 This change was done because of the new requirements in the version, and this doesn't implicate that the previous commit inserted the bug, because when the line involved in the fix-bug was inserted by first time, it doesn't contain any bug.
@@
 Thus, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy.
-Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
+Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feature or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
 As a result, the software fails at this line.
-But in fact, the previous commit which wrote the called API is not responsible, due to the line did't contain any bug at the moment in which was written.
+But in fact, the previous commit which wrote the called API is not responsible, due to the line did not contain any bug at the moment in which was written.
 
 Unfortunately, not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}.
-So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modifyed or, another change in the software, related to the update of the software and its evolution, caused the bug.
+So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
 
@@
 \includegraphics[height=2.4cm]{UpdateFixBug.png}
-\caption{Description of the bug-fix commit when the previous commit dind't cause the bug}
+\caption{Description of the bug-fix commit when the previous commit did not cause the bug}
 \label{fig:4}       % Give a unique label
@@
 The remainder of this paper is structured as follows.
-First, we present the motivations that support our study,  explaining the current body of knowleadge in section~\ref{sec:related}.
-Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applaying our approach to OpenStack in Section~\ref{sec:results}.
+First, we present the motivations that support our study,  explaining the current body of knowledge in section~\ref{sec:related}.
+Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applying our approach to OpenStack in Section~\ref{sec:results}.
 Section~\ref{sec:discussion} answers the research question suggested in ~\ref{sec:introduction}discusses potential applications and improvements of our approach.
@@
 The first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}.
-Currently, is a well-known algorithm called SZZ, which is based on text diferencing to discover modified, added and delete lines between the bug-fix and its previous version.
+Currently, is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and delete lines between the bug-fix and its previous version.
 SZZ uses CVS annotate command to identify the last commit that touched these lines.
@@
 
-Other methodology to identify the origins of a bug is describes in \cite{sinha2010buginnings}, this work doesn't present a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences.
+Other methodology to identify the origins of a bug is describes in \cite{sinha2010buginnings}, this work doesn't present a text-based technique as SZZ, the authors analyzed the effects of bug-fix changes on program dependencies.
 Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.
@@
 
-Exists several articles based on SZZ such as \cite{williams2008szz} revisied SZZ algorithm, tracking bug-inducing changes and identify change types of them.
-Also, in \cite{yangbug} the authors applyed this algorithm to find out what kind of bug-inducing changes are likely to become in a great threat after being marked as bug-fix changes.In addition, new techniques in bug prediction are based in this algotimh such as \cite{kim2008classifying} which was the first work classifying file changes as buggy or clean using change information features and source code terms.
+Exists several articles based on SZZ such as \cite{williams2008szz} revisited SZZ algorithm, tracking bug-inducing changes and identify change types of them.
+Also, in \cite{yangbug} the authors applied this algorithm to find out what kind of bug-inducing changes are likely to become in a great threat after being marked as bug-fix changes.In addition, new techniques in bug prediction are based in this algorithm such as \cite{kim2008classifying} which was the first work classifying file changes as buggy or clean using change information features and source code terms.
 
@@
 %We present our approach to identify how and where a bug was inserted into the source code, causing a later fix. 
-We extract all the data necesary to analyze when the bug was inserted from the issue tracking system and the code review system used by the project we are analyzing.
+We extract all the data necessary to analyze when the bug was inserted from the issue tracking system and the code review system used by the project we are analyzing.
 OpenStack uses Launchpad\footnote{\url{https://launchpad.net/openstack}} and Gerrit\footnote{\url{https://review.openstack.org/}}.
 
-The Launchapd of each project works with issues reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
+The Launchpad of each project works with issues reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
 But, in our study we are only interested in those tickets that describe a bug report and, in addition, have been closed with a merged in the code source to fix the bug.
@@
 \label{sec:firstStage}
-In our approach, first of all we must identifying which of those issues extracted from Launchapd are bug reports.
+In our approach, first of all we must identifying which of those issues extracted from Launchpad are bug reports.
 But, this is not a trivial task and we performed this identification using a web tool\footnote{\url{bugtracking.libresoft.es}} development to provide the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
@@
 
-The analisys was done manually, and we used \textit{git blame} to see all the previos commit in each line of a involved file.
+The analysis was done manually, and we used \textit{git blame} to see all the previous commit in each line of a involved file.
 Also, we used \textit{diff} to see all the differences between two files, in our case, the file is going to be the same but in different moment inside the control version system used.
@@
 \begin{enumerate}
-  \item git checkout \textit{commmit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
-  \item git checkout \textit{parent of commmit that fix the bug}, git blame \textit{file involved}.
+  \item git checkout \textit{commit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
+  \item git checkout \textit{parent of commit that fix the bug}, git blame \textit{file involved}.
 In this step we can see all the previous commits involved in the different lines touched in the fix bug.
-  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can esure that the previous commit inserted these lines.
+  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can ensure that the previous commit inserted these lines.
 \end{enumerate}
 
-Finally we need to discard some noise presents in our final resulst according to the responsability of the previous commit inserting the bug in the code source.
-Due to they were not responsibles for cause the bug, we delete those previous commit which presents the following criteria;
+Finally we need to discard some noise presents in our final results according to the responsibility of the previous commit inserting the bug in the code source.
+Due to they were not responsible for cause the bug, we delete those previous commit which presents the following criteria;
 \begin{itemize}
@@
     \item Changes in the comment.
-    \item Updatings in the version of a file. 
+    \item Updates in the version of a file. 
 \end{itemize}
@@
 
-We validate our methodology anlayzing 459 tickets in OpenStack.
+We validate our methodology analyzing 459 tickets in OpenStack.
 OpenStack was particularly of interest because of its continuously evolving due to its very active community.
-Although its short life, only five years, more than 5 thousand of resarchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project \footnote{\url{http://activity.openstack.org/dash/browser/}}.
-Futhermore, all history is saved and available in a version control system, being able to access to its issue tracking system \footnote{\url{https://launchpad.net/openstack}} and the source code review \footnote{\url{https://review.openstack.org/}}
+Although its short life, only five years, more than 5 thousand of researchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project \footnote{\url{http://activity.openstack.org/dash/browser/}}.
+Furthermore, all history is saved and available in a version control system, being able to access to its issue tracking system \footnote{\url{https://launchpad.net/openstack}} and the source code review \footnote{\url{https://review.openstack.org/}}
 
@@
 
-In this four projects we analized the relationship of bug fixes with their previous commits.
+In this four projects we analyzed the relationship of bug fixes with their previous commits.
 In order to identify the moment in which the bug was injected into the source code.
 The first stage we did automatically using the tool and a double bind between three researchers, three PhD student  included me.
-The second stage was done manually and only me was involved analizing this relationship.
+The second stage was done manually and only me was involved analyzing this relationship.
 %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
@@
 We extracted a total of 459 different tickets from the Launchpad of the four principal projects in OpenStack, 125 tickets from Nova, 125 tickets from cinder, 125 tickets from Horizon and 84 tickets from Neutron.
-These tickets first, were analized to identify those ones which were real bug reports.
+These tickets first, were analyzed to identify those ones which were real bug reports.
 And secondly, each file was analyzed to obtain which previous commit inserted the bug causing the failure of the system and reporting the bug report.
@@
 We classify a total of 459 tickets using the tool.
-In 417 of the ticktes, we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
+In 417 of the tickets, we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
 
-The table \ref{tab:2} shows the percentage of each researcher after analyzing the tickets, and the number of tickets classifyed identically by two different researchers.
-Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly differents with a higher number of tickets classifyed as Bug Report.
+The table \ref{tab:2} shows the percentage of each researcher after analyzing the tickets, and the number of tickets classified identically by two different researchers.
+Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly different with a higher number of tickets classified as Bug Report.
 
-Finally, the researchers identifyed in the same way 292 tickets, that is, their results matched in a 70\% of the cases.
-Obtaining 209 tickets classifyed as Bug report, 74 tickets classifyed as Not Bug Report and 9 tickets classifyed as Undecided.
+Finally, the researchers identified in the same way 292 tickets, that is, their results matched in a 70\% of the cases.
+Obtaining 209 tickets classified as Bug report, 74 tickets classified as Not Bug Report and 9 tickets classified as Undecided.
 
@@
 
-Also we had measured the concordance in the classification of each developer according to the project analized.
-The table \ref{tab:3} shows that the concordante got between all the three research was very similar, around a 70\%.
-Furthermore, the concordance form each researcher with the rest alwas was up to 60\%.
+Also we had measured the concordance in the classification of each developer according to the project analyzed.
+The table \ref{tab:3} shows that the concordant got between all the three research was very similar, around a 70\%.
+Furthermore, the concordance form each researcher with the rest always was up to 60\%.
 
@@
 
-At this stage, we analyzed the 209 we got a list with all the previous commits and we were be able to classifyed the previous commit/s as Responsible, Not Responsible or Undecided, taken into account that the bug could be inserted in different lines of different commits, but not everyone had to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
+At this stage, we analyzed the 209 we got a list with all the previous commits and we were be able to classified the previous commit/s as Responsible, Not Responsible or Undecided, taken into account that the bug could be inserted in different lines of different commits, but not everyone had to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
 In fact, the responsible can be only one of them, more than one or maybe none.
 
-We identifyed a total of 348 previous commits which can be responsible for inserting the line containing the bug.
-After analizing the Bug Reports and their previous commits and discarded 40 of them because were noise, Table \ref{tab:responsability}, we got that 152 previous commit were responsibles to cause the bug whereas 114 previous commit had not any responsability in the failure of the system, and only in 42 previous commits we were unable to identify the cause of the bug.
+We identified a total of 348 previous commits which can be responsible for inserting the line containing the bug.
+After analyzing the Bug Reports and their previous commits and discarded 40 of them because were noise, Table \ref{tab:responsability}, we got that 152 previous commit were responsible to cause the bug whereas 114 previous commit had not any responsibility in the failure of the system, and only in 42 previous commits we were unable to identify the cause of the bug.
 
@@
 \begin{center} {\footnotesize
-\caption{ Responsability of each previous commit before and after deleting the noise in the results}
+\caption{ Responsibility of each previous commit before and after deleting the noise in the results}
 \label{tab:responsability}
@@
 
-Futhermore, focusing on how many previous commits presented each Bug Report, we obtained that 131 had one previous commit implicated, whereas 58 had more than one previous commit implicated in their file/s.
-According to Table \ref{tab:secondStage}, from the 131, we obtained that 65 of them inserted the bug, but 30 of them were not responsibles in the failure of the system.
-And from the 58 which had more than one previous commits, we obtained in total 189 previous commit, where 86 of them were respnsibles and 82 were not responsibles.
+Furthermore, focusing on how many previous commits presented each Bug Report, we obtained that 131 had one previous commit implicated, whereas 58 had more than one previous commit implicated in their file/s.
+According to Table \ref{tab:secondStage}, from the 131, we obtained that 65 of them inserted the bug, but 30 of them were not responsible in the failure of the system.
+And from the 58 which had more than one previous commits, we obtained in total 189 previous commit, where 86 of them were responsible and 82 were not responsible.
 %Probably, the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
@@
 
-Also, we looked the distribution of the previous commit in each Bug Report, Table \ref{tab:secondStage2}, we observed that the most commun distribuion in the relationship between previous commit and bug report is one previous commit per Bug Report, following by the second commun distribution, two previous commit per Bug Report.
+Also, we looked the distribution of the previous commit in each Bug Report, Table \ref{tab:secondStage2}, we observed that the most common distribution in the relationship between previous commit and bug report is one previous commit per Bug Report, following by the second common distribution, two previous commit per Bug Report.
 \begin{table*}[htb]
@@
 
-Finally we wanted to know the responsability preactised by each previous commit in the failure of a system, in other words, we were interested in analize from those cases where exists more than one previous commit, how many of them inserted the bug in the code source, Table \ref{tab:secondStage3}.
-We obtained that in 8 Bug Reports all the previous commits were responsibles, in 30 Bug reports at least one of their previous commit caused the bug and in 11 bug report none of their previous commits inserted the bug.
+Finally we wanted to know the responsibility practiced by each previous commit in the failure of a system, in other words, we were interested in analyze from those cases where exists more than one previous commit, how many of them inserted the bug in the code source, Table \ref{tab:secondStage3}.
+We obtained that in 8 Bug Reports all the previous commits were responsible, in 30 Bug reports at least one of their previous commit caused the bug and in 11 bug report none of their previous commits inserted the bug.
 \begin{table*}[htb]
@@
 \fbox{\begin{minipage}{25em}
-\textbf{RQ2: We have comfirmed that 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them didn't injected any bug in the code source } 
+\textbf{RQ2: We have confirmed that 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them didn't injected any bug in the code source } 
 \end{minipage}}
@@
 
-How to proceed if looking for the responsability of a bug when only added lines are inserted?
+How to proceed if looking for the responsibility of a bug when only added lines are inserted?
 And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
@@
 This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
-The size of the tickets extracted form the Launcpad is medium, but doing the analisys manually we are sure that the results present in this paper are valid, being sure that the previous commits classifyed as not responsible, they are.
+The size of the tickets extracted form the Launchpad is medium, but doing the analysis manually we are sure that the results present in this paper are valid, being sure that the previous commits classified as not responsible, they are.
 
@@
     \item We are only using part of the information that the ticket provides, like comments and text.
-There could be a recognized pattern in teh data, unknown at first sight, that involves other parts of the information.
+There could be a recognized pattern in the data, unknown at first sight, that involves other parts of the information.
     \item Although we use a random script to extract the tickets reported in during the last year, 2015, from the launchpad, in this year could be some bias unidentified.
     \item In case of the researchers didn't find the information to know if the previous commit inserted the bug or in contrast, it was caused by the evolution of the software.
-They keep the traditionalist thought, classify these previous commits are responsibles.
+They keep the traditionalist thought, classify these previous commits are responsible.
 \end{itemize}
@@
     \item OpenStack is a special project put down a constant evolution due to their active community of developers.
-Maybe, in other projects with less commits per year the statistics about the responsability of previous commit change.
+Maybe, in other projects with less commits per year the statistics about the responsibility of previous commit change.
 \end{itemize}
@@
 \label{sec:conclusions}
-The empirical experiment carried out in OpenStack, supported that the current premisse assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not responsibles inserting the bug.
+The empirical experiment carried out in OpenStack, supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not responsible inserting the bug.
 With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
@@
 
-A final field in our future work concerns the full automatization on the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
-Another interesting investigation could leadge the same empirical study in a project with a community less active, to can prove if our idea is fullfil in other projects.
+A final field in our future work concerns the full automation on the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
+Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.
 
@@
 \section{Acknowledgments}
-We thank the two phd students, Dorealda Dalipaj and Nelson Sekitoleko, that participated differentiating Bug report from the others.
+We thank the two PhD students, Dorealda Dalipaj and Nelson Sekitoleko, that participated differentiating Bug report from the others.
 Also, we thank Bitergia \footnote{\url{http://bitergia.com/}} to explain its available database of OpenStack.
-Finally,thanks the Spanish Goverment because all authors are funded in part by it, through project TIN2014-59400-R.
+Finally,thanks the Spanish Government because all authors are funded in part by it, through project TIN2014-59400-R.
 

### 2016-01-29 paperMSR.tex
He ido tocando hasta metodología. Me está gustando lo que estoy leyendo.

@@
 
-\title{Who introduced the bug? The importance of the previous commit}
+\title{Who introduced this bug? \\ Don't look only at the previous commit!}
 %\subtitle{[Extended Abstract]
@@
 Gema Rodr\'iguez\\
-       \affaddr{Universidad Rey Juan Carlos}\\
+       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
@@
 Jesus M. Gonz\'alez-Barahona\\
-      \affaddr{Universidad Rey Juan Carlos}\\
+      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
@@
 \alignauthor Gregorio Robles\\
-       \affaddr{Universidad Rey Juan Carlos}\\
+       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
        %\affaddr{1932 Wallamaloo Lane}\\
@@
 
-When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the line that contains the bug in the source code.
-It seems reasonable to assign the previous modification of this line as the cause of the bug, this previous modification is \textit{The previous commit}.
-But in fact, find when and where a bug was injected into the source code is not a trivial task which has largely been ignored due to the data related about the origin of a bug is embedded in the evolution of the software \cite{sinha2010buginnings}.
+When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code.
+It seems reasonable to assume that the previous modification of this line or these lines are the cause of the bug; this previous modification is \textit{the previous commit}.
+But in fact, to find when and where a bug was introduced in the source code is not a trivial task.
+This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
+FIXME: clarificar la frase anterior...
+no ha quedado muy claro.
 
-In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.
-Also in \cite{pan2009toward}'s work describing the bug fix patterns we can find this assumption; \textit{"The version before the bug fix revision is the bug version"}.
-Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}.
-Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understanding the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.
+This is the reason why many studies in the area of mining software repositories start with this implicit assumption.
+So, for instance, we have found following reasonings in several areas of research, such as:
 
-The image \ref{fig:1} shows a clear example of we understand as cause of the bug.
-In the image we can see three different versions of the same file in the history of the control version used in the project.
-The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit.
-The code on the right \textit{(3)} is to ensure that in previous versions of the file did not exist the bug.
-In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was.
-And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as Boolean keeping the concordance with the rest of the code.
-
-Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug.
-In this example, the bug fix commit log \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the software.
-This change was done because of the new requirements in the version, and this doesn't implicate that the previous commit inserted the bug, because when the line involved in the fix-bug was inserted by first time, it doesn't contain any bug.
-
-We based on some reasons such as the explained before to suppose that the previous commit didn't insert the bug.
-Thus, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy.
-Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feature or an enhancement the called API should be changed to support this new characteristic, but it didn't it.
-As a result, the software fails at this line.
-But in fact, the previous commit which wrote the called API is not responsible, due to the line did not contain any bug at the moment in which was written.
-
-Unfortunately, not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}.
-So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
-
-In this paper, we attempt to address the following research question regarding who introduced the bug in the source code.
 \begin{itemize}
-    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-     \item RQ1:  How I can know that a change was done to fix a bug in the source code? How I can identify them?
-    %\item RQ2:  How often is the bug caused in the previous commit?
-     \item RQ2:  In which cases the previous commit/s inserted the line with the bug into the source code?
+  \item in bug seeding studies, e.g., \textit{``This earlier change is the one that caused the later fixed''}~\cite{williams2008szz} or \textit{``The lines affected in the process of fixing a bug are the same one that originated or seeded that bug''}~\cite{izquierdo2011developers},
+  \item in bug fix patterns, e.g., \textit{``The version before the bug fix revision is the bug version''}~\cite{pan2009toward},
+  \item and in tools that prevent for future bugs, e.g., \textit{``We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit''}~\cite{fejzer2015supporting}.
 \end{itemize}
 
-\begin{figure*}
+But although the assumption can be found frequently in the research literature, in our opinion there is not empirical evidence supporting it.
+That is the reason why we have conducted an observational study on fix-bugs, devoting a significant effort to locate the origin of a bug in the source code and understanding the possible causes.
+For this we had to take into account the moment in which the line was inserted and the general context of the project.
+
+Figure~\ref{fig:1} shows a clear example of what we understand as the cause of the bug.
+Let's assume that we have three different versions of the same file in the history of the control version of the project.
+
+\begin{figure*}[ht]
 \centering
 \includegraphics[height=2in, width=7in]{responsible.png}
-\caption{Example of when the previous commit,31f208423, inserted the bug}
+\caption{Example of a change in which the bug was introduced in the previous commit. More recent versions of the code are on the left.}
 \label{fig:1}       % Give a unique label
@@
 
-\begin{figure}[htb]
+\begin{enumerate}
+  \item The code on the left (subfigure \textit{(1)}) is the one written to fix the bug.
+  \item The code in the middle (subfigure \textit{(2)}) shows the moment in which the bug was introduced (being \textit{31f08423} the id of change), the previous commit.
+  \item The code on the right (subfigure \textit{(3)}) ensures that in previous versions of the file, the bug did not exist.
+\end{enumerate}
+
+\begin{figure}[ht]
 \centering
 \includegraphics[height=2.4cm]{gerritPrevCommit.png}
-\caption{Description of the bug-fix commit when the previous commit caused the bug}
+\caption{Description of the bug-fix commit for a case in which the previous commit caused the bug.}
 \label{fig:2}       % Give a unique label
@@
 
-\begin{figure*}[htb]
+According to the description in the log of the commit that fixed the bug (see Figure~\ref{fig:2}), commit \textit{31f08423} was the one where the bug was introduced, as it used a variable as string when a Boolean had to be used, keeping the concordance with the rest of the code.
+So, in this case, the bug was introduce in the previous commit.
+
+On the other hand, Figure~\ref{fig:3} shows a clear example of a case where the cause of the bug is not to be attributed to the previous commit.
+In this example, the bug fix commit log (see Figure~\ref{fig:4}) describes that the name of an argument changed when updating the version causing the failure in the software.
+This change was done because of the new requirements in the software version, and is unrelated to the changes performed in the previous commit.
+When the modified lines where introduced in the first time, they did not contain the bug.
+
+\begin{figure*}[ht]
 \centering
 \includegraphics[height=2in, width=7in]{noResponsible.png}
-\caption{Example of when the previous commit,0dc91bed, did not inserted the bug}
+\caption{Example of a change where the previous commit, 0dc91bed, did not insert the bug. More recent versions of the code are on the left.}
 \label{fig:3}       % Give a unique label
@@
 
-\begin{figure}[htb]
+\begin{figure}[ht]
 \centering
 \includegraphics[height=2.4cm]{UpdateFixBug.png}
-\caption{Description of the bug-fix commit when the previous commit did not cause the bug}
+\caption{Description of the bug-fix commit for a case in which the previous commit did not cause the bug.}
 \label{fig:4}       % Give a unique label
@@
 
+Based on anecdotal evidence like the one presented in Figures~\ref{fig:3} and Figure~\ref{fig:4}, we argue that in projects that are continuously evolving, with an ample developer community, code that before was correct could be buggy at some time.
+So, changes in other parts
+of the code may induce wrong behavior (bugs) in places that were correct in the past.
+This happens often in situations like changes to the API.
+In the moment the code ws written, it was correct and the woftware worked fine.
+Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail.
+But in such cases, the source of the error cannot be FIXME assigned to a change performed in the previous commit, as in that moment it referred to a different API.
+
+FIXME: poner esto bien
+
+The goal of this paper is to find if the cause of the bug can be FIXME assigned to the previous commit, understanding that at the time when the previous commit is introduced
+
+not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}.
+So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
+
+In detail, in this paper we attempt to address the following research question regarding who introduced the bug in the source code:
+
+FIXME: rephrase RQs
+
+\begin{itemize}
+    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
+     \item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+    %\item RQ2:  How often is the bug caused in the previous commit?
+     \item RQ2:  When did the previous commit introduce the line with the bug into the source code?
+\end{itemize}
+
 The remainder of this paper is structured as follows.
-First, we present the motivations that support our study,  explaining the current body of knowledge in section~\ref{sec:related}.
-Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applying our approach to OpenStack in Section~\ref{sec:results}.
-Section~\ref{sec:discussion} answers the research question suggested in ~\ref{sec:introduction}discusses potential applications and improvements of our approach.
-Section~\ref{sec:threats} reports threats to validity.
-Finally, Section~\ref{sec:conclusions} concludes the article.
+Next, we present the current body of knowledge in section~\ref{sec:related}.
+Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was introduced in the source code, followed by the results obtained after applying our approach to a selection of OpenStack bug fixes in Section~\ref{sec:results}.
+Section~\ref{sec:discussion} answers the research questions and discusses potential applications and improvements of our approach.
+After reporting the limitations and threats to validity in Section~\ref{sec:threats}, we draw some conclusions in Section~\ref{sec:conclusions}.
 
@@
 \label{sec:related}
-The first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}.
-Currently, is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and delete lines between the bug-fix and its previous version.
-SZZ uses CVS annotate command to identify the last commit that touched these lines.
 
-An improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion.
-Also, they deleting some false positives as blank spaces, changes in the format or changes in the comments.
+The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwersky et al.~ \cite{sliwerski2005changes}.
+Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
+The SZZ algorightm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{anotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.
 
-Other methodology to identify the origins of a bug is describes in \cite{sinha2010buginnings}, this work doesn't present a text-based technique as SZZ, the authors analyzed the effects of bug-fix changes on program dependencies.
-Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.
+An improvement to the SZZ algorithm is described by Kim et al.~\cite{kim2006automatic}.
+There the authors used annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion.
+Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments.
 
-These two approach have the similar ideas: (1) find the differences between the bug-fix version of and the previous version of the file to recognize those changes done by bug-fix commit.
-(2) look back in the code revision history until identify which version touched the lines affected in the bug-fix for the last time.
+Sinha et al.
+present another technique to identify the origins of a bug in~\cite{sinha2010buginnings}.
+Their technique is not text-based technique, as the SZZ algorithm, as the authors analyze the effects of bug-fix changes on program dependencies.
+So, taking into account the semantics of the source code they achieved higher accuracy in identifying the origins of a bug.
 
-Exists several articles based on SZZ such as \cite{williams2008szz} revisited SZZ algorithm, tracking bug-inducing changes and identify change types of them.
-Also, in \cite{yangbug} the authors applied this algorithm to find out what kind of bug-inducing changes are likely to become in a great threat after being marked as bug-fix changes.In addition, new techniques in bug prediction are based in this algorithm such as \cite{kim2008classifying} which was the first work classifying file changes as buggy or clean using change information features and source code terms.
+The two approaches have some metodological patterns in common:
+
+\begin{enumerate}
+  \item They find the differences between the bug-fix version and the previous version of the file to recognize those changes done by the bug-fix commit. 
+  \item They look back in the code revision history until they identify which version touched the lines affected in the bug-fix for the last time.
+\end{enumerate}
+
+FIXME: This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.
+
+The SZZ algorithm (and its \emph{successors}) have been widely used in the researc community.
+Williams et al.
+revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
+Yang et al.
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes
+Finally, some bug prediction algorithms are based on SZZ; Kim et al.
+showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.
+
+FIXME: maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere.
 
 %In addition some tools are based on SZZ too such as \cite{} 
-Finally our idea.
+%Finally our idea.
 
@@
 %We present our approach to identify how and where a bug was inserted into the source code, causing a later fix.
-We extract all the data necessary to analyze when the bug was inserted from the issue tracking system and the code review system used by the project we are analyzing.
-OpenStack uses Launchpad\footnote{\url{https://launchpad.net/openstack}} and Gerrit\footnote{\url{https://review.openstack.org/}}.
 
-The Launchpad of each project works with issues reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
-But, in our study we are only interested in those tickets that describe a bug report and, in addition, have been closed with a merged in the code source to fix the bug.
-In this bug reports we can find a comment with the link of Gerrit where the bug was fixed.
-Is in Gerrit where we can see all the patchsets proposed and the comments done by the reviewers.
+All data needed to analyze when the bug was introduced can be obtained from the issue tracking systems and the code review systems used generally by free/open source software (FOSS) projects.
+In our analysis, we have used OpenStack, a cloud computing platform with a huge developing community (more than 5,000 developers) and significant industrial support from several major companies such as Red Hat, Intel, IBM, HP, etc.
+OpenStack, as many other FOSS projects nowadays, uses Launchpad\footnote{\url{https://launchpad.net/openstack}} as issue tracking system, and Gerrit\footnote{\url{https://review.openstack.org/}} to support their code review process.
 
-\subsection{Fist Stage: The Filtering}
+The Launchpad of each project works with issue reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
+In our study, however, we are only interested in those tickets that
+\begin{enumerate}
+  \item describe a bug report, and
+  \item that have been closed and merged in the code source to fix the bug.
+\end{enumerate}
+
+In these bug reports we can find a comment with the link of Gerrit where the bug was fixed. Is in Gerrit where we can see all the patchsets proposed and the comments done by the reviewers.
+
+\subsection{Fist Stage: Filtering}
 \label{sec:firstStage}
+
 In our approach, first of all we must identifying which of those issues extracted from Launchpad are bug reports.
@@
 OpenStack was particularly of interest because of its continuously evolving due to its very active community.
-Although its short life, only five years, more than 5 thousand of researchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project \footnote{\url{http://activity.openstack.org/dash/browser/}}.
-Furthermore, all history is saved and available in a version control system, being able to access to its issue tracking system \footnote{\url{https://launchpad.net/openstack}} and the source code review \footnote{\url{https://review.openstack.org/}}
+Although its short life, only five years, more than 5 thousand of researchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project\footnote{\url{http://activity.openstack.org/dash/browser/}}.
+Furthermore, all history is saved and available in a version control system, being able to access to its issue tracking system\footnote{\url{https://launchpad.net/openstack}} and the source code review\footnote{\url{https://review.openstack.org/}}
 
@@
 %\begin{center} {\footnotesize
-\caption{ Commits per Project in OpenStack}
-\label{tab:OpenStack}
-\begin{tabular}{lll}
+\begin{tabular}{lrr}
 \toprule[0.3mm]%{\smallskip}
-  & All History \kern 1pc & Last Year (2015) \\\hline
+  & All History  & Last Year (2015) \\\hline
 Nova    \kern 1pc & 14,558 & 3,283 \\
@@
 \end{tabular} %}
+\caption{ Commits per Project in OpenStack}
+\label{tab:OpenStack}
+
 %\end{center}
@@
 %\begin{center} {\footnotesize
-\caption{ Statistics of each researcher in the classification}
-\label{tab:2}
 \begin{tabular}{lllll}
@@
 \end{tabular} %}
+\caption{ Statistics of each researcher in the classification}
+\label{tab:2}
 %\end{center}
@@
 \begin{center} {\footnotesize
-\caption{ Concordance between each developer in each repository}
-\label{tab:3}
 \begin{tabular}{llllll}
@@
 \end{tabular} }
+\caption{ Concordance between each developer in each repository}
+\label{tab:3}
 \end{center}
@@
 \begin{center} {\footnotesize
-\caption{ Responsibility of each previous commit before and after deleting the noise in the results}
-\label{tab:responsability}
 \begin{tabular}{lcc}
@@
 \end{tabular} }
+\caption{ Responsibility of each previous commit before and after deleting the noise in the results}
+\label{tab:responsability}
 \end{center}
@@
 \begin{center} {\footnotesize
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{tab:secondStage}
 \begin{tabular}{lcc}
@@
 \end{tabular} }
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{tab:secondStage}
 \end{center}
@@
 Also, we looked the distribution of the previous commit in each Bug Report, Table \ref{tab:secondStage2}, we observed that the most common distribution in the relationship between previous commit and bug report is one previous commit per Bug Report, following by the second common distribution, two previous commit per Bug Report.
+
 \begin{table*}[htb]
 \begin{center} {\footnotesize
-\caption{ Distribution of number of previous commit per Bug Report in each project}
-\label{tab:secondStage2}
 \begin{tabular}{lccccc}
@@
 \end{tabular} }
+\caption{ Distribution of number of previous commit per Bug Report in each project}
+\label{tab:secondStage2}
 \end{center}
@@
 We obtained that in 8 Bug Reports all the previous commits were responsible, in 30 Bug reports at least one of their previous commit caused the bug and in 11 bug report none of their previous commits inserted the bug.
+
 \begin{table*}[htb]
 \begin{center} {\footnotesize
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{tab:secondStage3}
 \begin{tabular}{lccccc}
@@
 \end{tabular} }
+\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\label{tab:secondStage3}
 \end{center}
@@
 \label{sec:discussion}
+
 \fbox{\begin{minipage}{25em}
+
 \textbf{RQ1: Using all the information available in the bug tracking system and code review system related a fix-bug, we have obtained that this fix-bug were real Bug Reports in a 72\% of the tickets analyzed}
 \end{minipage}}
+
 \fbox{\begin{minipage}{25em}
@@
 \end{minipage}}
-\\
-- No todos los casos son tan claros como los mostrados en los ejemplos ....
-- Casuistica del common juidment
-- Hemos sido conservadores
--Hemos utilizado la herramienta porque es un proceso complicado
+
+\begin{enumerate}
+ \item No todos los casos son tan claros como los mostrados en los ejemplos ....
+ \item Casuistica del common juidment
+ \item Hemos sido conservadores
+ \item Hemos utilizado la herramienta porque es un proceso complicado
+\end{enumerate}
+
 Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
+
 \begin{enumerate}
@@
 \section{Acknowledgments}
-We thank the two PhD students, Dorealda Dalipaj and Nelson Sekitoleko, that participated differentiating Bug report from the others.
-Also, we thank Bitergia \footnote{\url{http://bitergia.com/}} to explain its available database of OpenStack.
-Finally,thanks the Spanish Government because all authors are funded in part by it, through project TIN2014-59400-R.
+We thank Dorealda Dalipaj and Nelson Sekitoleko, two PhD students in our research team, that participated in the process of classifying bug reports.
+We also want to express our gratitude to Bitergia\footnote{\url{http://bitergia.com/}} for the OpenStack database and the support they have provided when questions have arised.
+Finally, we would like to acknowledge the Spanish Government because all authors are funded in part by it, through project TIN2014-59400-R.
 

### 2016-01-29 paperMSR.tex
Añadiendo y corrigiendo referencias.

@@
 
-\title{Who introduced this bug? \\ Don't look only at the previous commit!}
+\title{Who introduced this bug? \\ It may not have been in the previous commit!}
 %\subtitle{[Extended Abstract]
@@
 
-FIXME: maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere.
+FIXME: maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
+There the talk is precisely about those bugs whose origina are elsewhere.
+Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}
 
@@
 The Launchpad of each project works with issue reports called tickets, which describe bug reports, feature requests, maintenance tickets, and even design discussions.
-In our study, however, we are only interested in those tickets that
+In our study, however, we are only interested in those tickets that have following properties:
+
 \begin{enumerate}
-  \item describe a bug report, and
-  \item that have been closed and merged in the code source to fix the bug.
+  \item They describe a bug report, and
+  \item They have been closed and merged in the code source to fix the described bug.
 \end{enumerate}
 
-In these bug reports we can find a comment with the link of Gerrit where the bug was fixed. Is in Gerrit where we can see all the patchsets proposed and the comments done by the reviewers.
+In these bug reports we can find a comment with the link to Gerrit where the bug was fixed. It is in Gerrit where we can see all the patchsets proposed and the comments done by the reviewers.
 
@@
 
-In our approach, first of all we must identifying which of those issues extracted from Launchpad are bug reports.
-But, this is not a trivial task and we performed this identification using a web tool\footnote{\url{bugtracking.libresoft.es}} development to provide the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
-The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports.
+First, we have to identify what issues found in Launchpad are bug reports.
+This is not a trivial task and is labour intensive as it has to be done manually.
+As the process is repetitive, we developed a web-based tool\footnote{\url{bugtracking.libresoft.es}} that helps in the classification process.
+This tool offers all relevant information required to decide if an issue corresponds to a bug report or not.
+The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency in the identification of bug reports.
 
-During the identification of the issues we have to take into account the next parameters for each ticket, the title and the description of the issue report and the description of the fix commit.
-Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
-Each ticket was then categorized into one of three following groups.
+During the identification of the issues, we have to take into account the next parameters for each ticket:
+
+\begin{itemize}
+  \item The title of the issue report
+  \item The description of the issue report
+  \item The description of the fix commit
+  \item The changes to the source code, as sometimes neither the descriptions nor the comments clarified the underlying ticket. FIXME: what comments?
+\end{itemize}
+
+Each ticket was then categorized into one of three following groups:
+
 \begin{enumerate}
-  \item The ticket describes a bug report.
-  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
-  \item The ticket presents a vague description and cannot be classified without doubts.
+  \item Group 1 (\textit{Bug Report}): The ticket describes a bug report.
+  \item Group 2 (\textit{Not Bug Report}): The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
+  \item Group 3 (\textit{Undecided}): The ticket presents a vague description and cannot be classified without doubts.
 \end{enumerate}
 
-Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{Not Bug Report} and Group 3 as \textit{Undecided}.
+From the experience of analysing a small number of tickets, we agreed on following four criteria:
 
-As result of analyze the tickets, main differences extracting data and to classifying tickets were found. So, we agree to follow the next four criteria: 
-\begin{itemize}
-    \item When there are only test files in the ticket, we classified it as note being a bug report.
-Test files in a ticket will not be analyzed, they are indispensables and used as testing method to determine whether the code is fit for use.
-Sometimes the developers inserted the bug only in the test files, in these cases the ticket was not considered as bug report because the software works as expected only failed the test.
-    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, our criteria indicated that it was not a bug report because there is no failure. 
-    \item When the title described the program as not working as expected, our criteria indicated that it was a bug report. 
-    \item When the title described that updates were required, our criteria indicated that it was a bug report.
+\begin{enumerate}
+    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
+    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
+    \item When the ticket title described that updates were required, we agreed that it was a bug report.
 We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
-\end{itemize}
+    \item When only test files are affected in a ticket, we classified it as not being a bug report.
+Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use.
+When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails.
+FIXME: no se repiten las frases?
+\end{enumerate}
 
@@
 In this case, the ticket was classified into the \textit{Undecided} group.
+
 \subsection{Second Stage: Who caused the Bug?}
 \label{sec:secondStage}
+
 The next part is focusing on analyzing the previous commit in the \textit{Bug Report} group.

### 2016-01-29 paperMSR.tex
Retocando las tablas y alguna cosa más. Luego espero seguir

@@
 
-\title{Who introduced this bug? \\ It may not have been in the previous commit!}
+\title{Who introduced this bug? \\ It may not have been caused by the previous commit!}
 %\subtitle{[Extended Abstract]
@@
 Section~\ref{sec:discussion} answers the research questions and discusses potential applications and improvements of our approach.
-After reporting the limitations and threats to validity in Section~\ref{sec:threats}, we draw some conclusions in Section~\ref{sec:conclusions}.
+After reporting the limitations and threats to validity in Section~\ref{sec:threats}, we draw some conclusions and point out some potential future work in Section~\ref{sec:conclusions}.
 
@@
 All data needed to analyze when the bug was introduced can be obtained from the issue tracking systems and the code review systems used generally by free/open source software (FOSS) projects.
-In our analysis, we have used OpenStack, a cloud computing platform with a huge developing community (more than 5,000 developers) and significant industrial support from several major companies such as Red Hat, Intel, IBM, HP, etc.
-OpenStack, as many other FOSS projects nowadays, uses Launchpad\footnote{\url{https://launchpad.net/openstack}} as issue tracking system, and Gerrit\footnote{\url{https://review.openstack.org/}} to support their code review process.
+In our analysis, we have focused on Launchpad\footnote{\url{https://launchpad.net/}} as issue tracking system, and Gerrit\footnote{\url{https://www.gerritcodereview.com/}} as code review supporting tool, as they are widely used by FOSS projects nowadays, but our methodology should be generalizable to any such tool.
 
@@
 
+FIXME: aqui podemos poner un pantallazo de la interfaz web.
+
 Each ticket was then categorized into one of three following groups:
@@
 
-The next part is focusing on analyzing the previous commit in the \textit{Bug Report} group.
-For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and be sure that the lines was inserted/modified in the previous commit.
-This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.
+The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group.
+For that, we had to analyze the lines involved in the bug fix, in the \emph{parent} commit of the bug fix commit, and be sure that the lines were inserted/modified in the previous commit.
+This way we can be sure that the previous commit did not copy lines that contained the bug, because in that case, the previous commit is not responsible to cause the bug.
+FIXME: aclarar este parrafo!
 
-The analysis was done manually, and we used \textit{git blame} to see all the previous commit in each line of a involved file.
-Also, we used \textit{diff} to see all the differences between two files, in our case, the file is going to be the same but in different moment inside the control version system used.
+The analysis was done manually.
+We used \textit{git blame} to see the previous commit for each line of the involved file.
+Also, we used \textit{diff} to see the differences between the two files, in our case as the file is going to be the same, between the file in two different moments in the control version system.
 
-Te procedure following in each file involved in a fix bug is describing below;
+The procedure for each file involved in a bug fix is as follows:
+
 \begin{enumerate}
-  \item git checkout \textit{commit that fix the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fix the bug.
-  \item git checkout \textit{parent of commit that fix the bug}, git blame \textit{file involved}.
-In this step we can see all the previous commits involved in the different lines touched in the fix bug.
-  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. In this step we can ensure that the previous commit inserted these lines.
+  \item git checkout \textit{commit that fixed the bug}, git blame \textit{file involved}. In this step we can see the lines added, modified or deleted by the commit that fixed the bug.
+  \item git checkout \textit{parent of commit that fix the bug}, git blame \textit{file involved}. In this step we can see the previous commits for the different lines touched in the fixed bug.
+  \item git checkout \textit{parent of previous commit}, git blame \textit{file involved}. With this step we can ensure that the previous commit inserted these lines.
 \end{enumerate}
@@
 Finally we need to discard some noise presents in our final results according to the responsibility of the previous commit inserting the bug in the code source.
-Due to they were not responsible for cause the bug, we delete those previous commit which presents the following criteria;
+Due to they were not responsible for cause the bug, we delete those previous commit which presents the following criteria:
+
 \begin{itemize}
@@
 
-We validate our methodology analyzing 459 tickets in OpenStack.
+We validate our methodology analyzing 459 tickets from OpenStack.
+OpenStack is a cloud computing platform with a huge developing community (more than 5,000 developers) and significant industrial support from several major companies such as Red Hat, Intel, IBM, HP, etc.
 OpenStack was particularly of interest because of its continuously evolving due to its very active community.
-Although its short life, only five years, more than 5 thousand of researchers and more than 233 thousand of commits with more than 2 Million of lines of code have contributed in the development of the project\footnote{\url{http://activity.openstack.org/dash/browser/}}.
-Furthermore, all history is saved and available in a version control system, being able to access to its issue tracking system\footnote{\url{https://launchpad.net/openstack}} and the source code review\footnote{\url{https://review.openstack.org/}}
+Currently it has more than 233,000 commits with more than 2 million lines of code \footnote{\url{http://activity.openstack.org/dash/browser/}}.
+All its history is saved and available in a version control system, as well as its issue tracking system (Launchpad\footnote{\url{https://launchpad.net/openstack}}) and the source code review system (Gerrit\footnote{\url{https://review.openstack.org/}}).
 
-OpenStack is composed by 9 projects, but we only focused in the four of them, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack} these projects are really actives during all their history and in the last year.
+OpenStack is composed by 9 projects, but we only focused in four of them: Nova, Cinder, Neutron and Horizon.
+As can be seen from Table~\ref{tab:OpenStack}, these projects have been very active during their entier history, and in the last year.
+
 \begin{table}[htb]
@@
 %\begin{center} {\footnotesize
-\begin{tabular}{lllll}
+\begin{tabular}{lrrrr}
 \toprule[0.3mm]%{\smallskip}
   & Bug Report & Not Bug Report & Undecided & Total \\\hline
-R1  & (184)55\% & (115)34\% & (35)11\% & 334 \\
-R2  & (188)76\% & (54)22 \% & (7)3\% & 249 \\
-R3 & (188)56\% & (116)35\% & (30)9\% & 334 \\
-Finally & (209)72\% & (74)25\% & (9)3\% & 292 \\
+R1  & (184) 55\% & (115)34\% & (35) 11\% & 334 \\
+R2  & (188) 76\% & (54)22 \% & (7) 3\% & 249 \\
+R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
+Finally & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
 \bottomrule[0.3mm]
@@
 \begin{center} {\footnotesize
-\begin{tabular}{llllll}
+\begin{tabular}{lrrrrr}
 \toprule[0.3mm]%{\smallskip}
   & Nova & Cinder & Horizon & Neutron & Total\\\hline
-R1\&R2   & (44)70\% & (40)77\%  & (37)60\% & -        & 68\% \\
-R1\&R3   &  -        & (46)73\%  & (48)76\% & (26)62\% & 71 \% \\
-R2\&R3   & (41)66\% & (10)100\% & -         & -        &  71\% \\
+R1\&R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
+R1\&R3   &  -        & (46) 73\%  & (48) 76\% & (26) 62\% & 71\% \\
+R2\&R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
 \bottomrule[0.3mm]
@@
 \begin{center} {\footnotesize
-\begin{tabular}{lcc}
+\begin{tabular}{lrr}
 \toprule[0.3mm]

### 2016-01-29 paperMSR.tex
Added the screenshot of the Tool

@@
   \item The description of the fix commit
-  \item The changes to the source code, as sometimes neither the descriptions nor the comments clarified the underlying ticket. FIXME: what comments?
+  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad an Gerrit of each ticket, clarified the underlying ticket.
+FIXME: what comments?
 \end{itemize}
@@
 FIXME: aqui podemos poner un pantallazo de la interfaz web.
+We can see the web interface of the tool in the image \ref{fig:screenshot}, the left side is used to display the information extracted from Launchapad and Gerrit and the right part is the one in which the users can wirte and classify the ticket into one of the three groups.
+\begin{figure}[ht]
+\centering
+\includegraphics[height=12cm]{index.png}
+\caption{Screenshot of the tool used to classify the tickets}
+\label{fig:screenshot}       % Give a unique label
+\end{figure}
 
@@
     \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
-    \item When the ticket title described that updates were required, we agreed that it was a bug report.
+    \item When the ticket title described that updates were required, the ticket is a bug report.
 We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
@@
 
-The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group.
-For that, we had to analyze the lines involved in the bug fix, in the \emph{parent} commit of the bug fix commit, and be sure that the lines were inserted/modified in the previous commit.
-This way we can be sure that the previous commit did not copy lines that contained the bug, because in that case, the previous commit is not responsible to cause the bug.
+The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project.
+For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit.
+This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
 FIXME: aclarar este parrafo!

### 2016-01-29 paperMSR.tex
Added some FIXME

@@
 \end{minipage}}
-
+FIXME: Debería hablar sobre los siguientes puntos:
 \begin{enumerate}
@@
 And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
-[reference]
 \begin{enumerate}
@@
 \end{itemize}
+FIXME: Anñadir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.
 
@@
 With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
-Also, the software developers stand to benefit from identifying where the bug was inserted, improve their methodology.
+Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
 %How to plan to apply the knowledge in a way that can benefit software engineers.

### 2016-01-30 paperMSR.tex
Terminando los resultados. Con dudas de lo que querías decir

@@
 
-FIXME: aqui podemos poner un pantallazo de la interfaz web.
-We can see the web interface of the tool in the image \ref{fig:screenshot}, the left side is used to display the information extracted from Launchapad and Gerrit and the right part is the one in which the users can wirte and classify the ticket into one of the three groups.
+We can see a screenshot of the web interface of the tool in Figure~\ref{fig:screenshot}.
+The left side is used to display the information extracted from Launchpad and Gerrit, and the right part is the one in which the researchers can write and classify the ticket into one of the three groups.
+Additional meta-data, such as keywords, comments and the reviewer are included in the database.
+
 \begin{figure}[ht]
@@
 \includegraphics[height=12cm]{index.png}
-\caption{Screenshot of the tool used to classify the tickets}
+\caption{Screenshot of the tool used to classify the tickets.}
 \label{fig:screenshot}       % Give a unique label
@@
 
-We validate our methodology analyzing 459 tickets from OpenStack.
+We have validated our methodology analyzing tickets from OpenStack.
 OpenStack is a cloud computing platform with a huge developing community (more than 5,000 developers) and significant industrial support from several major companies such as Red Hat, Intel, IBM, HP, etc.
@@
 
-OpenStack is composed by 9 projects, but we only focused in four of them: Nova, Cinder, Neutron and Horizon.
+OpenStack is composed by 9 projects, but we only focused on the main four of them: Nova, Cinder, Neutron and Horizon.
 As can be seen from Table~\ref{tab:OpenStack}, these projects have been very active during their entier history, and in the last year.
@@
 Fuel    \kern 1pc & 9,139 & 5,123 \\
-Netron  \kern 1pc & 8,452 & 3,855 \\
+Neutron  \kern 1pc & 8,452 & 3,855 \\
 Horizon \kern 1pc & 4,871 & 1,994 \\
@@
 
-In this four projects we analyzed the relationship of bug fixes with their previous commits.
-In order to identify the moment in which the bug was injected into the source code.
-The first stage we did automatically using the tool and a double bind between three researchers, three PhD student  included me.
-The second stage was done manually and only me was involved analyzing this relationship.
+For these four projects we analyzed if bug fixes where introduce in their previous commits.
+For the first stage, we used the tool described in~\ref{sec:firstStage}.
+Each ticket was analyzed by two researchers independently.
+The second stage was done manually by the first author.
 %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
@@
 
-We extracted a total of 459 different tickets from the Launchpad of the four principal projects in OpenStack, 125 tickets from Nova, 125 tickets from cinder, 125 tickets from Horizon and 84 tickets from Neutron.
-These tickets first, were analyzed to identify those ones which were real bug reports.
-And secondly, each file was analyzed to obtain which previous commit inserted the bug causing the failure of the system and reporting the bug report.
+A total of 459 different tickets from the Launchpad of the four main projects in OpenStack: 125 tickets from Nova, 125 tickets from cinder, 125 tickets from Horizon and 84 tickets from Neutron.
 
@@
 
-We classify a total of 459 tickets using the tool.
-In 417 of the tickets, we used double bind analysis, and only those tickets classified as bug report by two of us, were considered in the next stage to analyze the relevance of their previous commits.
-
-The table \ref{tab:2} shows the percentage of each researcher after analyzing the tickets, and the number of tickets classified identically by two different researchers.
-Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly different with a higher number of tickets classified as Bug Report.
-
-Finally, the researchers identified in the same way 292 tickets, that is, their results matched in a 70\% of the cases.
-Obtaining 209 tickets classified as Bug report, 74 tickets classified as Not Bug Report and 9 tickets classified as Undecided.
+We classify a total of 459 tickets using the tool, resulting in 918 reviews.
+Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
 
@@
   & Bug Report & Not Bug Report & Undecided & Total \\\hline
-R1  & (184) 55\% & (115)34\% & (35) 11\% & 334 \\
-R2  & (188) 76\% & (54)22 \% & (7) 3\% & 249 \\
-R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
-Finally & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
+R1  & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
+R2  & (188) 76\% & (54) 22\% & (7) 3\% & 249 \\
+R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\ \hline
+Agree & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
 \bottomrule[0.3mm]
 \end{tabular} %}
-\caption{ Statistics of each researcher in the classification}
+\caption{Statistics for each researcher as a result of the classification process.
+For each researcher R, the number of tickets (and percentages) classified into the three groups is given.
+The \emph{Agree} row gives the number of tickets (and percentages) were two researchers agreed.}
 \label{tab:2}
@@
 
-Also we had measured the concordance in the classification of each developer according to the project analyzed.
-The table \ref{tab:3} shows that the concordant got between all the three research was very similar, around a 70\%.
-Furthermore, the concordance form each researcher with the rest always was up to 60\%.
+Table~\ref{tab:2} shows the classification percentages for each researcher after analyzing the tickets, and the number of tickets classified by two different researchers in the same group.
+%Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly different with a higher number of tickets classified as Bug Report.
+As a result, researchers identified 292 tickets in the same group, that is, their results matched in over 70\% of the cases.
+Of those, 209 tickets had been classified in the \emph{Bug report} group, 74 in the \emph{Not Bug Report} group and 9 tickets classified in the \emph{Undecided} group.
+
+We also measured the concordance in the classification of each developer according to the project analyzed (see table~\ref{tab:3}).
+Values obtained by the three researchers are very similar, in general around a 70\%.
+The concordance values were always above 60\%.
 
@@
   & Nova & Cinder & Horizon & Neutron & Total\\\hline
-R1\&R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
-R1\&R3   &  -        & (46) 73\%  & (48) 76\% & (26) 62\% & 71\% \\
-R2\&R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
+R1 -- R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
+R1 -- R3   &  -        & (46) 73\%  & (48) 76\% & (26) 62\% & 71\% \\
+R2 -- R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
 \bottomrule[0.3mm]
 \end{tabular} }
-\caption{ Concordance between each developer in each repository}
+\caption{Concordance among researchers for each repository.}
 \label{tab:3}
@@
 
+\vspace{0.2cm}
+\fbox{\begin{minipage}{25em}
+\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a fix-bug, we have obtained that in at least 72\% of the tickets analyzed the fix-bugs were real bug reports.}
+\end{minipage}}
+\vspace{0.1cm}
+
 \subsection{Second Stage}
@@
 
-At this stage, we analyzed the 209 we got a list with all the previous commits and we were be able to classified the previous commit/s as Responsible, Not Responsible or Undecided, taken into account that the bug could be inserted in different lines of different commits, but not everyone had to be responsible for the commit, sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
-In fact, the responsible can be only one of them, more than one or maybe none.
+In this stage we analyzed the 209 tickets classified as bug reports and their previous commits.
+The possible outcome was one of the following three options:
 
-We identified a total of 348 previous commits which can be responsible for inserting the line containing the bug.
-After analyzing the Bug Reports and their previous commits and discarded 40 of them because were noise, Table \ref{tab:responsability}, we got that 152 previous commit were responsible to cause the bug whereas 114 previous commit had not any responsibility in the failure of the system, and only in 42 previous commits we were unable to identify the cause of the bug.
+\begin{itemize}
+  \item Cause
+  \item No Cause
+  \item Undecided
+\end{itemize}
+
+This analysis takes into account that the bug could have been inserted in several lines in several commits, but not everyone had to be responsible for the commit; sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
+In fact, the cause could be found in a single commit, in many or even in none.
+FIXME: repasar este parrafo
+
+We identified a total of 348 previous commits which could be the cause of the 292 bugs under analysis, and analyzed the bug reports together with their previous commits.
+
+As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause.
+We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they were noise.
+FIXME: explicar que es eso de noise!
 
 \begin{table}[htb]
-\begin{center} {\footnotesize
+\begin{center}
 \begin{tabular}{lrr}
@@
   & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
-\raisebox{1ex}{Responsible} & 152 & 152 \\[0ex]
-\raisebox{1ex}{Not responsible} & 154 & 114 \\[0ex]
-\raisebox{1ex}{Undecided} & 42 & 42 \\[0ex]
+{Cause} & (152) 44\% & (152) 49\% \\[0ex]
+{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
+{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
 \bottomrule[0.3mm]
-\end{tabular} }
-\caption{ Responsibility of each previous commit before and after deleting the noise in the results}
+\end{tabular}
+\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
 \label{tab:responsability}
@@
 
-Furthermore, focusing on how many previous commits presented each Bug Report, we obtained that 131 had one previous commit implicated, whereas 58 had more than one previous commit implicated in their file/s.
+If we attend to how many previous commits each of the 292 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit.
+As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not the cause.
+For the 58 bugs that had more than one previous commit, a total number of 189 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
+
+% Furthermore, focusing on how many previous commits presented each Bug Report, we obtained that 131 had one previous commit implicated, whereas 58 had more than one previous commit implicated in their file/s.
 According to Table \ref{tab:secondStage}, from the 131, we obtained that 65 of them inserted the bug, but 30 of them were not responsible in the failure of the system.
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Responsible}     & 65 & 86 \\[0ex]
-\raisebox{1ex}{Not responsible} & 30 & 82 \\[0ex]
+\raisebox{1ex}{Cause}     & 65 & 86 \\[0ex]
+\raisebox{1ex}{Not cause} & 30 & 82 \\[0ex]
 \raisebox{1ex}{Undecided} & 36 & 11 \\[0ex]
@@
 \end{tabular} }
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
+\caption{Probability of the cause of the bug depending on how many previous commits the bug report had.}
 \label{tab:secondStage}
@@
 
-Also, we looked the distribution of the previous commit in each Bug Report, Table \ref{tab:secondStage2}, we observed that the most common distribution in the relationship between previous commit and bug report is one previous commit per Bug Report, following by the second common distribution, two previous commit per Bug Report.
+We also studied the distribution of the number of previous commits for each Bug Report.
+As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits.
 
@@
 
-Finally we wanted to know the responsibility practiced by each previous commit in the failure of a system, in other words, we were interested in analyze from those cases where exists more than one previous commit, how many of them inserted the bug in the code source, Table \ref{tab:secondStage3}.
-We obtained that in 8 Bug Reports all the previous commits were responsible, in 30 Bug reports at least one of their previous commit caused the bug and in 11 bug report none of their previous commits inserted the bug.
+Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them inserted the bug in the code source.
+Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug.
 
@@
 
+\vspace{0.2cm}
+\fbox{\begin{minipage}{25em}
+\textbf{RQ2: Only 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them did not introduce the bug in the code source.} 
+\end{minipage}}
+\vspace{0.1cm}
+
 \section{Discussion}
@@
 
-\fbox{\begin{minipage}{25em}
-
-\textbf{RQ1: Using all the information available in the bug tracking system and code review system related a fix-bug, we have obtained that this fix-bug were real Bug Reports in a 72\% of the tickets analyzed}
-\end{minipage}}
-
-\fbox{\begin{minipage}{25em}
-\textbf{RQ2: We have confirmed that 50\% of the previous commits analyzed caused the failure in the system, whereas the 37\% of them didn't injected any bug in the code source } 
-\end{minipage}}
 FIXME: Debería hablar sobre los siguientes puntos:
 \begin{enumerate}
- \item No todos los casos son tan claros como los mostrados en los ejemplos ....
+ \item No todos los casos son tan claros como los mostrados en los ejemplos....
  \item Casuistica del common juidment
@@
 \label{sec:conclusions}
+
 The empirical experiment carried out in OpenStack, supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not responsible inserting the bug.
@@
 \section{Acknowledgments}
+
 We thank Dorealda Dalipaj and Nelson Sekitoleko, two PhD students in our research team, that participated in the process of classifying bug reports.

### 2016-01-30 paperMSR.tex
Little changes in Results

@@
   \item The description of the fix commit
-  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad an Gerrit of each ticket, clarified the underlying ticket.
+  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket.
 FIXME: what comments?
@@
 
-This analysis takes into account that the bug could have been inserted in several lines in several commits, but not everyone had to be responsible for the commit; sometimes the previous commit copied lines from its previous commit or inserted comments and blank spaces.
-In fact, the cause could be found in a single commit, in many or even in none.
+This analysis takes into account that the bug could have been inserted in many lines belong to many differnt previous commits, but in fact, not all of them could cause the bug.
+Could happen that these previous commit copied lines from its previous commits or modified the comments and added blank spaces.
+Thus, the cause could be found in a single previous commit, in many or even in none.
 FIXME: repasar este parrafo
@@
 As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause.
-We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they were noise.
-FIXME: explicar que es eso de noise!
+We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file.
+FIXME: explicar que es eso de noise!, Con Noise me referia a los falsos positivos que puede haber en los commits previos, las líneas copiadas de otros commits o lineas en blanco, comentarios ...
 

### 2016-01-30 paperMSR.tex
añadidas mas cosas... i need info

@@
 
+\newif\ifdraft
+\drafttrue
+%\draftfalse
+
 \documentclass{sig-alternate-05-2015}
@@
 \usepackage{booktabs}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{xspace}
+
+\input{macros}
+
 \begin{document}
@@
 \alignauthor
-Jesus M. Gonz\'alez-Barahona\\
+Jes\'us M. Gonz\'alez-Barahona\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
@@
 Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed.
-FIXME: maybe something more here
+\grex{maybe we could say something more here}.
 \end{abstract}
@@
 This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
-FIXME: clarificar la frase anterior...
-no ha quedado muy claro.
+\grex{clarificar la frase anterior...
+no ha quedado muy claro.}
 
@@
 Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail.
-But in such cases, the source of the error cannot be FIXME assigned to a change performed in the previous commit, as in that moment it referred to a different API.
+But in such cases, the source of the error cannot be \grex{assigned} to a change performed in the previous commit, as in that moment it referred to a different API.
 
-FIXME: poner esto bien
+\grex{poner el siguiente parrafo bien}
 
-The goal of this paper is to find if the cause of the bug can be FIXME assigned to the previous commit, understanding that at the time when the previous commit is introduced
+The goal of this paper is to find if the cause of the bug can be \grex{assigned} to the previous commit, understanding that at the time when the previous commit is introduced
 
-not all times the code analyzed was so easy as the code showed in figures \ref{fig:1} and \ref{fig:3}.
+not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
 So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
@@
 
-FIXME: rephrase RQs
+\grex{rephrase RQs}
 
@@
 
-FIXME: This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.
+\grex{This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.}
 
@@
 
-FIXME: maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
+\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
 There the talk is precisely about those bugs whose origina are elsewhere.
-Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}
+Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}
 
@@
   \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket.
-FIXME: what comments?
+\grex{what comments?}
 \end{itemize}
@@
 When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails.
-FIXME: no se repiten las frases?
+\grex{no se repiten las frases?}
 \end{enumerate}
@@
 This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
-FIXME: aclarar este parrafo!
+\grex{aclarar este parrafo!}
 
@@
 This analysis takes into account that the bug could have been inserted in many lines belong to many differnt previous commits, but in fact, not all of them could cause the bug.
-Could happen that these previous commit copied lines from its previous commits or modified the comments and added blank spaces.
+It could have happened that in the previous commit lines had been copied from further previous commits, or comments may have been modified, or blank spaces/lines have been added.
 Thus, the cause could be found in a single previous commit, in many or even in none.
-FIXME: repasar este parrafo
+\grex{repasar este parrafo}
 
@@
 We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file.
-FIXME: explicar que es eso de noise!, Con Noise me referia a los falsos positivos que puede haber en los commits previos, las líneas copiadas de otros commits o lineas en blanco, comentarios ...
+\grex{explicar que es eso de noise!} \gema{Con Noise me referia a los falsos positivos que puede haber en los commits previos, las lineas copiadas de otros commits o lineas en blanco, comentarios ...}
 
@@
 
-FIXME: Debería hablar sobre los siguientes puntos:
+\gema{Deberia hablar sobre los siguientes puntos:} \grex{Puedes elaborar un poco mas cada punto, aunque sea en castellano?}
 \begin{enumerate}
@@
 \end{itemize}
-FIXME: Anñadir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.
+
+\gema{Incluir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.}
 

### 2016-01-30 paperMSR.tex
doing some comm

--- 2016-01-30 paperMSR.tex
@@
 
-In this stage we analyzed the 209 tickets classified as bug reports and their previous commits.
+In this stage we analyzed the 189 tickets classified as bug reports and their previous commits.
 The possible outcome was one of the following three options:
@@
 
-We identified a total of 348 previous commits which could be the cause of the 292 bugs under analysis, and analyzed the bug reports together with their previous commits.
+We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis, we analyzed the bug reports together with their previous commits discarting these cases where the previous commit was false positives such as blank lines, changes in comments or even a change in the version of the file., so in total we had analyzed 308 previous commit.
 
-As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause.
-We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file.
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commit, 152 of them have been considered the cause of the bug, whereas 114 were not the cause.
+We were unable to identify the cause of the bug in 42 cases, due to there was only added lines or our knowleadge about the code.
+
 FIXME: explicar que es eso de noise!, Con Noise me referia a los falsos positivos que puede haber en los commits previos, las líneas copiadas de otros commits o lineas en blanco, comentarios ...
@@
 
-If we attend to how many previous commits each of the 292 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit.
-As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not the cause.
-For the 58 bugs that had more than one previous commit, a total number of 189 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
+If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit.
+As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
+For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
 
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Cause}     & 65 & 86 \\[0ex]
-\raisebox{1ex}{Not cause} & 30 & 82 \\[0ex]
-\raisebox{1ex}{Undecided} & 36 & 11 \\[0ex]
+\raisebox{1ex}{Cause}     & (65)50\% & (86)48\% \\[0ex]
+\raisebox{1ex}{Not cause} & (30)23\% & (82)46\% \\[0ex]
+\raisebox{1ex}{Undecided} & (36)27\% & (11)6\% \\[0ex]
 \bottomrule[0.3mm]
 \end{tabular} }
-\caption{Probability of the cause of the bug depending on how many previous commits the bug report had.}
+\caption{Probability of the cause of the bug when the bug report present one previous commit or more than one previous commit.}
 \label{tab:secondStage}
@@
 \end{table}
-
+[Los resultados que he obtenido y que queria plasmar en las tablas son:
+- He analizado 189 bugs reports\\
+- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.\\
+- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.\\
+- Además he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
+etc.\|\\\
+- Finalmente realicé ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
+Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente había un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
+Por tanto la tabla 7 muestra cual es la responsabilidad (tods responsables, al menos uno ningun responsable y desconozco la responsabilidad) de los coommits previos presentes en un bug report.
+Por ejemplo, bugs reports que tenían dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report había al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.
+]
 We also studied the distribution of the number of previous commits for each Bug Report.
@@
 \end{tabular} }
-\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
-\label{tab:secondStage3}
+\caption{ Number of previous commit responsibles per bug report}
 \end{center}
@@
 \begin{enumerate}
- \item No todos los casos son tan claros como los mostrados en los ejemplos....
+ \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se han anadido codigo 
  \item Casuistica del common juidment

### 2016-01-30 paperMSR.tex

--- 2016-01-30 paperMSR.tex
@@
 
-We identified a total of 348 previous commits which could be the cause of the 292 bugs under analysis, and analyzed the bug reports together with their previous commits.
+We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis, we analyzed the bug reports together with their previous commits discarting these cases where the previous commit was false positives such as blank lines, changes in comments or even a change in the version of the file., so in total we had analyzed 308 previous commit.
+
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commit, 152 of them have been considered the cause of the bug, whereas 114 were not the cause.
+We were unable to identify the cause of the bug in 42 cases, due to there was only added lines or our knowleadge about the code.
 
@@
 \end{table}
-
+\gema{Los resultados que he obtenido y que queria plasmar en las tablas son:
+- He analizado 189 bugs reports\\
+- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.\\
+- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.\\
+- Además he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
+etc.\|\\\
+- Finalmente realicé ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
+Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente había un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
+Por tanto la tabla 7 muestra cual es la responsabilidad (tods responsables, al menos uno ningun responsable y desconozco la responsabilidad) de los coommits previos presentes en un bug report.
+Por ejemplo, bugs reports que tenían dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report había al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.
+}
 We also studied the distribution of the number of previous commits for each Bug Report.
@@
 \begin{enumerate}
- \item No todos los casos son tan claros como los mostrados en los ejemplos....
- \item Casuistica del common juidment
- \item Hemos sido conservadores
- \item Hemos utilizado la herramienta porque es un proceso complicado
+ \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se han anadido códifo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo.
+ \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han añadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la línea se olvido de realizar dichas comporbaciones, y en ese caso sería el causante del bug.
+Pero existen casos que la comprobación que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error.
+Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provocó el error, porque realmente era dificil saberlo.
+ \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
 \end{enumerate}

### 2016-01-30 paperMSR.tex
Added some comments more

@@
 \grex{maybe we could say something more here}.
+\gema{podriamos escribir algunos porcentajes de lo que hemos encontrado, algo asi como que un 37\% de los commits previos no son responsables de introducir niingun bug}
 \end{abstract}
@@
 \grex{This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.}
+\gema{ He buscado en google schoolar las entradas que tiene SZZ algoritm y aparecen 1170 resultados desde 2006 que es cuando sacaron el articulo, pero alguna de las entradas solo contine algorithm y no SZZ algoritm}
 
@@
 Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}
-
+\gema{Hay que incluir lo que nuestro articulo aporta al estado actual}
 %In addition some tools are based on SZZ too such as \cite{} 
@@
 \end{table}
-\gema{Los resultados que he obtenido y que queria plasmar en las tablas son:
-- He analizado 189 bugs reports\\
-- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.\\
-- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.\\
-- Además he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
-etc.\|\\\
-- Finalmente realicé ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
+\gema{Los resultados que he obtenido y que queria plasmar en las tablas son:}
+\gema{- He analizado 189 bugs reports}\\
+\gema{- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.}\\
+\gema{- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.}\\
+\gema{- Además he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
+etc.}\\
+\gema{- Finalmente realicé ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
 Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente había un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
 Por tanto la tabla 7 muestra cual es la responsabilidad (tods responsables, al menos uno ningun responsable y desconozco la responsabilidad) de los coommits previos presentes en un bug report.
-Por ejemplo, bugs reports que tenían dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report había al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.
-}
+Por ejemplo, bugs reports que tenían dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report había al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.}
 We also studied the distribution of the number of previous commits for each Bug Report.
@@
 
+\gema{Algunos de los problemas que nos hemos encontrado durante el analisis y que podrian ser resueltos de otra forma diferente a la nuestra y quizas puede que varie algo los resultados no lo se}
 Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
@@
 \end{enumerate}
+\gema{anadir ademas que los resultados optenidos presentan una oposicion a la idea actual de que el previo commit introdujo el error}
 

### 2016-01-30 paperMSR.tex
Minor comments

@@
 
+\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
+
 The remainder of this paper is structured as follows.
@@
 Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}
-\gema{Hay que incluir lo que nuestro articulo aporta al estado actual}
+
+\gema{Hay que incluir lo que nuestro articulo aporta al estado actual} \grex{Buena idea, pero eso es mejor ponerlo en la intro.}
 %In addition some tools are based on SZZ too such as \cite{} 
@@
 \gema{- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.}\\
-\gema{- Además he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
+\gema{- Ademas he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
 etc.}\\
-\gema{- Finalmente realicé ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
-Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente había un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
+\gema{- Finalmente realice ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
+Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente habia un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
 Por tanto la tabla 7 muestra cual es la responsabilidad (tods responsables, al menos uno ningun responsable y desconozco la responsabilidad) de los coommits previos presentes en un bug report.
-Por ejemplo, bugs reports que tenían dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report había al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.}
+Por ejemplo, bugs reports que tenian dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report habia al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.}
 We also studied the distribution of the number of previous commits for each Bug Report.
@@
 \caption{ Number of previous commit responsibles per bug report}
+\label{tab:secondStage3}
 \end{center}
@@
 \begin{enumerate}
- \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se han anadido códifo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo.
- \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han añadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la línea se olvido de realizar dichas comporbaciones, y en ese caso sería el causante del bug.
-Pero existen casos que la comprobación que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error.
-Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provocó el error, porque realmente era dificil saberlo.
+ \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se ha anadido codigo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo.
+ \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han anadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la linea se olvido de realizar dichas comporbaciones, y en ese caso seria el causante del bug.
+Pero existen casos que la comprobacion que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error.
+Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provoco el error, porque realmente era dificil saberlo.
  \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
@@
 
-\gema{Incluir un link con la web en la que pondré todos los datos y scripts utilizados para los datos.}
+\gema{Incluir un link con la web en la que pondre todos los datos y scripts utilizados para los datos.}
 

### 2016-01-30 paperMSR.tex
added text to introduction

@@
      \item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+     \item \gema{RQ1: How we can identify a change done to fix a bug inserted in the code source?
+Que tal esta forma de plantear la RQ1?
+Esta pregunta se refiere a como podemos diferenciar los bug reports de los otros pero realizada desde el punto de vista del comit previo }
     %\item RQ2:  How often is the bug caused in the previous commit?
-     \item RQ2:  When did the previous commit introduce the line with the bug into the source code?
+     \item RQ2:  When did the previous commit introduce the line containing the bug into the source code?
 \end{itemize}
@@
 \grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
+With this paper we try to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software.
+Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process.
 
@@
 
-\gema{Hay que incluir lo que nuestro articulo aporta al estado actual} \grex{Buena idea, pero eso es mejor ponerlo en la intro.}
+\gema{Hay que incluir lo que nuestro articulo aporta al estado actual} \grex{Buena idea, pero eso es mejor ponerlo en la intro.}\gema{Ya esta puesto}
 %In addition some tools are based on SZZ too such as \cite{} 
@@
   \item The description of the fix commit
-  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket.
-\grex{what comments?}
+  \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers and reviewers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket.
+\grex{what comments?}\gema{los comentarios de los reviewers que podemos ver en Luanchpad y Gerrit }
 \end{itemize}
@@
 When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails.
-\grex{no se repiten las frases?}
+\grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}
 \end{enumerate}
@@
 
-This analysis takes into account that the bug could have been inserted in many lines belong to many differnt previous commits, but in fact, not all of them could cause the bug.
-It could have happened that in the previous commit lines had been copied from further previous commits, or comments may have been modified, or blank spaces/lines have been added.
+This analysis takes into account that the bug could have been inserted in many lines belong to many different previous commits, but in fact, not all of them could cause the bug.
+Sometimes happens that in the previous commit some lines had been copied from further previous commits, or comments may have been modified, or blank spaces/lines have been added.
 Thus, the cause could be found in a single previous commit, in many or even in none.
-\grex{repasar este parrafo}
+\grex{repasar este parrafo} \gema{Que tal ahora?
+esta mas claro?}
 

### 2016-01-31 paperMSR.tex
Alpha version. Let's see if we get a good paper still

@@
 To this end, we conducted an observational study on bug reports, their fixes, and their corresponding previous commits for the OpenStack project.
-Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed.
-\grex{maybe we could say something more here}.
-\gema{podriamos escribir algunos porcentajes de lo que hemos encontrado, algo asi como que un 37\% de los commits previos no son responsables de introducir niingun bug}
+Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction (at least 37\%) of the bugs analyzed.
 \end{abstract}
@@
 When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code.
-It seems reasonable to assume that the previous modification of this line or these lines are the cause of the bug; this previous modification is \textit{the previous commit}.
-But in fact, to find when and where a bug was introduced in the source code is not a trivial task.
-This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
-\grex{clarificar la frase anterior...
-no ha quedado muy claro.}
+It may semm at first reasonable to assume that previous modifications of this line or these lines are the cause of the bug; the previous modification is what is called \textit{the previous commit}.
+But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption.
+This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
+\grex{Gema, puedes clarificar la frase anterior?
+No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}
 
@@
 Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail.
-But in such cases, the source of the error cannot be \grex{assigned} to a change performed in the previous commit, as in that moment it referred to a different API.
+But in such cases, the source of the error cannot be attributed to a change performed in the previous commit, as in that moment it referred to a different API.
 
-\grex{poner el siguiente parrafo bien}
+The goal of this paper is to find if the cause of the bug can be attributed to the previous commit.
+A previous commit will be identified as the cause if the buggy behavior is present at the time it is performed.
+If the buggy behavior is due to other changes in the software, e.g., due to its evolution or changes elsewhere in the source code base, the previous commit should not be considered as the cause of a bug.
 
-The goal of this paper is to find if the cause of the bug can be \grex{assigned} to the previous commit, understanding that at the time when the previous commit is introduced
-
-not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
-So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
-
-In detail, in this paper we attempt to address the following research question regarding who introduced the bug in the source code:
-
-\grex{rephrase RQs}
+To achieve our goal, this paper attempts to address the following research questions:
 
@@
     %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-     \item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+    %\item RQ1:     How can we know that a change was done to fix a bug in the source code? How can we identify them?
      \item \gema{RQ1: How we can identify a change done to fix a bug inserted in the code source?
@@
 Esta pregunta se refiere a como podemos diferenciar los bug reports de los otros pero realizada desde el punto de vista del comit previo }
+     \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
     %\item RQ2:  How often is the bug caused in the previous commit?
-     \item RQ2:  When did the previous commit introduce the line containing the bug into the source code?
+     \item RQ2: How often is the previous commit the cause of the bug?
 \end{itemize}
 
-\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
-With this paper we try to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+Answering RQ1 is a prerequisite to be able to answer RQ2.
+This is because (real) bugs are managed together in an issue-tracking tool with feature requests, optimizations, test files, among others.
+As we are only interested in our research in the actual bugs, we need to identify those as a previous step to analyze if they have been caused by the previous commit.
+
+With this paper we try to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
 Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software.
 Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process.
+\grex{reescribir este parrafo para que quede mas claro.}
 
@@
 
-The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwersky et al.~ \cite{sliwerski2005changes}.
+The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwersky et al.~\cite{sliwerski2005changes}.
 Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
@@
 
-\grex{This last paragraph should be clarified, and more on papers using the SZZ algorithm! Maybe we should state how many papers in total exist based or using SZZ in Google Scholar.}
-\gema{ He buscado en google schoolar las entradas que tiene SZZ algoritm y aparecen 1170 resultados desde 2006 que es cuando sacaron el articulo, pero alguna de las entradas solo contine algorithm y no SZZ algoritm}
-
-The SZZ algorithm (and its \emph{successors}) have been widely used in the researc community.
 Williams et al.
@@
 Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes~\cite{yangbug}.
 Finally, some bug prediction algorithms are based on SZZ; Kim et al.
-showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.
+showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
+\grex{Creo que deberiamos hablar de mas papers que hacen uso de SZZ y derivados}.
 
-\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
-There the talk is precisely about those bugs whose origina are elsewhere.
-Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}
+The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community.
+Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January
+2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.
 
-\gema{Hay que incluir lo que nuestro articulo aporta al estado actual} \grex{Buena idea, pero eso es mejor ponerlo en la intro.}\gema{Ya esta puesto}
+In the research literature, we can already find methods that consider other sources of information than the previous commit. In fact, German et al.~\cite{german2009change} 
+point out that software is in constant change, and that changes performed may have impact across the whole system and may lead to the manifestation of bugs in unchanged parts.
+In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base.
+
 %In addition some tools are based on SZZ too such as \cite{} 
@@
   \item The changes to the source code, as sometimes neither the descriptions nor the comments by developers and reviewers in the Launchpad and Gerrit of each ticket, clarified the underlying ticket.
-\grex{what comments?}\gema{los comentarios de los reviewers que podemos ver en Luanchpad y Gerrit }
 \end{itemize}
@@
     \item When only test files are affected in a ticket, we classified it as not being a bug report.
-Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use.
+We consider bug errors in test files are a different type of bugs, as the software may still work as expected.
+\grex{no se si esto es lo que querias decir}
+
+%    Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use.
 When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails.
@@
 The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project.
+
+\grex{Este parrafo deberia decir lo mismo que el anterior. Si es asi, borremos el anterior}
+In this second part, our work was focused on analyzing the previous commit exclusively for those tickets classified in the \textit{Bug Report} group.
+Therefore we had to locate the line that contained the bug, inquire the reason of the software failure, and gathering additional information on the context of the project.
+
 For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit.
 This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
-\grex{aclarar este parrafo!}
+\grex{Gema, puedes aclarar este parrafo?
+Que es el "parent" commit?
+Es lo mismo que el previous commit?
+Es la primera vez que hablamos de el.
+Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}
 
@@
 
-We classify a total of 459 tickets using the tool, resulting in 918 reviews.
+We classify a total of 459 tickets using the tool, resulting in 918 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}.
 Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
 
-\begin{table}
+\begin{table*}
 \centering
 %\begin{center} {\footnotesize
-\begin{tabular}{lrrrr}
+\begin{tabular}{l|rrr|r}
 \toprule[0.3mm]%{\smallskip}
   & Bug Report & Not Bug Report & Undecided & Total \\\hline
-R1  & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
-R2  & (188) 76\% & (54) 22\% & (7) 3\% & 249 \\
-R3 & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\ \hline
-Agree & (209) 72\% & (74) 25\% & (9) 3\% & 292 \\
+R1  & (184) 55\% & (115) 34\% & (35) 11\% & 334 (100\%) \\
+R2  & (188) 76\% & (54) 22\% & (7) ~3\% & 249 (100\%) \\
+R3 & (188) 56\% & (116) 35\% & (30) ~9\% & 334 (100\%) \\ \hline
+Agree & (209) 72\% & (74) 25\% & (9) ~3\% & 292 (100\%) \\
 \bottomrule[0.3mm]
@@
 For each researcher R, the number of tickets (and percentages) classified into the three groups is given.
-The \emph{Agree} row gives the number of tickets (and percentages) were two researchers agreed.}
+The \emph{Agree} row gives the number of tickets (and percentages) where two researchers agreed.}
 \label{tab:2}
 %\end{center}
-\end{table}
+\end{table*}
+
+%\grex{Tiene sentido añadir porcentajes, como he hecho a la columna de Total?}
 
@@
 
-\begin{table}[htb]
+\begin{table*}[htb]
 \begin{center} {\footnotesize
-\begin{tabular}{lrrrrr}
+\begin{tabular}{l|rrrr|r}
 \toprule[0.3mm]%{\smallskip}
   & Nova & Cinder & Horizon & Neutron & Total\\\hline
-R1 -- R2   & (44) 70\% & (40) 77\%  & (37) 60\% & -        & 68\% \\
-R1 -- R3   &  -        & (46) 73\%  & (48) 76\% & (26) 62\% & 71\% \\
-R2 -- R3   & (41) 66\% & (10) 100\% & -         & -        &  71\% \\
+R1 -- R2   & (44) 70\% & (40) ~77\%  & (37) 60\% & -        & (121) 68\% \\
+R1 -- R3   &  -        & (46) ~73\%  & (48) 76\% & (26) 62\% & (120) 71\% \\
+R2 -- R3   & (41) 66\% & (10) 100\% & -         & -        &  (51) 71\% \\
 \bottomrule[0.3mm]
@@
 \end{center}
-\end{table}
+\end{table*}
+
+\grex{Tiene sentido anadir numeros absolutos, como he hecho a la columna de Total en la Tabla 3?}
 
@@
 
+\grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}
+
 \subsection{Second Stage}
@@
 
-In this stage we analyzed the 189 tickets classified as bug reports and their previous commits.
-The possible outcome was one of the following three options:
+In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} as bug reports and their previous commits.
+The possible outcome of the analysis was one of the following three options:
 
@@
 
-This analysis takes into account that the bug could have been inserted in many lines belong to many different previous commits, but in fact, not all of them could cause the bug.
-Sometimes happens that in the previous commit some lines had been copied from further previous commits, or comments may have been modified, or blank spaces/lines have been added.
+This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug.
+It may happen that in the previous commit lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
 Thus, the cause could be found in a single previous commit, in many or even in none.
-\grex{repasar este parrafo} \gema{Que tal ahora?
-esta mas claro?}
+\grex{Todavia no esta del todo claro...
+yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo.
+Ademas, nos lo podemos permitir; tenemos espacio.}
 
-We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis, we analyzed the bug reports together with their previous commits discarting these cases where the previous commit was false positives such as blank lines, changes in comments or even a change in the version of the file., so in total we had analyzed 308 previous commit.
+We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis.
+Then, we analyzed the bug reports together with their previous commits discarting the cases where the previous commit was a false positive (blank lines, changes in comments or even a change in the version of the file).
+So, in total we have analyzed 308 previous commit.
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commit, 152 of them have been considered the cause of the bug, whereas 114 were not the cause.
-We were unable to identify the cause of the bug in 42 cases, due to there was only added lines or our knowleadge about the code.
-
-As can be seen in Table~\ref{tab:responsability}, in 152 cases the previous commits have been considered the cause of the bug, whereas 114 times they were not the cause.
-We were unable to identify the cause of the bug in 42 cases, and discarded 40 more because they ere false positives such as blank lines, changes in comments or even a change in the version of the file.
-\grex{explicar que es eso de noise!} \gema{Con Noise me referia a los falsos positivos que puede haber en los commits previos, las lineas copiadas de otros commits o lineas en blanco, comentarios ...}
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
+We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code.
+\grex{Gema, puedes poner un ejemplo de estas dos cosas?
+Uno de solo added lines y otro de limited knowledge.
+Si el ejemplo es verdadero, mejor.}
+We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
 
@@
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
+\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}
+
+\grex{No me queda claro que quieres decir con mas de un identificador previo}
+
+\grex{Para los 58 bugs que tenian mas de un identificador previo hay 179 commits.
+Bien.
+Dices que 86 causaron el bug, 82 no y en 11 no se ha podido determinar.
+Lo que no veo es por que no agruampos estos datos segun los 58 bugs}
 
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
-\raisebox{1ex}{Cause}     & (65)50\% & (86)48\% \\[0ex]
-\raisebox{1ex}{Not cause} & (30)23\% & (82)46\% \\[0ex]
-\raisebox{1ex}{Undecided} & (36)27\% & (11)6\% \\[0ex]
+\raisebox{1ex}{Cause}     & (65) 50\% & (86) 48\% \\[0ex]
+\raisebox{1ex}{Not cause} & (30) 23\% & (82) 46\% \\[0ex]
+\raisebox{1ex}{Undecided} & (36) 27\% & (11) ~6\% \\[0ex]
 \bottomrule[0.3mm]
@@
 \end{table}
-\gema{Los resultados que he obtenido y que queria plasmar en las tablas son:}
-\gema{- He analizado 189 bugs reports}\\
-\gema{- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.}\\
-\gema{- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.}\\
-\gema{- Ademas he mirado como o porse distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
+
+%\gema{Los resultados que he obtenido y que queria plasmar en las tablas son:}
+%\gema{- He analizado 189 bugs reports}\\
+%\gema{- De los 189, 131 presentaban el mismo identificador de commit previo para todas las lineas que habian sido modificadas, mientras que 58 presentaban mas de un identificador de commit previo.}\\
+%\gema{- Dentro de los bugs reports que tienen mas de un commit previo analizando el total de todos los commits para saber quien causo el bug, he encontrado que en total de los 179 comit previos 86 causaron el bug mientarsa que 82 no lo causaron y 11 no he podido decidir si eran causantes o no.}\\
+%\gema{- Ademas he mirado como se distribuyen los commits en cada bug report dentro de cada proyecto analizado, y he visto que por ejemplo Neutron presentaba 11 bugs report con solo un ticket previo, 3 bugs report con dos identificadores diferentes para los commit previos, 2 bug reports que presentaban  3 commit previos...
 etc.}\\
-\gema{- Finalmente realice ora clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
+%\gema{- Finalmente realice otra clasificacion en la que tenia en cuenta el numero de commits que fueron causantes del error para un mismo bug report.
 Al analizar los bug reports encontre que en aquellos que presenstaban mas de un commit previo no todos los commit eran causantes del error, y en ocasiones solamente habia un commit que causo el error y los otros no o por el contrario habia bugs report en los que ninguno de sus commits previos era responsable y otras ocasiones en las que todos los commits previos eran responsables.
@@
 Por ejemplo, bugs reports que tenian dos commits previos, en 4 de ellos los dos commits previous eran responsables, mientras que en 9 bug report habia al menos un responsable y en otros 4 bug report ninguno de los dos commit previos eran responsables.}
-We also studied the distribution of the number of previous commits for each Bug Report.
+
+We also studied the distribution of the number of previous commits for each bug.
 As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits.
+\grex{the number of commits that can be considered as previous is 1, followed by 2 commits.
+No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo?
+Que utilidad tiene?}
 
@@
 
-Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them inserted the bug in the code source.
+Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them introduced the bug in the code source.
+Even if several previous commits are involved, it may be the case that none, only one or all of them is the cause of the bug.
+\grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}
 Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug.
+If we look at bugs that had two previous commits, in 4 cases both commits were the cause, in 9 cases only one of them was the cause and in another 4 cases non of them could be determined as the cause.
+
+\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}
 
@@
 
-\gema{Deberia hablar sobre los siguientes puntos:} \grex{Puedes elaborar un poco mas cada punto, aunque sea en castellano?}
-\begin{enumerate}
- \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se ha anadido codigo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo.
- \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han anadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la linea se olvido de realizar dichas comporbaciones, y en ese caso seria el causante del bug.
-Pero existen casos que la comprobacion que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error.
-Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provoco el error, porque realmente era dificil saberlo.
- \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
-\end{enumerate}
+The experience gained in this study with exposure to several hundreds of bugs allows us to state that determining who (or what) introduced a bug is a non-trivial task.
 
-\gema{Algunos de los problemas que nos hemos encontrado durante el analisis y que podrian ser resueltos de otra forma diferente a la nuestra y quizas puede que varie algo los resultados no lo se}
-Once we have all the tickets analyzed by diferents researchers who have used a double blind, how to proceed if there are discordances between them:
+Although at first, as shown in the Figure~\ref{fig:1} and Figure~\ref{fig:2}, one may think that this is an easy task, we have found many examples where we have been unable to determine the cause as no previous commit can be identified.
+This is, for instance, the case when only code has been added and there is no way to identify the previous commit.
+In this case, further research could find out if this is not really the addition of a new feature rather than a bug.
 
-\begin{enumerate}
-  \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
-  \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
-\end{enumerate}
-
-How to proceed if looking for the responsibility of a bug when only added lines are inserted?
 And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
@@
 \end{enumerate}
-\gema{anadir ademas que los resultados optenidos presentan una oposicion a la idea actual de que el previo commit introdujo el error}
+
+\gema{Puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
+
+There are other cases where it is difficult to determine if the change is the cause.
+For instance, when additional conditions are added to \emph{if}s or \emph{else}s, one might think that in the previous commit those were not included due to an error, so that the previous commit becomes the cause of the bug.
+However, situations exist where the additional conditions in an if appear because of the introduction of a new functionality, and thus the line in the previous commit was correct at the time it was introduced.
+In our analysis, if the latter situation is not explicity mentioned we have considered that the previous commit caused the error.
+
+But already the identification of an issue as a bug report is a process that is not as straightforward as one might think.
+Out of 459 tickets we were only capable to achieve a consensus for 292 cases (63.6\%), which hints to the complexity of the task.
+The amount of information, the number of fields and the requirement of human interaction made us invest time in the creation of a tool that assisted us in the process.
+
+%\begin{enumerate}
+% \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se ha anadido codigo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo.
+% \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han anadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la linea se olvido de realizar dichas comporbaciones, y en ese caso seria el causante del bug.
+Pero existen casos que la comprobacion que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error.
+Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provoco el error, porque realmente era dificil saberlo.
+% \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
+%\end{enumerate}
+
+%\gema{Algunos de los problemas que nos hemos encontrado durante el analisis y que podrian ser resueltos de otra forma diferente a la nuestra y quizas puede que varie algo los resultados no lo se}
+
+In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.
+\grex{Tengo que elaborar mas esto, que es el punto fuerte del articulo.}
 
@@
 \label{sec:threats}
+
+As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account.
+In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package including data sources, intermediate data and scripts that can be obtained at the following URL: \gema{Incluir la URL en la que pondre todos los datos y scripts utilizados para los datos.}
+
 %The limited sample size of tickets used in this research is the major threat to its validity.
@@
 This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
-The size of the tickets extracted form the Launchpad is medium, but doing the analysis manually we are sure that the results present in this paper are valid, being sure that the previous commits classified as not responsible, they are.
+The number of the tickets extracted form Launchpad is high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry.
+It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.
 
-Although, we understand that the model presented has some threats, external and internal, that make our model not 100\% valid.
 The internal threats related to the researchers that have conducted the study are following:
@@
 \begin{itemize}
-    \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we are lost some real bug reports belonging this group .
+  \item We have not considered those tickets where the two researchers showed discordance. 
+  \begin{enumerate}
+    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
+    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
+  \end{enumerate}
+    \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we have lost some \emph{actual} bug reports.
     \item There could be some lax criteria involving the subjective opinion of the researchers.
-    \item The researchers are not experts in OpenStack, and our inexperience may have influenced the results of the analysis.
-    \item We are only using part of the information that the ticket provides, like comments and text.
+    \item Although the researchers are experienced programmers, they are not experts in the  OpenStack project, and their inexperience may have influenced the results of the analysis.
+    \item We are only using part of the information that the tickets provide, like comments and text.
 There could be a recognized pattern in the data, unknown at first sight, that involves other parts of the information.
-    \item Although we use a random script to extract the tickets reported in during the last year, 2015, from the launchpad, in this year could be some bias unidentified.
-    \item In case of the researchers didn't find the information to know if the previous commit inserted the bug or in contrast, it was caused by the evolution of the software.
-They keep the traditionalist thought, classify these previous commits are responsible.
+    \item We have used a random script to extract the tickets from Launchpad that have been reported during 2015.
+There could be unintended bias of the data, because many reasons, as for instnace the phase of the project.
+    \item In some cases, researchers may have classified the previous commit as the cause of the bug, even if this may not be the case (see discussion on additional conditions in if statements).
 \end{itemize}
@@
     \item Some tickets are not explicitly described, which could increase the percentage of \textit{Undecided}. This is especially true if the reviewers are not from OpenStack.
-    \item OpenStack is a special project put down a constant evolution due to their active community of developers.
-Maybe, in other projects with less commits per year the statistics about the responsibility of previous commit change.
+    \item OpenStack is a special project with a constant evolution due to their active community of developers. Maybe, in other projects with less commits per year, results may be totally different.
 \end{itemize}
-
-\gema{Incluir un link con la web en la que pondre todos los datos y scripts utilizados para los datos.}
 
@@
 
-The empirical experiment carried out in OpenStack, supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not responsible inserting the bug.
+The empirical experiment carried out in OpenStack supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not the cause of the bug.
+
 With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
@@
 
-A final field in our future work concerns the full automation on the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
-Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.
+A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
+Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa?
+En castellano si quieres}
 

### 2016-01-31 paperMSR.tex
Parrafo de la contribucion del articulo

@@
 
-With this paper we try to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
-Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software.
-Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process.
-\grex{reescribir este parrafo para que quede mas claro.}
+The main contribution of this paper is to shed some light on the correctness of the asumption that a bug is caused in the previous commit.
+In the point of time where the previous commit was performed, the lines that are modified in the bug-fix were correct.
+We show that a significant portion of bugs can be attributed to other causes, offering evidence that all the research findings and methods that have been constructed based on this assumption are not using accurate data and may give inaccurate results.
+Finally, our study can be understood as a step forward to better understand the bug seeding process.
 
@@
 
-\gema{Puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
+\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
 
@@
 In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.
-\grex{Tengo que elaborar mas esto, que es el punto fuerte del articulo.}
+\grex{Tengo que elaborar mas esto, que es el punto mas fuerte (o de mayor) del articulo.}
 

### 2016-01-31 paperMSR.tex
some changes

--- 2016-01-30 paperMSR.tex
@@
 Our results show that the assumption that bugs have been introduced in the previous commit does not hold for a large fraction of the bugs analyzed.
-\grex{maybe we could say something more here}.
+Concretlly, a 37\% of the previous commits analyzed are opposite to the current assumption and they didn't cause the bug.\grex{maybe we could say something more here}.
 \gema{podriamos escribir algunos porcentajes de lo que hemos encontrado, algo asi como que un 37\% de los commits previos no son responsables de introducir niingun bug}
@@
 But in fact, to find when and where a bug was introduced in the source code is not a trivial task.
-This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
+This has largely been ignored, mainly because the data related to the origin of a bug is embedded in the evolution of the software, meaning that when someone fixes a bug they don't take into consideration the context and the history behind of the project~\cite{sinha2010buginnings}.
 \grex{clarificar la frase anterior...
-no ha quedado muy claro.}
+no ha quedado muy claro.}\gema{mejor ahora?}
 
@@
 \grex{poner el siguiente parrafo bien}
-
-The goal of this paper is to find if the cause of the bug can be \grex{assigned} to the previous commit, understanding that at the time when the previous commit is introduced
-
-not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
+\gema{podemos eliminar el siguiente parrafo porque en realidad lo que qería decir aquí es la contribucion del paper y si la pongo luego puedo eliminar este parrafo}
+The goal of this paper is to find if the cause of the bug can be assigned to the previous commit, understanding that at the time when the previous commit is introduced not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
 So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
@@
     %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-     \item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
-     \item \gema{RQ1: How we can identify a change done to fix a bug inserted in the code source?
-Que tal esta forma de plantear la RQ1?
+     %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+     \item RQ1: How we can identify a change done to fix a bug inserted in the code source?
+\gema{Que tal esta forma de plantear la RQ1?
 Esta pregunta se refiere a como podemos diferenciar los bug reports de los otros pero realizada desde el punto de vista del comit previo }
@@
 \grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
-With this paper we try to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
-Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software.
-Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process.
+The goal of this paper is to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy.
+Finally, our results could lead to think that all the articles based on this assumption are not using the best data in their approach and as a result they can improve their results with our idea.
+On the other hand, this could be very useful in future researchs, could help developers understanding the bug seeding process.
 
@@
 present another technique to identify the origins of a bug in~\cite{sinha2010buginnings}.
-Their technique is not text-based technique, as the SZZ algorithm, as the authors analyze the effects of bug-fix changes on program dependencies.
+Their technique is not text-based technique, as the SZZ algorithm, the authors analyze the effects of bug-fix changes on program dependencies.
 So, taking into account the semantics of the source code they achieved higher accuracy in identifying the origins of a bug.
@@
 
-The SZZ algorithm (and its \emph{successors}) have been widely used in the researc community.
+The SZZ algorithm (and its \emph{successors}) have been widely used in the research community.
 Williams et al.
@@
 There the talk is precisely about those bugs whose origina are elsewhere.
-Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}
+Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}
 
@@
 From the experience of analysing a small number of tickets, we agreed on following four criteria: 
-
 \begin{enumerate}
-    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
-    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
-    \item When the ticket title described that updates were required, the ticket is a bug report.
+    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considerated as a bug report. 
+    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure.
+    \item When the ticket described that some updates were required, the ticket is a bug report.
 We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
@@
 When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails.
-\grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}
+\grex{no se repiten las frases?}\gema{He cambiado el inico de las frases para que no sea tan repetitivo}
 \end{enumerate}
@@
 \end{table}
+
+After this, we can answer the first research question because at this moment we have all the data necessary and all the knowleadge to can distinguish bug reports from others reports.
 

### 2016-01-31 paperMSR.tex

--- 2016-01-31 paperMSR.tex
@@
 But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption.
-This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}.
+This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}, meaning that when someone fixes a bug they don't take into consideration the context and the history behind of the project and you cannot have access into this information easily.
 \grex{Gema, puedes clarificar la frase anterior?
-No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}
+No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}\gema{No se si asi queda mas claro, la idea de embebed la saque del articulo y por lo que entendi con embebed se referia a que no hay ningun log o nada donde los desarrolladores expliquen porque se ha producido un error desde un punto de vista mas historico, que la informacion sobre el error se encuentra embebida en la historia y la evolucion del propio proyecto, no creo que pueda sacar ningun ejemplo }
 
@@
 
-The goal of this paper is to find if the cause of the bug can be attributed to the previous commit.
-A previous commit will be identified as the cause if the buggy behavior is present at the time it is performed.
-If the buggy behavior is due to other changes in the software, e.g., due to its evolution or changes elsewhere in the source code base, the previous commit should not be considered as the cause of a bug.
+\grex{poner el siguiente parrafo bien}
+\gema{podemos eliminar el siguiente parrafo porque en realidad lo que qería decir aquí es la contribucion del paper y si la pongo luego puedo eliminar este parrafo}
+The goal of this paper is to find if the cause of the bug can be assigned to the previous commit, understanding that at the time when the previous commit is introduced not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
+So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
 
-To achieve our goal, this paper attempts to address the following research questions:
+In detail, in this paper we attempt to address the following research question regarding who introduced the bug in the source code:
 
+\grex{rephrase RQs}
 \begin{itemize}
@@
     %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
-     \item \gema{RQ1: How we can identify a change done to fix a bug inserted in the code source?
-Que tal esta forma de plantear la RQ1?
-Esta pregunta se refiere a como podemos diferenciar los bug reports de los otros pero realizada desde el punto de vista del comit previo }
      \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
+     \item \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
+}
     %\item RQ2:  How often is the bug caused in the previous commit?
@@
 
-With this paper we try to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
-Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software.
-Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process.
-\grex{reescribir este parrafo para que quede mas claro.}
+\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
+The goal of this paper is to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy.
+Finally, our results could lead to think that all the articles based on this assumption are not using the best data in their approach and as a result they can improve their results with our idea.
+On the other hand, this could be very useful in future researchs, could help developers understanding the bug seeding process.
 
@@
 2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.
+
+The SZZ algorithm (and its \emph{successors}) have been widely used in the research community.
+Williams et al.
+revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
+Yang et al.
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes
+Finally, some bug prediction algorithms are based on SZZ; Kim et al.
+showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.
+
+\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
+There the talk is precisely about those bugs whose origina are elsewhere.
+Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}
 
@@
 From the experience of analysing a small number of tickets, we agreed on following four criteria: 
+\begin{enumerate}
 
-\begin{enumerate}
-    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
-    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
-    \item When the ticket title described that updates were required, the ticket is a bug report.
+    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considerated as a bug report. 
+    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure.
+    \item When the ticket described that some updates were required, the ticket is a bug report.
 We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected.
@@
 We consider bug errors in test files are a different type of bugs, as the software may still work as expected.
-\grex{no se si esto es lo que querias decir}
+\grex{no se si esto es lo que querias decir}\gema{si, es eso lo que queria decir}
 
@@
 \grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}
+
 \end{enumerate}
@@
 
-The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project.
-
-\grex{Este parrafo deberia decir lo mismo que el anterior. Si es asi, borremos el anterior}
 In this second part, our work was focused on analyzing the previous commit exclusively for those tickets classified in the \textit{Bug Report} group.
@@
 
-For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit.
-This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
+For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit, we refered to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
+We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
 \grex{Gema, puedes aclarar este parrafo?
@@
 Es la primera vez que hablamos de el.
-Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}
+Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se shan cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del pervio para saber que en realidad en ese momento se produjo el cambio.
+En el gerrit nos dan esa info como se puede ver en \ref{fig:parent}}
+\begin{figure}[ht]
+\centering
+\includegraphics[height=2cm]{parent.png}
+\label{fig:patent}       % Give a unique label
+\end{figure}
 
@@
 
-We classify a total of 459 tickets using the tool, resulting in 918 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}.
-Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
+We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}.\gema{Es cierto, son 917} Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
 
@@
 %\grex{Tiene sentido añadir porcentajes, como he hecho a la columna de Total?}
+%26-56 hours
 
@@
 
+After this, we can answer the first research question because at this moment we have all the data necessary and all the knowleadge to can distinguish bug reports from others reports.
+
 \grex{Tiene sentido anadir numeros absolutos, como he hecho a la columna de Total en la Tabla 3?}
+\gema{Si, tiene sentido}
 
@@
 \grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}
+\gema{El problema es que no hemos medido el tiempo, he hablado con ellos y me dicen que de media de 5 a 10 minutos por ticket, a mi me llevo unos 5 minutos de media, por que ya estaba mas acostumbrada, pero de todas formas se podría medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?}
 
@@
 
-In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} as bug reports and their previous commits.
+In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} as bug reports and their previous commits.
 The possible outcome of the analysis was one of the following three options:
@@
 This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug.
-It may happen that in the previous commit lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
+It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
 Thus, the cause could be found in a single previous commit, in many or even in none.
@@
 yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo.
-Ademas, nos lo podemos permitir; tenemos espacio.}
+Ademas, nos lo podemos permitir; tenemos espacio.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[height=12cm]{manylines.png}
+%\caption{Screenshot of the tool used to classify the tickets.}
+%\label{fig:screenshot}       % Give a unique label
+%\end{figure}
 
@@
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}
+Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
-\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}
+\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
 
-\grex{No me queda claro que quieres decir con mas de un identificador previo}
+\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}
 
@@
 Dices que 86 causaron el bug, 82 no y en 11 no se ha podido determinar.
-Lo que no veo es por que no agruampos estos datos segun los 58 bugs}
+Lo que no veo es por que no agruampos estos datos segun los 58 bugs}\gema{Esos datos estan agrupados en la tabla 7, el fin de esta tabla era mostrar que cuando hay un solo comit previo el numero de no causantes del error es menor que cuando hay mas de un commit previo}
 
@@
 No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo?
-Que utilidad tiene?}
+Que utilidad tiene?}\gema{Creo que era interesante saber como se distribuyen los causantes de los bugs en cada projecto y cuantos commits previos presentan los bugs report en cada projecto analizado, ademas cuantos mas commits previos, en ocasiones, es muy dificil saber quien es el responsable por tanto pense que podria haber algun patron en relacion con el numero de commits previos y cuantos de ellos son responsables, pero parece que esto no ocurre con la muestra que hemos analizado.}
 
@@
 Even if several previous commits are involved, it may be the case that none, only one or all of them is the cause of the bug.
-\grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}
+\grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}\gema{si, eso sucede y eso casos se encuentran dentro de al menos un responsable, (at least one responsible)}
 Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug.
@@
 
-\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}
+\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para tener una idea de como se distribuyen los causantes del error, podría eliminar las tablas si en realidad no las encuentras funcionales y no aportan informacion.
+}
 
@@
 En castellano si quieres}
+\gema{Si, la idea es realizar el mismo estudio pero con otro projecto que no sea OpenStack, porque en realidad OpenStack esta evolucionando continuamente.
+Y para poder demostrar que en realidad la idea se cumple en todos los projectos, deberiamos analizar un projecto que sea mas 'estable' y en el que la API no se este cambiando continuamente }
 

### 2016-01-31 paperMSR.tex
Some comments more

@@
 
-\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para tener una idea de como se distribuyen los causantes del error, podría eliminar las tablas si en realidad no las encuentras funcionales y no aportan informacion.
-}
+\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para entender como de complejo es el problema, porque no es lo mismo que dos commits anteriores sean responsables a que lo sean 5, entendiendo que si son cambios independientes es muy raro que sean causantes de un mismo error.
+y para saber si algun patron se repite y nos ayuda a entender algo, pero las tablas no llegan a ser muy concluyentes y los numeros son bajos, podemos introducirlo como un poco de discusion sobre que podria ser interesante analizar mas y ver si con mas poblacion se repite algun patron y decir exactamente cuantos comits son los responsables en un bug report.}
 

### 2016-01-31 paperMSR.tex
cambiando los goals

--- 2016-01-31 paperMSR.tex
@@
 But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption.
-This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}, meaning that when someone fixes a bug they don't take into consideration the context and the history behind of the project and you cannot have access into this information easily.
-\grex{Gema, puedes clarificar la frase anterior?
-No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}\gema{No se si asi queda mas claro, la idea de embebed la saque del articulo y por lo que entendi con embebed se referia a que no hay ningun log o nada donde los desarrolladores expliquen porque se ha producido un error desde un punto de vista mas historico, que la informacion sobre el error se encuentra embebida en la historia y la evolucion del propio proyecto, no creo que pueda sacar ningun ejemplo }
+This has been largely ignored in much of the bug-fix literature, mainly because the data related to the origin of a bug is \emph{embedded} in the evolution of the software~\cite{sinha2010buginnings}, as the authors state.
+With this they mean that there is no easy evidence (artifact, comment or log) where developers specify what produced that error from a more historical point of view; the explanation of the cause is thus \emph{embedded} in the project.
 
@@
 
-\grex{rephrase RQs}
+%\grex{rephrase RQs}
 \begin{itemize}
-    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
-     \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
-     \item \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
+% \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
 }
@@
      \item RQ2: How often is the previous commit the cause of the bug?
-\end{itemize}
 
-Answering RQ1 is a prerequisite to be able to answer RQ2.
+     As already explained, this is the main question that we want to answer in this paper.
+Given bugs that have been fixed, how many of those were introduced by the previous commit.
+To do so, we first have to answer RQ1.
+
+    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
+    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+     \item RQ1: How can we identify changes done to fix a bug?
+
+     To be able to answer RQ2, we first need to study the issue-tracking system and identify there the subset of tickets that correspond to already fixed bugs.
+In essence, RQ1 could be also stated as \emph{How many tickets in the issue tracking system are (real) bug reports?}.
 This is because (real) bugs are managed together in an issue-tracking tool with feature requests, optimizations, test files, among others.
@@
 
-\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
-The goal of this paper is to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+\end{itemize}
+
+The goal of this paper is to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
 Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy.

### 2016-01-31 paperMSR.tex
sigo tocando comentarios

@@
 \grex{poner el siguiente parrafo bien}
-\gema{podemos eliminar el siguiente parrafo porque en realidad lo que qería decir aquí es la contribucion del paper y si la pongo luego puedo eliminar este parrafo}
+\gema{podemos eliminar el siguiente parrafo porque en realidad lo que queria decir aqui es la contribucion del paper y si la pongo luego puedo eliminar este parrafo} \grex{Queda entonces mirar a ver cual de los dos parrafos es mejor o si hacer un merge}
 The goal of this paper is to find if the cause of the bug can be assigned to the previous commit, understanding that at the time when the previous commit is introduced not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
@@
 
-\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
+%\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
 There the talk is precisely about those bugs whose origina are elsewhere.
@@
 In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base.
+\grex{Quizas mirar si hay mas articulos en esta linea.
+No es muy importante esto.}
 
@@
 We consider bug errors in test files are a different type of bugs, as the software may still work as expected.
-\grex{no se si esto es lo que querias decir}\gema{si, es eso lo que queria decir}
 
@@
 
-For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit, we refered to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
-We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug.
+For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
+We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
+We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
 \grex{Gema, puedes aclarar este parrafo?
@@
 Es la primera vez que hablamos de el.
-Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se shan cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del pervio para saber que en realidad en ese momento se produjo el cambio.
-En el gerrit nos dan esa info como se puede ver en \ref{fig:parent}}
+Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio.
+En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}
+
 \begin{figure}[ht]
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:patent}       % Give a unique label
+\label{fig:parent}       % Give a unique label
+\caption{Information in Gerrit.\grex{contar que se ve en la figura}}
 \end{figure}
@@
 
-We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}.\gema{Es cierto, son 917} Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
+We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!} \gema{Es cierto, son 917}.
+Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
 
@@
 
-\grex{Tiene sentido anadir numeros absolutos, como he hecho a la columna de Total en la Tabla 3?}
-\gema{Si, tiene sentido}
-
 \vspace{0.2cm}
@@
 \grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}
-\gema{El problema es que no hemos medido el tiempo, he hablado con ellos y me dicen que de media de 5 a 10 minutos por ticket, a mi me llevo unos 5 minutos de media, por que ya estaba mas acostumbrada, pero de todas formas se podría medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?}
+\gema{El problema es que no hemos medido el tiempo, he hablado con ellos y me dicen que de media de 5 a 10 minutos por ticket, a mi me llevo unos 5 minutos de media, por que ya estaba mas acostumbrada, pero de todas formas se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?}
 

### 2016-01-31 paperMSR.tex
sigo tocando comentarios

@@
 
+\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}
+
 \begin{figure}[ht]
@@
 Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
+This process requires manual inspection by researchers.
+In the mean classifying a ticket takes \gema{between 5 and 10 minutes per ticket}, although the amount of time decreases with experience as could be expected.
+
+\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}
 
@@
 
-\grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}
-\gema{El problema es que no hemos medido el tiempo, he hablado con ellos y me dicen que de media de 5 a 10 minutos por ticket, a mi me llevo unos 5 minutos de media, por que ya estaba mas acostumbrada, pero de todas formas se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?}
-
 \subsection{Second Stage}
@@
 
-In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} as bug reports and their previous commits.
+In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} \grex{no se si hace falta, a ver que dice jesus} as bug reports and their previous commits.
 The possible outcome of the analysis was one of the following three options:
@@
 \end{tabular} }
-\caption{ Distribution of number of previous commit per Bug Report in each project}
+\caption{ Distribution of the number of previous commits per bug report for each project.}
 \label{tab:secondStage2}
@@
 Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them introduced the bug in the code source.
-Even if several previous commits are involved, it may be the case that none, only one or all of them is the cause of the bug.
-\grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}\gema{si, eso sucede y eso casos se encuentran dentro de al menos un responsable, (at least one responsible)}
+Even if several previous commits are involved, it may be the case that none, at least one of them or all of them is the cause of the bug.
+
 Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug.
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
-\raisebox{1ex}{All Responsible}          & 4 & 3 & 0 & 1 & 8\\[0ex]
-\raisebox{1ex}{At least one responsible} & 9 & 7 & 5 & 9 & 30\\[0ex]
-\raisebox{1ex}{None Responsible}         & 4 & 2 & 4 & 1 & 11\\[0ex]
+\raisebox{1ex}{All are the cuase}          & 4 & 3 & 0 & 1 & 8\\[0ex]
+\raisebox{1ex}{At least one is the cause} & 9 & 7 & 5 & 9 & 30\\[0ex]
+\raisebox{1ex}{None is the cause}         & 4 & 2 & 4 & 1 & 11\\[0ex]
 \raisebox{1ex}{Undecided}                & 1 & 0 & 1 & 0 & 2\\[0ex]
@@
 \end{tabular} }
-\caption{ Number of previous commit responsibles per bug report}
+\caption{Number of previous commits identified as the cause of a bug per bug report}
 \label{tab:secondStage3}
@@
 
-\gema{Puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
+\grex{Gema, puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
 

### 2016-01-31 paperMSR.tex
Some comments more

--- 2016-01-31 paperMSR.tex
@@
 But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption.
-This has been largely ignored in much of the bug-fix literature, mainly because the data related to the origin of a bug is \emph{embedded} in the evolution of the software~\cite{sinha2010buginnings}, as the authors state.
-With this they mean that there is no easy evidence (artifact, comment or log) where developers specify what produced that error from a more historical point of view; the explanation of the cause is thus \emph{embedded} in the project.
+This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}, meaning that when someone fixes a bug they don't take into consideration the context and the history behind of the project and you cannot have access into this information easily.
+\grex{Gema, puedes clarificar la frase anterior?
+No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}\gema{No se si asi queda mas claro, la idea de embebed la saque del articulo y por lo que entendi con embebed se referia a que no hay ningun log o nada donde los desarrolladores expliquen porque se ha producido un error desde un punto de vista mas historico, que la informacion sobre el error se encuentra embebida en la historia y la evolucion del propio proyecto, no creo que pueda sacar ningun ejemplo }
 
@@
 
-%\grex{rephrase RQs}
+\grex{rephrase RQs}
 \begin{itemize}
-% \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
+    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
+    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
+     \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
+     \item \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
 }
@@
      \item RQ2: How often is the previous commit the cause of the bug?
+\end{itemize}
 
-     As already explained, this is the main question that we want to answer in this paper.
-Given bugs that have been fixed, how many of those were introduced by the previous commit.
-To do so, we first have to answer RQ1.
-
-    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
-    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
-     \item RQ1: How can we identify changes done to fix a bug?
-
-     To be able to answer RQ2, we first need to study the issue-tracking system and identify there the subset of tickets that correspond to already fixed bugs.
-In essence, RQ1 could be also stated as \emph{How many tickets in the issue tracking system are (real) bug reports?}.
+Answering RQ1 is a prerequisite to be able to answer RQ2.
 This is because (real) bugs are managed together in an issue-tracking tool with feature requests, optimizations, test files, among others.
@@
 
-\end{itemize}
-
-The goal of this paper is to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
+\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
+The goal of this paper is to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
 Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy.
@@
 Thus, the cause could be found in a single previous commit, in many or even in none.
+In the \ref{fig:previous} we see that the previous commits are more than one, in this case two \textit{e7be0a988} and \textit{e5296c1da}.
+The previous commit \textit{e7be0a988} didn't cause the bug because it's a line to know the version of the file.
+The previous commit \textit{e5296c1da} caused the bug because it inserted a incorrect \textit{break} line.
 \grex{Todavia no esta del todo claro...
@@
 
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[height=12cm]{manylines.png}
-%\caption{Screenshot of the tool used to classify the tickets.}
-%\label{fig:screenshot}       % Give a unique label
-%\end{figure}
+\begin{figure}[ht]
+\centering
+\includegraphics[height=2.5cm]{manyprevious.png}
+\caption{Previous commits: \textit{e7be0a988}, \textit{e5296c1da} }
+\label{fig:previous}       % Give a unique label
+\end{figure}
 
@@
 
-\gema{Puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
+\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
+\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.
+Otro caso puede ser lo if/else, en estos casos hay que ser cuidadosos y saber diferenciar si el causante fue el comit previo porque se olvido de comporbar una condicion, o si el commit previo no fue el causante del error porque la condicion que se introduce en el commit que arregla el error se debe a que han anadido una nueva funcionalidad despues de haber anadido el if/else y necesitan comprobarla ahora, por tanto seria debido a la evolucion del projecto.
+En este ultimo caso, si no tenemos toda la descripcion de lo que realmente esta pasando, para poder decidir en que situacion estamos, hemos sido conservadores y hemos inducado que el commit anterior fue el responsable}
 

### 2016-01-31 paperMSR.tex

--- 2016-01-31 paperMSR.tex
@@
 
-\grex{Gema, puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}
+\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
+\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.
+Otro caso puede ser lo if/else, en estos casos hay que ser cuidadosos y saber diferenciar si el causante fue el comit previo porque se olvido de comporbar una condicion, o si el commit previo no fue el causante del error porque la condicion que se introduce en el commit que arregla el error se debe a que han anadido una nueva funcionalidad despues de haber anadido el if/else y necesitan comprobarla ahora, por tanto seria debido a la evolucion del projecto.
+En este ultimo caso, si no tenemos toda la descripcion de lo que realmente esta pasando, para poder decidir en que situacion estamos, hemos sido conservadores y hemos inducado que el commit anterior fue el responsable}
 

### 2016-01-31 paperMSR.tex
trabajando en los comentarios

--- 2016-01-31 paperMSR.tex
@@
 In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.
-\grex{Tengo que elaborar mas esto, que es el punto fuerte del articulo.}
+\grex{Tengo que elaborar mas esto, que es el punto mas impactante del articulo.}
 
@@
 
-A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
-Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa?
-En castellano si quieres}
-\gema{Si, la idea es realizar el mismo estudio pero con otro projecto que no sea OpenStack, porque en realidad OpenStack esta evolucionando continuamente.
-Y para poder demostrar que en realidad la idea se cumple en todos los projectos, deberiamos analizar un projecto que sea mas 'estable' y en el que la API no se este cambiando continuamente }
+A final field of future work could be concerned with the full automation of the methodology, developing  an automatic classifier based on the idea that not all the previous commits inject the bug.
+\grex{mejorar este parrafo.}
+
+Another interesting investigation could perform the same empirical study on a project with a less active community, to prove if our idea is fulfill in other projects.
+So, for projects that do not evolve as rapidly as OpenStack, e.g., those with a more stable API, could offer completely different results even if applying the same analysis methodology used in this paper.
 

### 2016-01-31 paperMSR.tex
some changes

--- 2016-01-31 paperMSR.tex
@@
 But although the assumption can be found frequently in the research literature, in our opinion there is not empirical evidence supporting it.
-That is the reason why we have conducted an observational study on fix-bugs, devoting a significant effort to locate the origin of a bug in the source code and understanding the possible causes.
+That is the reason why we have conducted an observational study on bug-fixs, devoting a significant effort to locate the origin of a bug in the source code and understanding the possible causes.
 For this we had to take into account the moment in which the line was inserted and the general context of the project.
@@
 \grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
+\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
+Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
 
@@
 \label{fig:parent}       % Give a unique label
-\caption{Information in Gerrit.\grex{contar que se ve en la figura}}
+\caption{Information about the bug }
 \end{figure}
@@
 \fbox{\begin{minipage}{25em}
-\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a fix-bug, we have obtained that in at least 72\% of the tickets analyzed the fix-bugs were real bug reports.}
+\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a bug-fix, we have obtained that in at least 72\% of the tickets analyzed the bug-fixs were real bug reports.}
 \end{minipage}}

### 2016-02-01 paperMSR.tex
Tocando lo del parent commit

@@
 For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
-We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
-\grex{Gema, puedes aclarar este parrafo?
+We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit.
+It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
+Figure~\ref{fig:parent} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.
+
+We do this process to be sure that we are looking the correct change, because sometimes although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
+
+%\grex{Gema, puedes aclarar este parrafo?
 Que es el "parent" commit?
@@
 Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio.
-En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}
+En el gerrit nos dan esa info como se puede ver en la figura}
 
-\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
-\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
+%\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
+%\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
 Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
@@
 \label{fig:parent}       % Give a unique label
-\caption{Information about the bug }
+\caption{Information about the bug offered by Gerrit.}
 \end{figure}
@@
   \item We have not considered those tickets where the two researchers showed discordance. 
-  \begin{enumerate}
-    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
-    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
-  \end{enumerate}
+%  \begin{enumerate}
+%    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
+%    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
+%  \end{enumerate}
     \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we have lost some \emph{actual} bug reports.
@@
 
-With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
+With our methodology we have identifie which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
 Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.

### 2016-02-01 paperMSR.tex
some changes

--- 2016-01-31 paperMSR.tex
@@
 
-For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
+For that, we had to analyze the lines involved in the bug fix commit and in its \emph{parent} commit, being sure that the lines were added, inserted or modified in the previous commit.
+We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file before the bug fix and could be different from the commit previous.
 We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
@@
 Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
-
+The information about the bug fix commit is shown in the figure \ref{fig:6}, this information has been extracted from the gerrit of the figure \ref{fig:1} and we can apreciate that the previous commit in the example \ref{fig:1}(\textit{31f08423}) is different from the parent commit displayed in the figure \ref{fig:6},(\textit{db7fc59ebc}).
 \begin{figure}[ht]
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:parent}       % Give a unique label
-\caption{Information about the bug }
+\label{fig:6}       % Give a unique label
+\caption{Information about the bug fix commit displayed in gerrit. }
 \end{figure}

### 2016-02-01 paperMSR.tex
Tocando el comentario relacionado con el number of commits per previous commit

--- 2016-02-01 paperMSR.tex
@@
 It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
-Figure~\ref{fig:parent} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.
+Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.
 
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:parent}       % Give a unique label
 \caption{Information about the bug offered by Gerrit.}
+\label{fig:parentgerrit}       % Give a unique label
 \end{figure}
@@
 We also studied the distribution of the number of previous commits for each bug.
-As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits.
+This result will provide further insight into the bug-seeding nature; it offers as well an idea of the complexity of identifying the cause of a bug, as the more commits involved, the harder it is to identify the cause and understand it.
+As shown in Table~\ref{tab:secondStage2}, usually the number of commits that can be considered as previous is 1 (over 69\% of the cases), followed by 2 commits (13\%).
+In around 10\% of the cases, 3 or more commits are involved.
+
+% the number of commits that can be considered as previous is 1, followed by 2 commits.
 \grex{the number of commits that can be considered as previous is 1, followed by 2 commits.
@@
 \end{tabular} }
-\caption{ Distribution of the number of previous commits per bug report for each project.}
+\caption{ Distribution of the number of commits that can be considered as the previous commit per bug report for each project.}
 \label{tab:secondStage2}
@@
 As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account.
-In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package including data sources, intermediate data and scripts that can be obtained at the following URL: \gema{Incluir la URL en la que pondre todos los datos y scripts utilizados para los datos.}
+In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}} including data sources, intermediate data and scripts that can be obtained.
 

### 2016-02-01 paperMSR.tex

@@
 It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
-Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.
+Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found, that corresponds to the bug-fix shown in~\ref{fig:1}.
+As can be seen, the previous commit (\textit{31f08423}) in Figure~\ref{fig:1} is different from the parent commit displayed in Figure~\ref{fig:parentgerrit} (\textit{db7fc59ebc}).
 
@@
 \includegraphics[height=2cm]{parent.png}
-\caption{Information about the bug offered by Gerrit.}
+\caption{Information about the bug as displayed by Gerrit.}
 \label{fig:parentgerrit}       % Give a unique label

### 2016-02-01 paperMSR.tex
Abstract and intro done.

--- 2016-02-01 paperMSR.tex
@@
 
-\newif\ifdraft
-\drafttrue
+%\newif\ifdraft
+%\drafttrue
 %\draftfalse
@@
 \alignauthor
-Jes\'us M. Gonz\'alez-Barahona\\
+Jesus M. Gonzalez-Barahona\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
@@
 In fact, many studies on bug seeding start with this assumption.
-However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug may have been introduced by other actions, such as an older modification, or a change in the API that is being called.
+However, there is little empirical evidence supporting it, and there are reasons to suppose that in some cases the bug may have been introduced by other actions, such as an older modification, or a change in the API that is being called.
 
-This paper tries to shed some light on this topic, by analyzing the relationship of bug fixes with their previous commits.
+This paper tries to shed some light on this topic by analyzing the relationship of bug fixes with their previous commits.
 To this end, we conducted an observational study on bug reports, their fixes, and their corresponding previous commits for the OpenStack project.
@@
 
-When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code.
-It may semm at first reasonable to assume that previous modifications of this line or these lines are the cause of the bug; the previous modification is what is called \textit{the previous commit}.
+When a failure is found in some software, developers try to fix it by locating and modifying the source code line(s) that are reponsible for the wrong behaviour.
+It may semm at first reasonable to assume that previous modifications of this line or lines are the cause of the bug.
+That previous modification is what will refer through this paper as the \textit{previous commit}.
+
 But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption.
 This has been largely ignored in much of the bug-fix literature, mainly because the data related to the origin of a bug is \emph{embedded} in the evolution of the software~\cite{sinha2010buginnings}, as the authors state.
-With this they mean that there is no easy evidence (artifact, comment or log) where developers specify what produced that error from a more historical point of view; the explanation of the cause is thus \emph{embedded} in the project.
+With this they mean that there is no easy evidence (artifact, comment or log) where developers specify what produced that error from a more historical point of view.
+The explanation of the cause is thus \emph{embedded} in the project.
 
 This is the reason why many studies in the area of mining software repositories start with this implicit assumption.
-So, for instance, we have found following reasonings in several areas of research, such as:
+As an anectodal evidence, we have found the following rationales in several areas of research:
 
 \begin{itemize}
-  \item in bug seeding studies, e.g., \textit{``This earlier change is the one that caused the later fixed''}~\cite{williams2008szz} or \textit{``The lines affected in the process of fixing a bug are the same one that originated or seeded that bug''}~\cite{izquierdo2011developers},
-  \item in bug fix patterns, e.g., \textit{``The version before the bug fix revision is the bug version''}~\cite{pan2009toward},
-  \item and in tools that prevent for future bugs, e.g., \textit{``We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit''}~\cite{fejzer2015supporting}.
+  \item bug seeding studies, e.g., \textit{``This earlier change is the one that caused the later fixed''}~\cite{williams2008szz} or \textit{``The lines affected in the process of fixing a bug are the same one that originated or seeded that bug''}~\cite{izquierdo2011developers},
+  \item bug fix patterns, e.g., \textit{``The version before the bug fix revision is the bug version''}~\cite{pan2009toward},
+  \item tools that prevent future bugs, e.g., \textit{``We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit''}~\cite{fejzer2015supporting}. 
 \end{itemize}
 
-But although the assumption can be found frequently in the research literature, in our opinion there is not empirical evidence supporting it.
-That is the reason why we have conducted an observational study on bug-fixs, devoting a significant effort to locate the origin of a bug in the source code and understanding the possible causes.
-For this we had to take into account the moment in which the line was inserted and the general context of the project.
+But although the assumption can be found frequently in the research literature, in our opinion there is not enough empirical evidence supporting it.
+That is the reason why we have conducted an observational study on bug fixing, devoting a significant effort to locate the origin of a bug in the source code and understanding the possible causes.
+For this we took into account when the line was inserted and the general context of the project at that point.
 
@@
   \item The code in the middle (subfigure \textit{(2)}) shows the moment in which the bug was introduced (being \textit{31f08423} the id of change), the previous commit.
-  \item The code on the right (subfigure \textit{(3)}) ensures that in previous versions of the file, the bug did not exist.
+  \item The code on the right (subfigure \textit{(3)}) shows how in previous versions of the file, the bug did not exist.
 \end{enumerate}
@@
 
-According to the description in the log of the commit that fixed the bug (see Figure~\ref{fig:2}), commit \textit{31f08423} was the one where the bug was introduced, as it used a variable as string when a Boolean had to be used, keeping the concordance with the rest of the code.
+According to the description in the log of the commit that fixed the bug (see Figure~\ref{fig:2}), commit \textit{31f08423} was the one where the bug was introduced, as it used a string variable, while a Boolean had to be used, keeping the concordance with the rest of the code.
 So, in this case, the bug was introduce in the previous commit.
 
-On the other hand, Figure~\ref{fig:3} shows a clear example of a case where the cause of the bug is not to be attributed to the previous commit.
-In this example, the bug fix commit log (see Figure~\ref{fig:4}) describes that the name of an argument changed when updating the version causing the failure in the software.
+On the other hand, Figure~\ref{fig:3} shows a clear example of a case where the cause of the bug cannot be attributed to the previous commit.
+In this example, the bug fixing commit log (see Figure~\ref{fig:4}) describes that the name of an argument changed when updating the version causing the failure in the software.
 This change was done because of the new requirements in the software version, and is unrelated to the changes performed in the previous commit.
-When the modified lines where introduced in the first time, they did not contain the bug.
+When the modified lines where introduced the first time, they where not buggy.
 
@@
 
-Based on anecdotal evidence like the one presented in Figures~\ref{fig:3} and Figure~\ref{fig:4}, we argue that in projects that are continuously evolving, with an ample developer community, code that before was correct could be buggy at some time.
-So, changes in other parts
-of the code may induce wrong behavior (bugs) in places that were correct in the past.
-This happens often in situations like changes to the API.
-In the moment the code ws written, it was correct and the woftware worked fine.
-Additions of new features or enhancements to the API had as a side effect that the formerly correct code presents a wrong behavior, making the software fail.
-But in such cases, the source of the error cannot be attributed to a change performed in the previous commit, as in that moment it referred to a different API.
+Based on anecdotal evidence like the one presented in Figures~\ref{fig:3} and Figure~\ref{fig:4}, we argue that in projects that are continuously evolving, with a large development community, code that at some point was correct could become buggy later.
+Changes in other parts
+of the code may trigger wrong behavior (bugs) in places which were correct in the past.
+This happens often in situations like changes of the API.
+In the moment the code was written, it was correct and the woftware worked fine.
+Additions of new features or enhancements to the API may have as a side effect that the formerly correct code starts to show a wrong behavior, making the software fail.
+In such cases, the source of the error cannot be attributed to the changes performed in the previous commit, which were correct when they were introduced, since in that moment they referred to a different API.
 
-\grex{poner el siguiente parrafo bien}
-\gema{podemos eliminar el siguiente parrafo porque en realidad lo que queria decir aqui es la contribucion del paper y si la pongo luego puedo eliminar este parrafo} \grex{Queda entonces mirar a ver cual de los dos parrafos es mejor o si hacer un merge}
-The goal of this paper is to find if the cause of the bug can be assigned to the previous commit, understanding that at the time when the previous commit is introduced not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}.
-So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.
+The goal of this paper is to find out to which extent the cause of bugs can be attributed to the previous commit.
+We will consider that the previous commit is ``responsible'' for the bug if that code was buggy (caused the malfunction) in the context of the code at the moment it was introduced.
+If the code was right at that time, but the bug is due to some other change in the chain of previous commits, ot to changes to other areas of the code (such as a change in APIs), we don't consider that change to be responsible of the bug.
 
-In detail, in this paper we attempt to address the following research question regarding who introduced the bug in the source code:
+In detail, we attempt to address the following research questions:
 
@@
 \begin{itemize}
-% \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source?
-}
-    %\item RQ2:  How often is the bug caused in the previous commit?
+     \item RQ1: How can we identify changes done to fix a bug?
      \item RQ2: How often is the previous commit the cause of the bug?
+\end{itemize}
 
-     As already explained, this is the main question that we want to answer in this paper.
-Given bugs that have been fixed, how many of those were introduced by the previous commit.
-To do so, we first have to answer RQ1.
-
+RQ2 is the main question that we want to answer in this paper: given bugs that have been fixed by changing some code, how many of those were introduced by the previous commit.
     %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
     %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
-     \item RQ1: How can we identify changes done to fix a bug?
 
-     To be able to answer RQ2, we first need to study the issue-tracking system and identify there the subset of tickets that correspond to already fixed bugs.
-In essence, RQ1 could be also stated as \emph{How many tickets in the issue tracking system are (real) bug reports?}.
-This is because (real) bugs are managed together in an issue-tracking tool with feature requests, optimizations, test files, among others.
-As we are only interested in our research in the actual bugs, we need to identify those as a previous step to analyze if they have been caused by the previous commit.
+But be able to answer RQ2, we first need to study the issue-tracking system and identify the subset of closed tickets that correspond to fixed bugs.
+In essence, RQ1 could be also stated as \emph{Which tickets in the issue tracking system are (real) bug reports?}.
+This is because (real) bugs are managed in an issue-tracking system together with feature requests, optimizations, test cases, etc.
+As we are only interested in  bugs, we need to identify those as a previous step to analyze if they have been caused by the previous commit.
 
-\end{itemize}
-
-The goal of this paper is to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug.
-Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy.
-Finally, our results could lead to think that all the articles based on this assumption are not using the best data in their approach and as a result they can improve their results with our idea.
-On the other hand, this could be very useful in future researchs, could help developers understanding the bug seeding process.
+One interesting aspect of our study is that it addresses a very fundamental aspect of many studies on how bugs are fixed: the underlying assumption that there must be a commit previous to the fix, touching the same lines that were later fixed, when somebody introduced the bug.
+If some evidence is found that in a large fraction of the cases the corresponding code was correct when it was introduced, there is no reason to blame it as the cause of the bug, even when chenging it fixes the bug.
+Therefore, any result obtained after this assumption should be revisited with some care.
+We want to contribute with a first step in removing this uncertainty.
 
@@
 
-For that, we had to analyze the lines involved in the bug fix commit and in its \emph{parent} commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file before the bug fix and could be different from the commit previous.
+For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
+We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
 We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
@@
 \grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}
-\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
-Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
-The information about the bug fix commit is shown in the figure \ref{fig:6}, this information has been extracted from the gerrit of the figure \ref{fig:1} and we can apreciate that the previous commit in the example \ref{fig:1}(\textit{31f08423}) is different from the parent commit displayed in the figure \ref{fig:6},(\textit{db7fc59ebc}).
+
 \begin{figure}[ht]
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:6}       % Give a unique label
-\caption{Information about the bug fix commit displayed in gerrit. }
+\label{fig:parent}       % Give a unique label
+\caption{Information in Gerrit.\grex{contar que se ve en la figura}}
 \end{figure}
@@
 \fbox{\begin{minipage}{25em}
-\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a bug-fix, we have obtained that in at least 72\% of the tickets analyzed the bug-fixs were real bug reports.}
+\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a fix-bug, we have obtained that in at least 72\% of the tickets analyzed the fix-bugs were real bug reports.}
 \end{minipage}}

### 2016-02-01 paperMSR.tex
tocando comentario de multiples previous commits

--- 2016-02-01 paperMSR.tex
@@
 
-This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug.
+This analysis takes into account that the bug could span many lines that may belong to several previous commits, but in fact, not all of them could had caused the bug.
 It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
-Thus, the cause could be found in a single previous commit, in many or even in none.
-In the \ref{fig:previous} we see that the previous commits are more than one, in this case two \textit{e7be0a988} and \textit{e5296c1da}.
-The previous commit \textit{e7be0a988} didn't cause the bug because it's a line to know the version of the file.
-The previous commit \textit{e5296c1da} caused the bug because it inserted a incorrect \textit{break} line.
-\grex{Todavia no esta del todo claro...
+Hence, the cause could be found in a single previous commit, in many or even in none.
+
+Figure~\ref{fig:manyprevious} contains a real example of a previous commit where more than one commit has been identified.
+In this case, we have two possible commits: \textit{e7be0a988} and \textit{e5296c1da}.
+Previous commit \textit{e7be0a988} did not cause the bug, because the modification affects only the version number of the software.
+It is previous commit \textit{e5296c1da} the one that caused the bug, because it introduced an incorrect \texttt{break} line.
+%\grex{Todavia no esta del todo claro...
 yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo.
 Ademas, nos lo podemos permitir; tenemos espacio.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+
+\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
 
@@
 \includegraphics[height=2.5cm]{manyprevious.png}
-\caption{Previous commits: \textit{e7be0a988}, \textit{e5296c1da} }
-\label{fig:previous}       % Give a unique label
+\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
+\label{fig:manyprevious}       % Give a unique label
 \end{figure}

### 2016-02-01 paperMSR.tex

--- 2016-02-01 paperMSR.tex
@@
 For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file.
-We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
-\grex{Gema, puedes aclarar este parrafo?
+We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit.
+It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
+Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found, that corresponds to the bug-fix shown in~\ref{fig:1}.
+As can be seen, the previous commit (\textit{31f08423}) in Figure~\ref{fig:1} is different from the parent commit displayed in Figure~\ref{fig:parentgerrit} (\textit{db7fc59ebc}).
+
+We do this process to be sure that we are looking the correct change, because sometimes although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
+
+%\grex{Gema, puedes aclarar este parrafo?
 Que es el "parent" commit?
@@
 Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio.
-En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}
+En el gerrit nos dan esa info como se puede ver en la figura}
 
-\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}
+%\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
+%\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
+Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
 
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:parent}       % Give a unique label
-\caption{Information in Gerrit.\grex{contar que se ve en la figura}}
+\caption{Information about the bug as displayed by Gerrit.}
+\label{fig:parentgerrit}       % Give a unique label
 \end{figure}

### 2016-02-01 paperMSR.tex
some changes

--- 2016-02-01 paperMSR.tex
@@
 
-For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit.
-It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
-Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found, that corresponds to the bug-fix shown in~\ref{fig:1}.
-As can be seen, the previous commit (\textit{31f08423}) in Figure~\ref{fig:1} is different from the parent commit displayed in Figure~\ref{fig:parentgerrit} (\textit{db7fc59ebc}).
-
-We do this process to be sure that we are looking the correct change, because sometimes although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
-
-%\grex{Gema, puedes aclarar este parrafo?
+For that, we had to analyze the lines involved in the bug fix commit and in its \emph{parent} commit, being sure that the lines were added, inserted or modified in the previous commit.
+We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file before the bug fix and could be different from the commit previous.
+We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
+\grex{Gema, puedes aclarar este parrafo?
 Que es el "parent" commit?
@@
 Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio.
-En el gerrit nos dan esa info como se puede ver en la figura}
+En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}
 
-%\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
-%\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
+\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
+\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
 Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
-
+The information about the bug fix commit is shown in the figure \ref{fig:6}, this information has been extracted from the gerrit of the figure \ref{fig:1} and we can apreciate that the previous commit in the example \ref{fig:1}(\textit{31f08423}) is different from the parent commit displayed in the figure \ref{fig:6},(\textit{db7fc59ebc}).
 \begin{figure}[ht]
@@
 \includegraphics[height=2cm]{parent.png}
-\caption{Information about the bug as displayed by Gerrit.}
-\label{fig:parentgerrit}       % Give a unique label
+\label{fig:6}       % Give a unique label
+\caption{Information about the bug fix commit displayed in gerrit. }
 \end{figure}
@@
 
-We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!} \gema{Es cierto, son 917}.
+We classify a total of 459 tickets using the tool, resulting in 917 reviews.
 Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
@@
 
-In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} \grex{no se si hace falta, a ver que dice jesus} as bug reports and their previous commits.
+In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} \grex{no se si hace falta, a ver que dice jesus}\gema{Jesus me dijo que no era muy importante a estas alturas} as bug reports and their previous commits.
 The possible outcome of the analysis was one of the following three options:
@@
 
-This analysis takes into account that the bug could span many lines that may belong to several previous commits, but in fact, not all of them could had caused the bug.
+This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug.
 It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
-Hence, the cause could be found in a single previous commit, in many or even in none.
-
-Figure~\ref{fig:manyprevious} contains a real example of a previous commit where more than one commit has been identified.
-In this case, we have two possible commits: \textit{e7be0a988} and \textit{e5296c1da}.
-Previous commit \textit{e7be0a988} did not cause the bug, because the modification affects only the version number of the software.
-It is previous commit \textit{e5296c1da} the one that caused the bug, because it introduced an incorrect \texttt{break} line.
-%\grex{Todavia no esta del todo claro...
+Thus, the cause could be found in a single previous commit, in many or even in none.
+In the \ref{fig:7} we see that the previous commits are more than one, in this case two \textit{e7be0a988} and \textit{e5296c1da}.
+The previous commit \textit{e7be0a988} didn't cause the bug because it's a line to know the version of the file.
+The previous commit \textit{e5296c1da} caused the bug because it inserted a incorrect \textit{break} line.
+\grex{Todavia no esta del todo claro...
 yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo.
 Ademas, nos lo podemos permitir; tenemos espacio.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
-
-\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
 
@@
 \includegraphics[height=2.5cm]{manyprevious.png}
-\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
-\label{fig:manyprevious}       % Give a unique label
+\caption{Previous commits: \textit{e7be0a988}, \textit{e5296c1da} }
+\label{fig:7}       % Give a unique label
 \end{figure}
@@
 As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code.
+We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} or due to our limited knowleadge about the code \ref{fig:9}.
 \grex{Gema, puedes poner un ejemplo de estas dos cosas?
@@
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+\begin{figure}[ht]
+\centering
+\includegraphics[height=2cm]{addedlines.png}
+\label{fig:8}       % Give a unique label
+\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
+%52919
+\end{figure}
 
+\begin{figure}[ht]
+\centering
+\includegraphics[height=2cm]{unknown.png}
+\label{fig:9}       % Give a unique label
+\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
+\end{figure}
 \begin{table}[htb]
@@
 We also studied the distribution of the number of previous commits for each bug.
-This result will provide further insight into the bug-seeding nature; it offers as well an idea of the complexity of identifying the cause of a bug, as the more commits involved, the harder it is to identify the cause and understand it.
-As shown in Table~\ref{tab:secondStage2}, usually the number of commits that can be considered as previous is 1 (over 69\% of the cases), followed by 2 commits (13\%).
-In around 10\% of the cases, 3 or more commits are involved.
-
-% the number of commits that can be considered as previous is 1, followed by 2 commits.
+As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits.
 \grex{the number of commits that can be considered as previous is 1, followed by 2 commits.
@@
 \end{tabular} }
-\caption{ Distribution of the number of commits that can be considered as the previous commit per bug report for each project.}
+\caption{ Distribution of the number of previous commits per bug report for each project.}
 \label{tab:secondStage2}
@@
 In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.
-\grex{Tengo que elaborar mas esto, que es el punto mas impactante del articulo.}
+\grex{Tengo que elaborar mas esto, que es el punto fuerte del articulo.}
 
@@
 As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account.
-In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}} including data sources, intermediate data and scripts that can be obtained.
+In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package including data sources, intermediate data and scripts that can be obtained at the following URL: \gema{Incluir la URL en la que pondre todos los datos y scripts utilizados para los datos.}
 
@@
   \item We have not considered those tickets where the two researchers showed discordance. 
-%  \begin{enumerate}
-%    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
-%    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
-%  \end{enumerate}
+  \begin{enumerate}
+    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
+    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
+  \end{enumerate}
     \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we have lost some \emph{actual} bug reports.
@@
 
-With our methodology we have identifie which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
+With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
 Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
@@
 
-A final field of future work could be concerned with the full automation of the methodology, developing  an automatic classifier based on the idea that not all the previous commits inject the bug.
-\grex{mejorar este parrafo.}
-
-Another interesting investigation could perform the same empirical study on a project with a less active community, to prove if our idea is fulfill in other projects.
-So, for projects that do not evolve as rapidly as OpenStack, e.g., those with a more stable API, could offer completely different results even if applying the same analysis methodology used in this paper.
+A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug.
+Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa?
+En castellano si quieres}
+\gema{Si, la idea es realizar el mismo estudio pero con otro projecto que no sea OpenStack, porque en realidad OpenStack esta evolucionando continuamente.
+Y para poder demostrar que en realidad la idea se cumple en todos los projectos, deberiamos analizar un projecto que sea mas 'estable' y en el que la API no se este cambiando continuamente }
 

### 2016-02-01 paperMSR.tex

--- 2016-02-01 paperMSR.tex
@@
 
-For that, we had to analyze the lines involved in the bug fix commit and in its \emph{parent} commit, being sure that the lines were added, inserted or modified in the previous commit.
-We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file before the bug fix and could be different from the commit previous.
-We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
-\grex{Gema, puedes aclarar este parrafo?
+For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit.
+We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit.
+It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
+Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found, that corresponds to the bug-fix shown in~\ref{fig:1}.
+As can be seen, the previous commit (\textit{31f08423}) in Figure~\ref{fig:1} is different from the parent commit displayed in Figure~\ref{fig:parentgerrit} (\textit{db7fc59ebc}).
+
+We do this process to be sure that we are looking the correct change, because sometimes although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.
+
+%\grex{Gema, puedes aclarar este parrafo?
 Que es el "parent" commit?
@@
 Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio.
-En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}
+En el gerrit nos dan esa info como se puede ver en la figura}
 
-\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
-\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
+%\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
+%\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug.
 Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}
-The information about the bug fix commit is shown in the figure \ref{fig:6}, this information has been extracted from the gerrit of the figure \ref{fig:1} and we can apreciate that the previous commit in the example \ref{fig:1}(\textit{31f08423}) is different from the parent commit displayed in the figure \ref{fig:6},(\textit{db7fc59ebc}).
+
 \begin{figure}[ht]
@@
 \includegraphics[height=2cm]{parent.png}
-\label{fig:6}       % Give a unique label
-\caption{Information about the bug fix commit displayed in gerrit. }
+\caption{Information about the bug as displayed by Gerrit.}
+\label{fig:parentgerrit}       % Give a unique label
 \end{figure}
@@
 
-This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug.
+This analysis takes into account that the bug could span many lines that may belong to several previous commits, but in fact, not all of them could had caused the bug.
 It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
-Thus, the cause could be found in a single previous commit, in many or even in none.
-In the \ref{fig:7} we see that the previous commits are more than one, in this case two \textit{e7be0a988} and \textit{e5296c1da}.
-The previous commit \textit{e7be0a988} didn't cause the bug because it's a line to know the version of the file.
-The previous commit \textit{e5296c1da} caused the bug because it inserted a incorrect \textit{break} line.
-\grex{Todavia no esta del todo claro...
+Hence, the cause could be found in a single previous commit, in many or even in none.
+
+Figure~\ref{fig:manyprevious} contains a real example of a previous commit where more than one commit has been identified.
+In this case, we have two possible commits: \textit{e7be0a988} and \textit{e5296c1da}.
+Previous commit \textit{e7be0a988} did not cause the bug, because the modification affects only the version number of the software.
+It is previous commit \textit{e5296c1da} the one that caused the bug, because it introduced an incorrect \texttt{break} line.
+%\grex{Todavia no esta del todo claro...
 yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo.
@@
 
+\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
+\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
 \begin{figure}[ht]
@@
 \includegraphics[height=2.5cm]{manyprevious.png}
-\caption{Previous commits: \textit{e7be0a988}, \textit{e5296c1da} }
-\label{fig:7}       % Give a unique label
+\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
+\label{fig:manyprevious}       % Give a unique label
 \end{figure}
@@
 As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} or due to our limited knowleadge about the code \ref{fig:9}.
+We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} and we cannot be able to know which previous commit could be the one that forgot added this lines, or due to our limited knowleadge about the code \ref{fig:9}.
 \grex{Gema, puedes poner un ejemplo de estas dos cosas?
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejempli de limited knowledge, cuando encuentre uno bueno lo anado}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 \centering
-\includegraphics[height=2cm]{addedlines.png}
+\includegraphics[height=1cm]{addedlines.png}
 \label{fig:8}       % Give a unique label
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[height=2cm]{unknown.png}
-\label{fig:9}       % Give a unique label
-\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
-\end{figure}
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[height=2cm]{unknown.png}
+%\label{fig:9}       % Give a unique label
+%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
+%\end{figure}
 \begin{table}[htb]

### 2016-02-01 paperMSR.tex

--- 2016-02-01 paperMSR.tex
@@
 \grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
-
+\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
 \begin{figure}[ht]
@@
 As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code.
+We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} and we cannot be able to know which previous commit could be the one that forgot added this lines, or due to our limited knowleadge about the code \ref{fig:9}.
 \grex{Gema, puedes poner un ejemplo de estas dos cosas?
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejempli de limited knowledge, cuando encuentre uno bueno lo anado}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+\begin{figure}[ht]
+\centering
+\includegraphics[height=1cm]{addedlines.png}
+\label{fig:8}       % Give a unique label
+\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
+%52919
+\end{figure}
 
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[height=2cm]{unknown.png}
+%\label{fig:9}       % Give a unique label
+%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
+%\end{figure}
 \begin{table}[htb]

### 2016-02-01 paperMSR.tex
a change
pasandole el aspell

--- 2016-02-01 paperMSR.tex
@@
 
-%\newif\ifdraft
-%\drafttrue
+\newif\ifdraft
+\drafttrue
 %\draftfalse
@@
 
-When a failure is found in some software, developers try to fix it by locating and modifying the source code line(s) that are reponsible for the wrong behaviour.
-It may semm at first reasonable to assume that previous modifications of this line or lines are the cause of the bug.
+When a failure is found in some software, developers try to fix it by locating and modifying the source code line(s) that are the cause for the wrong behavior.
+It may seem at first reasonable to assume that previous modifications of this line or lines are the cause of the bug.
 That previous modification is what will refer through this paper as the \textit{previous commit}.
@@
 This is the reason why many studies in the area of mining software repositories start with this implicit assumption.
-As an anectodal evidence, we have found the following rationales in several areas of research:
+As an anecdotal evidence, we have found the following rationales in several areas of research:
 
@@
 This happens often in situations like changes of the API.
-In the moment the code was written, it was correct and the woftware worked fine.
+In the moment the code was written, it was correct and the software worked fine.
 Additions of new features or enhancements to the API may have as a side effect that the formerly correct code starts to show a wrong behavior, making the software fail.
@@
 The goal of this paper is to find out to which extent the cause of bugs can be attributed to the previous commit.
-We will consider that the previous commit is ``responsible'' for the bug if that code was buggy (caused the malfunction) in the context of the code at the moment it was introduced.
-If the code was right at that time, but the bug is due to some other change in the chain of previous commits, ot to changes to other areas of the code (such as a change in APIs), we don't consider that change to be responsible of the bug.
+We will consider that the previous commit is the cause for the bug if that code was buggy (caused the malfunction) in the context of the code at the moment it was introduced.
+If the code was right at that time, but the bug is due to some other change in the chain of previous commits, or to changes to other areas of the code (such as a change in APIs), we do not consider that change to be the cause of the bug.
 
@@
 In essence, RQ1 could be also stated as \emph{Which tickets in the issue tracking system are (real) bug reports?}.
-This is because (real) bugs are managed in an issue-tracking system together with feature requests, optimizations, test cases, etc.
+This is because (real) bugs are managed in an issue-tracking system together with feature requests, optimization, test cases, etc.
 As we are only interested in  bugs, we need to identify those as a previous step to analyze if they have been caused by the previous commit.
@@
 One interesting aspect of our study is that it addresses a very fundamental aspect of many studies on how bugs are fixed: the underlying assumption that there must be a commit previous to the fix, touching the same lines that were later fixed, when somebody introduced the bug.
-If some evidence is found that in a large fraction of the cases the corresponding code was correct when it was introduced, there is no reason to blame it as the cause of the bug, even when chenging it fixes the bug.
+If some evidence is found that in a large fraction of the cases the corresponding code was correct when it was introduced, there is no reason to blame it as the cause of the bug, even when changing it fixes the bug.
 Therefore, any result obtained after this assumption should be revisited with some care.
@@
 
-The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwersky et al.~\cite{sliwerski2005changes}.
+The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}.
 Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
-The SZZ algorightm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{anotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.
+The SZZ algorithm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{annotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.
 
@@
 
-The two approaches have some metodological patterns in common:
+The two approaches have some methodological patterns in common:
 
@@
 Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes~\cite{yangbug}.
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
 Finally, some bug prediction algorithms are based on SZZ; Kim et al.
@@
 Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes
 Finally, some bug prediction algorithms are based on SZZ; Kim et al.
@@
 First, we have to identify what issues found in Launchpad are bug reports.
-This is not a trivial task and is labour intensive as it has to be done manually.
+This is not a trivial task and is labor intensive as it has to be done manually.
 As the process is repetitive, we developed a web-based tool\footnote{\url{bugtracking.libresoft.es}} that helps in the classification process.
@@
 
-From the experience of analysing a small number of tickets, we agreed on following four criteria: 
+From the experience of analyzing a small number of tickets, we agreed on following four criteria: 
 \begin{enumerate}
 
-    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considerated as a bug report. 
+    \item Each time that the title or the description of a ticket describes an unexpected behavior in the program, our criteria indicated that it was considered as a bug report. 
     \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure.
@@
 
-Finally we need to discard some noise presents in our final results according to the responsibility of the previous commit inserting the bug in the code source.
-Due to they were not responsible for cause the bug, we delete those previous commit which presents the following criteria:
+Finally we had to discard some \emph{noise} present in our results.
+This happened when the changes in the previous commit could not have caused the bug.
+So, we deleted the previous commits for which the following criteria were met:
 
 \begin{itemize}
-    \item Blank lines
-    \item Format changes
+    \item Exclusively blank lines
+    \item Changes in the format
     \item Copied lines
-    \item Changes in the comment.
-    \item Updates in the version of a file. 
+    \item Changes in source code comments
+    \item Updates in the version number of a file/software 
 \end{itemize}
@@
 OpenStack was particularly of interest because of its continuously evolving due to its very active community.
-Currently it has more than 233,000 commits with more than 2 million lines of code \footnote{\url{http://activity.openstack.org/dash/browser/}}.
+Currently it has more than 233,000 commits with more than 2 million lines of code\footnote{\url{http://activity.openstack.org/dash/browser/}}.
 All its history is saved and available in a version control system, as well as its issue tracking system (Launchpad\footnote{\url{https://launchpad.net/openstack}}) and the source code review system (Gerrit\footnote{\url{https://review.openstack.org/}}).
@@
 OpenStack is composed by 9 projects, but we only focused on the main four of them: Nova, Cinder, Neutron and Horizon.
-As can be seen from Table~\ref{tab:OpenStack}, these projects have been very active during their entier history, and in the last year.
+As can be seen from Table~\ref{tab:OpenStack}, these projects have been very active during their entire history, and in the last year.
 
@@
 
-After this, we can answer the first research question because at this moment we have all the data necessary and all the knowleadge to can distinguish bug reports from others reports.
+After this, we can answer the first research question because at this moment we have all the data necessary and all the knowledge to can distinguish bug reports from others reports.
 
@@
 \fbox{\begin{minipage}{25em}
-\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a bug-fix, we have obtained that in at least 72\% of the tickets analyzed the bug-fixs were real bug reports.}
+\textbf{RQ1: Using all the information available in the bug tracking system and code review systems related to a bug-fix, we have obtained that in at least 72\% of the tickets analyzed the bug-fixes were real bug reports.}
 \end{minipage}}
@@
 We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis.
-Then, we analyzed the bug reports together with their previous commits discarting the cases where the previous commit was a false positive (blank lines, changes in comments or even a change in the version of the file).
+Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (blank lines, changes in comments or even a change in the version of the file).
 So, in total we have analyzed 308 previous commit.
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code.
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
+We were unable to decide in 42 cases, as only lines had been added or due to our limited knowledge about the code.
 \grex{Gema, puedes poner un ejemplo de estas dos cosas?
@@
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
-\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+%\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
 
-\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}
+%\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}
 
-\grex{Para los 58 bugs que tenian mas de un identificador previo hay 179 commits.
+%\grex{Para los 58 bugs que tenian mas de un identificador previo hay 179 commits.
 Bien.
@@
 
-\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para entender como de complejo es el problema, porque no es lo mismo que dos commits anteriores sean responsables a que lo sean 5, entendiendo que si son cambios independientes es muy raro que sean causantes de un mismo error.
+%\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para entender como de complejo es el problema, porque no es lo mismo que dos commits anteriores sean responsables a que lo sean 5, entendiendo que si son cambios independientes es muy raro que sean causantes de un mismo error.
 y para saber si algun patron se repite y nos ayuda a entender algo, pero las tablas no llegan a ser muy concluyentes y los numeros son bajos, podemos introducirlo como un poco de discusion sobre que podria ser interesante analizar mas y ver si con mas poblacion se repite algun patron y decir exactamente cuantos comits son los responsables en un bug report.}
@@
   & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
-\raisebox{1ex}{All are the cuase}          & 4 & 3 & 0 & 1 & 8\\[0ex]
+\raisebox{1ex}{All are the cause}          & 4 & 3 & 0 & 1 & 8\\[0ex]
 \raisebox{1ex}{At least one is the cause} & 9 & 7 & 5 & 9 & 30\\[0ex]
@@
 \grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
-\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.
-Otro caso puede ser lo if/else, en estos casos hay que ser cuidadosos y saber diferenciar si el causante fue el comit previo porque se olvido de comporbar una condicion, o si el commit previo no fue el causante del error porque la condicion que se introduce en el commit que arregla el error se debe a que han anadido una nueva funcionalidad despues de haber anadido el if/else y necesitan comprobarla ahora, por tanto seria debido a la evolucion del projecto.
+\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.}
+
+%\gema{Otro caso puede ser lo if/else, en estos casos hay que ser cuidadosos y saber diferenciar si el causante fue el comit previo porque se olvido de comporbar una condicion, o si el commit previo no fue el causante del error porque la condicion que se introduce en el commit que arregla el error se debe a que han anadido una nueva funcionalidad despues de haber anadido el if/else y necesitan comprobarla ahora, por tanto seria debido a la evolucion del projecto.
 En este ultimo caso, si no tenemos toda la descripcion de lo que realmente esta pasando, para poder decidir en que situacion estamos, hemos sido conservadores y hemos inducado que el commit anterior fue el responsable}
@@
 In our analysis, if the latter situation is not explicity mentioned we have considered that the previous commit caused the error.
+
+\gema{ con respecto a los previous commits que son varios: las tablas no llegan a ser muy concluyentes y los numeros son bajos; podemos introducir un poco de discusion sobre que podria ser interesante analizar mas y ver si con mas poblacion se repite algun patron y decir exactamente cuantos comits son los responsables en un bug report.}
 
@@
     \item We have used a random script to extract the tickets from Launchpad that have been reported during 2015.
-There could be unintended bias of the data, because many reasons, as for instnace the phase of the project.
+There could be unintended bias of the data, because many reasons, as for instance the phase of the project.
     \item In some cases, researchers may have classified the previous commit as the cause of the bug, even if this may not be the case (see discussion on additional conditions in if statements).
@@
 
-With our methodology we have identifie which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
+With our methodology we have identified which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs.
 Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
@@
 We thank Dorealda Dalipaj and Nelson Sekitoleko, two PhD students in our research team, that participated in the process of classifying bug reports.
-We also want to express our gratitude to Bitergia\footnote{\url{http://bitergia.com/}} for the OpenStack database and the support they have provided when questions have arised.
+We also want to express our gratitude to Bitergia\footnote{\url{http://bitergia.com/}} for the OpenStack database and the support they have provided when questions have arisen.
 Finally, we would like to acknowledge the Spanish Government because all authors are funded in part by it, through project TIN2014-59400-R.

### 2016-02-01 paperMSR.tex
changing results

--- 2016-02-01 paperMSR.tex
@@
 \alignauthor
-Gema Rodr\'iguez\\
+Gema Rodr\'iguez-P\'erez\\
        \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
@@
 This process requires manual inspection by researchers.
-In the mean classifying a ticket takes \gema{between 5 and 10 minutes per ticket}, although the amount of time decreases with experience as could be expected.
+In the mean classifying a ticket takes between 5 and 10 minutes per ticket, although the amount of time decreases with experience as could be expected.
 
@@
 
-In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} \grex{no se si hace falta, a ver que dice jesus}\gema{Jesus me dijo que no era muy importante a estas alturas} as bug reports and their previous commits.
-The possible outcome of the analysis was one of the following three options:
+In this stage we analyzed the 189 tickets of the classified as \textit{Bug Reports}, the possible outcome of the analysis was one of the following three options:
 
@@
 \includegraphics[height=2.5cm]{manyprevious.png}
-\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
+\caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}
 \label{fig:manyprevious}       % Give a unique label
@@
 As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} and we cannot be able to know which previous commit could be the one that forgot added this lines, or due to our limited knowleadge about the code \ref{fig:9}.
-\grex{Gema, puedes poner un ejemplo de estas dos cosas?
+We were unable to decide in 42 cases or due to our limited knowleadge about the code.
+The figure \ref{fig:add} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
+In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied},\grex{Gema, puedes poner un ejemplo de estas dos cosas?
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejempli de limited knowledge, cuando encuentre uno bueno lo anado}
+Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 \includegraphics[height=1cm]{addedlines.png}
-\label{fig:8}       % Give a unique label
+\label{fig:added}       % Give a unique label
 \caption{Example of added lines where we are unable to decide which previous commit caused the bug}
@@
 
-If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit.
-As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
+If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as the example \ref{fig:3}, whereas 58 had more than one previous commit as the one shows in ~\ref{fig:manyprevious}.
+In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.

### 2016-02-01 paperMSR.tex

--- 2016-02-01 paperMSR.tex
@@
 
-We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!} \gema{Es cierto, son 917}.
+We classify a total of 459 tickets using the tool, resulting in 917 reviews.
 Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
 This process requires manual inspection by researchers.
-In the mean classifying a ticket takes \gema{between 5 and 10 minutes per ticket}, although the amount of time decreases with experience as could be expected.
+In the mean classifying a ticket takes between 5 and 10 minutes per ticket, although the amount of time decreases with experience as could be expected.
 
@@
 
-In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} \grex{no se si hace falta, a ver que dice jesus} as bug reports and their previous commits.
-The possible outcome of the analysis was one of the following three options:
+In this stage we analyzed the 189 tickets of the classified as \textit{Bug Reports}, the possible outcome of the analysis was one of the following three options:
 
@@
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
-We were unable to decide in 42 cases, as only lines had been added or due to our limited knowledge about the code.
-\grex{Gema, puedes poner un ejemplo de estas dos cosas?
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
+We were unable to decide in 42 cases or due to our limited knowleadge about the code.
+The figure \ref{fig:add} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
+In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\grex{Gema, puedes poner un ejemplo de estas dos cosas?
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+\begin{figure}[ht]
+\centering
+\includegraphics[height=1cm]{addedlines.png}
+\label{fig:added}       % Give a unique label
+\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
+%52919
+\end{figure}
 
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[height=2cm]{unknown.png}
+%\label{fig:9}       % Give a unique label
+%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
+%\end{figure}
 \begin{table}[htb]
@@
 
-If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit.
-As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
+If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as the example \ref{fig:3}, whereas 58 had more than one previous commit as the one in ~\ref{fig:manyprevious}.
+In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
-%\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
+\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
 

### 2016-02-01 paperMSR.tex
retocando aqui y alla

--- 2016-02-01 paperMSR.tex
@@
 \end{tabular} }
-\caption{Probability of the cause of the bug when the bug report present one previous commit or more than one previous commit.}
+\caption{Probability of being the cause of a bug depending on if just one previous commit or more than one previous commits are identified.}
 \label{tab:secondStage}
@@
 
-And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
-\begin{enumerate}
-\item Is responsible the function where these lines are content?
-\item Is responsible the last commit that modify something in the function?
-\end{enumerate}
+%And we are talking about a bug report not a new feature, these kinds of cases use to be when a researcher forgot check some case inside a function.
+%\begin{enumerate}
+%\item Is responsible the function where these lines are content?
+%\item Is responsible the last commit that modify something in the function?
+%\end{enumerate}
 
-\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
-\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.}
+%\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}
+%\gema{En casos de que el error se arregle solamente anadiendo lineas, al intentar saber quien es el causante, podemos pensar en que el responsable podria ser el primero que introduce la funcion que olvido tener en cuenta ese caso, o si la funcion en la que se anade el codigo ha sido modificada varias veces pordriamos pensar que el ultimo que modifico la funcion puede ser el causante porue no se dio cuenta que fataba por anadir ese codigo.}
 
@@
 In our analysis, if the latter situation is not explicity mentioned we have considered that the previous commit caused the error.
-
-\gema{ con respecto a los previous commits que son varios: las tablas no llegan a ser muy concluyentes y los numeros son bajos; podemos introducir un poco de discusion sobre que podria ser interesante analizar mas y ver si con mas poblacion se repite algun patron y decir exactamente cuantos comits son los responsables en un bug report.}
 
@@
 This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
-The number of the tickets extracted form Launchpad is high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry.
+The number of the tickets extracted form Launchpad is relatively high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry.
 It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.

### 2016-02-01 paperMSR.tex
changing the image of added lines
algunos retoques mas

@@
 
-The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}.
+Bug-introducing code changes has been a \emph{hot} topic in the mining software repositories research community for over a decade.
+The most used algorithm to identify bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}, which is an improvement to previous approaches~\cite{vcubranic2003hipikat,fischer2003analyzing,fischer2003populating}.
 Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
@@
 
-An improvement to the SZZ algorithm is described by Kim et al.~\cite{kim2006automatic}.
-There the authors used annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion.
+There are several research articles that propose improvements to the SZZ algorithm.
+Kim et al.~\cite{kim2006automatic} use annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion.
 Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments.
+Williams et al.
+revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
+
+The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community.
+Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January
+2016.
+An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.
+Hence, there is a myriad of articles that propose its use for a large number of uses.
+For instance, Yang et al.
+applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
+Kim et al.
+showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
+Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}.
+Izquierdo et al.
+use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}.
+Yin et al.
+use it to find out how many fixes to bugs introduce new bugs~\cite{yin2011fixes}.
+Fejzer et al.
+us it to support code review~\cite{fejzer2015supporting}.
+Asaduzzaman et al.
+apply the SZZ algorithm on Android to study maintenance implications~\cite{asaduzzaman2012bug}.
+
+%Bachmann et al. on the missing link between comments in change logs and bug fixes ~\cite{bachmann2010missing}
+%Wu et al. propose a tool solution~\cite{wu2011relink}
+
+The question of whether a bug report is really a bug or not has been widely studied in the 
+mining software repositories research literature in the last years.
+So, Pan et al.
+classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}.
+Antoniol et al.
+have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}.
+Herzig et al.
+have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sens that they were not a bug report but a feature request, internal refactoring or update to documentation~\cite{herzig2013s}.
+They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools.
+
+%\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
+There the talk is precisely about those bugs whose origina are elsewhere.
+Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}
+
+Prechelt and Pepper offer a good overview of what they call defect-insertion circumstance analysis.
+They point out that one of the obstacles in the way of a reliable analysis are the ``additional changes between defect insertion time and defect correction time that happen to happen at subsequently defect-corrected locations''~\cite{prechelt2014software}.
+Some methods that consider sources of information other than the previous commit already exist.
+So, German et al.~\cite{german2009change}
+point out that software is in constant change, and that changes performed may have impact across the whole system and may lead to the manifestation of bugs in unchanged parts.
+In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base.
 
@@
 present another technique to identify the origins of a bug in~\cite{sinha2010buginnings}.
-Their technique is not text-based technique, as the SZZ algorithm, the authors analyze the effects of bug-fix changes on program dependencies.
+Their technique is not text-based technique, as the SZZ algorithm, as the authors analyze the effects of bug-fix changes on program dependencies.
 So, taking into account the semantics of the source code they achieved higher accuracy in identifying the origins of a bug.
@@
 
-Williams et al.
-revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
-Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
-Finally, some bug prediction algorithms are based on SZZ; Kim et al.
-showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
-\grex{Creo que deberiamos hablar de mas papers que hacen uso de SZZ y derivados}.
-
-The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community.
-Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January
-2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.
-
-The SZZ algorithm (and its \emph{successors}) have been widely used in the research community.
-Williams et al.
-revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
-Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes
-Finally, some bug prediction algorithms are based on SZZ; Kim et al.
-showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.
-
-%\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}.
-There the talk is precisely about those bugs whose origina are elsewhere.
-Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}
-
-In the research literature, we can already find methods that consider other sources of information than the previous commit. In fact, German et al.~\cite{german2009change} 
-point out that software is in constant change, and that changes performed may have impact across the whole system and may lead to the manifestation of bugs in unchanged parts.
-In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base.
-\grex{Quizas mirar si hay mas articulos en esta linea.
-No es muy importante esto.}
+%\grex{Quizas mirar si hay mas articulos en esta linea. No es muy importante esto.}
 
@@
 All data needed to analyze when the bug was introduced can be obtained from the issue tracking systems and the code review systems used generally by free/open source software (FOSS) projects.
-In our analysis, we have focused on Launchpad\footnote{\url{https://launchpad.net/}} as issue tracking system, and Gerrit\footnote{\url{https://www.gerritcodereview.com/}} as code review supporting tool, as they are widely used by FOSS projects nowadays, but our methodology should be generalizable to any such tool.
+In our analysis, we have focused on Launchpad\footnote{\url{https://launchpad.net/}} as issue tracking system, and Gerrit\footnote{\url{https://www.gerritcodereview.com/}} as code review supporting tool, as they are widely used by FOSS projects nowadays, but our methodology should be adaptable to any such tool.
 
@@
 
-We classify a total of 459 tickets using the tool, resulting in 917 reviews.
+We classify a total of 459 tickets using the tool, resulting in 917 reviews\footnote{One review was discarded as it was left empty.}.
 Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.
@@
 
-\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}
+%\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}
 
@@
 \gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
+
 \begin{figure}[ht]
@@
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases or due to our limited knowleadge about the code.
-The figure \ref{fig:add} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
-In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\grex{Gema, puedes poner un ejemplo de estas dos cosas?
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
+We were unable to decide in 42 cases or due to our limited knowledge about the code.
+Figure~\ref{fig:added} shows an example of fix bug commit where only lines have been added.
+In such a case, we are not able to know which previous commit is the one that caused the error, so we classify it as \textit{Undecided}.
+%\grex{Gema, puedes poner un ejemplo de estas dos cosas?
 Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
-We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+Si el ejemplo es verdadero, mejor.}
+\gema{Me falters el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
+In addition, we discarded 40 more previous commits because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+
 \begin{figure}[ht]
 \centering
-\includegraphics[height=1cm]{addedlines.png}
+\includegraphics[height=2.5cm]{addedlines.png}
 \label{fig:added}       % Give a unique label
-\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
+\caption{Example of scenario where the bug fix is composed only of lines added.
+The fix bug commit with lines added in green can be seen on the left (subfigure (1)), and the file as it was before the fix bug commit on the right (subfigure (2)).}
 %52919
@@
 However, situations exist where the additional conditions in an if appear because of the introduction of a new functionality, and thus the line in the previous commit was correct at the time it was introduced.
-In our analysis, if the latter situation is not explicity mentioned we have considered that the previous commit caused the error.
+In our analysis, if the latter situation is not explicitly mentioned we have considered that the previous commit caused the error.
 
@@
 It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.
+However, it should be noted that the amount of tickets in in the order of magnitude of similar studies found in the research literature, for instance Hindle's et al.
+article on large commits, where 100~\cite{hindle2008large}.
 
@@
 
-\nocite{*}
+%\nocite{*}
 %

### 2016-02-01 paperMSR.tex
changes

--- 2016-02-01 paperMSR.tex
@@
 We were unable to decide in 42 cases or due to our limited knowleadge about the code.
-The figure \ref{fig:add} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
-In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\grex{Gema, puedes poner un ejemplo de estas dos cosas?
-Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
+The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
+In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 \centering
-\includegraphics[height=1cm]{addedlines.png}
+\includegraphics[height=2.5cm]{addedlines.png}
 \label{fig:added}       % Give a unique label
 \caption{Example of added lines where we are unable to decide which previous commit caused the bug}
-%52919
 \end{figure}
@@
 
-If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as the example \ref{fig:3}, whereas 58 had more than one previous commit as the one in ~\ref{fig:manyprevious}.
+If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as the example \ref{fig:3}, whereas 58 had more than one previous commit as the one in the example ~\ref{fig:manyprevious}.
 In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
-\grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
-
 %\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}
@@
 As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account.
-In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}} including data sources, intermediate data and scripts that can be obtained.
+In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}}\gema{he creado esta pagina en github para el paquete de reproducibilidad http://gemarodri.github.io/2016-msr-prevcommit/} including data sources, intermediate data and scripts that can be obtained.
 

### 2016-02-01 paperMSR.tex

--- 2016-02-01 paperMSR.tex
@@
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
-We were unable to decide in 42 cases or due to our limited knowledge about the code.
-Figure~\ref{fig:added} shows an example of fix bug commit where only lines have been added.
-In such a case, we are not able to know which previous commit is the one that caused the error, so we classify it as \textit{Undecided}.
-%\grex{Gema, puedes poner un ejemplo de estas dos cosas?
-Uno de solo added lines y otro de limited knowledge.
-Si el ejemplo es verdadero, mejor.}
-\gema{Me falters el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
-In addition, we discarded 40 more previous commits because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
+We were unable to decide in 42 cases or due to our limited knowleadge about the code.
+The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
+In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
+We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
 

### 2016-02-01 paperMSR.tex
Quitando comentarios

--- 2016-02-01 paperMSR.tex
@@
 An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.
-Hence, there is a myriad of articles that propose its use for a large number of uses.
-For instance, Yang et al.
+Hence, there is a myriad of articles that use SZZ on an ample number of scenarios.
+Without trying to be exhaustive, we offer several examples.
+So, Yang et al.
 applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
+Zimmermann et al.
+use it for predicting bugs in large software systems~\cite{zimmermann2007predicting}.
 Kim et al.
 showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
+Kamei et al.
+apply it to validate effort-aware bug-prediction models~\cite{kamei2010revisiting}.
 Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}.
@@
 use it to find out how many fixes to bugs introduce new bugs~\cite{yin2011fixes}.
+Tantithamthavorn et al.
+employ it to quickly identify the location of a bug~\cite{tantithamthavorn2013mining}.
 Fejzer et al.
@@
 In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.
-\grex{Tengo que elaborar mas esto, que es el punto mas impactante del articulo.}
 
@@
 
-A final field of future work could be concerned with the full automation of the methodology, developing  an automatic classifier based on the idea that not all the previous commits inject the bug.
-\grex{mejorar este parrafo.}
-
+A final field of future work could be concerned with the full automation of the methodology presented in this paper, developing an automatic classifier. %\grex{mejorar este parrafo.}
 Another interesting investigation could perform the same empirical study on a project with a less active community, to prove if our idea is fulfill in other projects.

### 2016-02-01 paperMSR.tex
Added example many previous commits

--- 2016-02-01 paperMSR.tex
@@
 \centering
-\includegraphics[height=2.5cm]{manyprevious.png}
+\includegraphics[height=2cm]{manyprevious.png}
 \caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}

### 2016-02-01 paperMSR.tex
Mejorando la legibilida de las graficas

@@
 \centering
-\includegraphics[height=2cm]{parent.png}
+\includegraphics[height=1.9cm]{parent.png}
 \caption{Information about the bug as displayed by Gerrit.}
@@
 
-\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
-\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
+%\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
+%\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
-\includegraphics[height=2cm]{manyprevious.png}
-\caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}
+\includegraphics[height=4cm]{manyprevious.png}
+\caption{Example of previous commit where more than one commit has been identified.
+On the left, the file after the bug-fixing commit.
+Previous commit \textit{e5296c1da} (middle) is the cause of the bug in line 2422 with the presence of an incorrect \texttt{break} statement.
+Previous commits \textit{e7be0a988} (right) has also been identified; however, as it just changes the version number (line 218), it can be classified as not causing the bug.}
 \label{fig:manyprevious}       % Give a unique label
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
-\includegraphics[height=2.5cm]{addedlines.png}
+\includegraphics[height=3.6cm]{addedlines.png}
 \label{fig:added}       % Give a unique label
@@
 %52919
-\end{figure}
+\end{figure*}
 
@@
 As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account.
-In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}}\gema{he creado esta pagina en github para el paquete de reproducibilidad http://gemarodri.github.io/2016-msr-prevcommit/} including data sources, intermediate data and scripts that can be obtained.
+In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gemarodri.github.io/2016-msr-prevcommit/}} including data sources, intermediate data and scripts that can be obtained.
 

### 2016-02-01 paperMSR.tex
add limited knowleadge image

--- 2016-02-01 paperMSR.tex
@@
 The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
-In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
+In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.The figure ~\ref{fig:unknow} shows an example of limited knowleadge about which line could inserted the bug.
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[height=2cm]{unknown.png}
-%\label{fig:9}       % Give a unique label
-%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
-%\end{figure}
+\begin{figure}[ht]
+\centering
+\includegraphics[height=3.5cm]{unknowleadge.png}
+\label{fig:unknow}       % Give a unique label
+\caption{Example of unknowleadge where we are unable to decide which line contains the bug }
+\end{figure}
 \begin{table}[htb]

### 2016-02-01 paperMSR.tex
minor changes to visualization
Working on the last figure introduced

@@
 \drafttrue
-%\draftfalse
+\draftfalse
 
@@
 \centering
-\includegraphics[height=4cm]{manyprevious.png}
+\includegraphics[height=4.1cm]{manyprevious.png}
 \caption{Example of previous commit where more than one commit has been identified.
@@
 Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (blank lines, changes in comments or even a change in the version of the file).
-So, in total we have analyzed 308 previous commit.
+So, in total we have analyzed 308 previous commits.
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause.
-We were unable to decide in 42 cases or due to our limited knowleadge about the code.
-The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines.
-In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.The figure ~\ref{fig:unknow} shows an example of limited knowleadge about which line could inserted the bug.
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
+We were unable to decide in 42 cases or due to our limited knowledge about the code.
+The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only addition of lines.
+In this case, we have not been able to know which previous commit could be the one that forgot to add those lines, so we classified it as \textit{Undecided}.
+Figure~\ref{fig:unknow} offers an example of a different situation, where the researchers could not classify the bug due to not having sufficient knowledge of the change, the context and the project.
 We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
@@
 \centering
-\includegraphics[height=3.6cm]{addedlines.png}
+\includegraphics[height=3.8cm]{addedlines.png}
 \label{fig:added}       % Give a unique label
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
-\includegraphics[height=3.5cm]{unknowleadge.png}
+\includegraphics[height=7.3cm]{unknowleadge.png}
 \label{fig:unknow}       % Give a unique label
-\caption{Example of unknowleadge where we are unable to decide which line contains the bug }
-\end{figure}
+\caption{Example of previous commit where we have been unable to decide which line contains the bug.
+The left code snippet contains the code after the bug fix; the right code snippet shows the code before the bug fix.}
+\end{figure*}
+
 \begin{table}[htb]

### 2016-02-01 paperMSR.tex
Version enviada

@@
 \centering
-\includegraphics[height=2in, width=7in]{responsible.png}
+\includegraphics[height=2in,width=7.2in]{responsible.png}
 \caption{Example of a change in which the bug was introduced in the previous commit. More recent versions of the code are on the left.}
@@
 \centering
-\includegraphics[height=2in, width=7in]{noResponsible.png}
+\includegraphics[height=2in,width=7.2in]{noResponsible.png}
 \caption{Example of a change where the previous commit, 0dc91bed, did not insert the bug. More recent versions of the code are on the left.}
@@
 Bug-introducing code changes has been a \emph{hot} topic in the mining software repositories research community for over a decade.
-The most used algorithm to identify bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}, which is an improvement to previous approaches~\cite{vcubranic2003hipikat,fischer2003analyzing,fischer2003populating}.
-Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
+The most used algorithm to automatically identify bug-introducing code changes has been proposed by Sliwerski et al.~\cite{sliwerski2005changes}, which is an improvement to previous approaches~\cite{vcubranic2003hipikat,fischer2003analyzing,fischer2003populating}.
+Currently, it is a well-known algorithm, called SZZ, based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version.
 The SZZ algorithm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{annotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.
 
-There are several research articles that propose improvements to the SZZ algorithm.
+There are several research articles that suggest improvements to the SZZ algorithm.
 Kim et al.~\cite{kim2006automatic} use annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion.
@@
 Williams et al.
-revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
+have revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.
 
@@
 So, Yang et al.
-applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
+apply SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
 Zimmermann et al.
@@
 Kim et al.
-showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
+show how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}.
 Kamei et al.
@@
 Yin et al.
-use it to find out how many fixes to bugs introduce new bugs~\cite{yin2011fixes}.
+use SZZ to find how many fixes to bugs introduce new bugs~\cite{yin2011fixes}.
 Tantithamthavorn et al.
@@
 Fejzer et al.
-us it to support code review~\cite{fejzer2015supporting}.
+use it to support code review~\cite{fejzer2015supporting}.
 Asaduzzaman et al.
-apply the SZZ algorithm on Android to study maintenance implications~\cite{asaduzzaman2012bug}.
+apply the SZZ algorithm on Android to study its maintainability~\cite{asaduzzaman2012bug}.
 
@@
 %Wu et al. propose a tool solution~\cite{wu2011relink}
-
-The question of whether a bug report is really a bug or not has been widely studied in the 
-mining software repositories research literature in the last years.
-So, Pan et al.
-classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}.
-Antoniol et al.
-have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}.
-Herzig et al.
-have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sens that they were not a bug report but a feature request, internal refactoring or update to documentation~\cite{herzig2013s}.
-They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools.
 
@@
 
-Prechelt and Pepper offer a good overview of what they call defect-insertion circumstance analysis.
+Prechelt and Pepper offer a good overview of the limitations of bug-introducing code changes when adopted by practitioners.
 They point out that one of the obstacles in the way of a reliable analysis are the ``additional changes between defect insertion time and defect correction time that happen to happen at subsequently defect-corrected locations''~\cite{prechelt2014software}.
@@
 \end{enumerate}
+
+On the other hand, the question of whether a bug report is really a bug or not has been widely studied in the 
+mining software repositories research literature in the last years.
+So, Pan et al.
+classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}.
+Antoniol et al.
+have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}.
+Herzig et al.
+have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sense that they were not a bug report but a feature request, an internal refactoring or an update to documentation~\cite{herzig2013s}.
+They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools.
 
@@
 OpenStack is a cloud computing platform with a huge developing community (more than 5,000 developers) and significant industrial support from several major companies such as Red Hat, Intel, IBM, HP, etc.
-OpenStack was particularly of interest because of its continuously evolving due to its very active community.
+OpenStack was particularly of interest because it is continuously evolving due to its very active community.
 Currently it has more than 233,000 commits with more than 2 million lines of code\footnote{\url{http://activity.openstack.org/dash/browser/}}.
-All its history is saved and available in a version control system, as well as its issue tracking system (Launchpad\footnote{\url{https://launchpad.net/openstack}}) and the source code review system (Gerrit\footnote{\url{https://review.openstack.org/}}).
+All its history is saved and available in a version control system\footnote{\url{https://wiki.openstack.org/wiki/Getting_The_Code}}, as well as its issue tracking system (Launchpad\footnote{\url{https://launchpad.net/openstack}}) and the source code review system (Gerrit\footnote{\url{https://review.openstack.org/}}).
 
-OpenStack is composed by 9 projects, but we only focused on the main four of them: Nova, Cinder, Neutron and Horizon.
-As can be seen from Table~\ref{tab:OpenStack}, these projects have been very active during their entire history, and in the last year.
+OpenStack is composed of 9 projects, but we only focused on the main four: Nova, Cinder, Neutron and Horizon.
+As can be seen in Table~\ref{tab:OpenStack}, these projects have been very active during their entire history, and in the last year.
 
@@
 This process requires manual inspection by researchers.
-In the mean classifying a ticket takes between 5 and 10 minutes per ticket, although the amount of time decreases with experience as could be expected.
+In the mean, classifying a ticket takes between 5 and 10 minutes, although the amount of time decreases with experience as could be expected.
 
@@
 
-Table~\ref{tab:2} shows the classification percentages for each researcher after analyzing the tickets, and the number of tickets classified by two different researchers in the same group.
+Table~\ref{tab:2} shows the classification percentages of the analized tickets for each researcher, and the number of tickets classified into the same group by two different researchers.
 %Obtaining that the researchers R1 and R2 had a similar data in their results, whereas research R2 got results significantly different with a higher number of tickets classified as Bug Report.
 As a result, researchers identified 292 tickets in the same group, that is, their results matched in over 70\% of the cases.
-Of those, 209 tickets had been classified in the \emph{Bug report} group, 74 in the \emph{Not Bug Report} group and 9 tickets classified in the \emph{Undecided} group.
+Of those, 209 tickets had been classified in the \emph{Bug report} group, 74 in the \emph{Not Bug Report} group, and 9 tickets classified in the \emph{Undecided} group.
 
@@
 
-After this, we can answer the first research question because at this moment we have all the data necessary and all the knowledge to can distinguish bug reports from others reports.
+%After this, we can answer the first research question because at this moment we have all the data necessary and all the knowledge to can distinguish bug reports from others reports.
 
@@
 
-In this stage we analyzed the 189 tickets of the classified as \textit{Bug Reports}, the possible outcome of the analysis was one of the following three options:
+In this stage we have analyzed the 189 tickets\footnote{20 tickets have not been analyzed due to time constraints.} of the classified as \textit{Bug Reports}, the possible outcome of the analysis was one of the following three options:
 
@@
 
-This analysis takes into account that the bug could span many lines that may belong to several previous commits, but in fact, not all of them could had caused the bug.
-It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced.
+This analysis takes into account that the bug could span many lines that may belong to several previous commits, but in fact, not all of them may have caused the bug.
+It may happen that in the previous commit lines may have been copied from further previous commits, comments may have been modified, or blank spaces/lines may have been introduced.
 Hence, the cause could be found in a single previous commit, in many or even in none.
@@
 \centering
-\includegraphics[height=4.1cm]{manyprevious.png}
+\includegraphics[height=4.9cm,width=7.2in]{manyprevious.png}
 \caption{Example of previous commit where more than one commit has been identified.
-On the left, the file after the bug-fixing commit.
-Previous commit \textit{e5296c1da} (middle) is the cause of the bug in line 2422 with the presence of an incorrect \texttt{break} statement.
-Previous commits \textit{e7be0a988} (right) has also been identified; however, as it just changes the version number (line 218), it can be classified as not causing the bug.}
+On the left in subfigure (1), the file after the bug-fixing commit.
+Previous commit \textit{e5296c1da} (subfigure (2)) is the cause of the bug in line 2422 with the presence of an incorrect \texttt{break} statement.
+Previous commits \textit{e7be0a988} (subfigure (3)) has also been identified; however, as it just changes the version number (line 218), it can be classified as not causing the bug.}
 \label{fig:manyprevious}       % Give a unique label
@@
 
-We identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis.
-Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (blank lines, changes in comments or even a change in the version of the file).
+We have identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis.
+Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
 So, in total we have analyzed 308 previous commits.
 
-As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause.
-We were unable to decide in 42 cases or due to our limited knowledge about the code.
-The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only addition of lines.
-In this case, we have not been able to know which previous commit could be the one that forgot to add those lines, so we classified it as \textit{Undecided}.
-Figure~\ref{fig:unknow} offers an example of a different situation, where the researchers could not classify the bug due to not having sufficient knowledge of the change, the context and the project.
-We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
+As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 have been identified as not being the cause.
+
+We have been unable to decide in 42 cases. Figure~8 %\ref{fig:added}
+ provides an example of such a situation; the file content after the bug fix can be seen on the left in subfigure (1) and the file before the fix commit on the right in subfigure (2); as it can be observed, the only difference is lines that have been added.
+Figure~9 %\ref{fig:unknow}
+ offers an example of a different situation, where the researchers have not been able to classify the bug due to not having sufficient knowledge of the change, the context and the project.
+In both cases, we have not been able to know which previous commit could be the cause of the bug, so we classified them as \textit{Undecided}.
 
@@
 \centering
-\includegraphics[height=3.8cm]{addedlines.png}
+\includegraphics[height=4.7cm, width=13cm]{addedlines.png}
 \label{fig:added}       % Give a unique label
@@
 \centering
-\includegraphics[height=7.3cm]{unknowleadge.png}
+\includegraphics[height=7.8cm]{unknowleadge.png}
 \label{fig:unknow}       % Give a unique label
@@
 
-If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as the example \ref{fig:3}, whereas 58 had more than one previous commit as the one in the example ~\ref{fig:manyprevious}.
-In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure.
+If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as in Figure~\ref{fig:3}, whereas 58 had more than one previous commit as the one in Figure~\ref{fig:manyprevious}.
+In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, while 30 did not cause the failure.
 For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not.
@@
   & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
-  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
+  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
 \raisebox{1ex}{Neutron} & 11 & 3 & 2 & 2 & 0 \\[0ex]
@@
    & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous} & \multicolumn{1}{c}{Total}\\
-  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
+  & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
 \raisebox{1ex}{All are the cause}          & 4 & 3 & 0 & 1 & 8\\[0ex]
